---
title: "Ablation Waiting Time Audit Report"
output:
  pdf_document: default
  html_document: default
date: "2024-01-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.table.format = "html") 
library(dplyr)
library(kableExtra)

# This is a way of generating an All Organs stats and individual organ stats in single table
overall_group = function(data, col_name)
{
  d1 = data %>%
    mutate(summary_level = "grouped")
  
  d2 = data %>%
    mutate(summary_level = "ungrouped") %>%
    mutate(!!sym(col_name) := "All Organs")
  
  d12 = rbind(d1, d2) %>%
    group_by(summary_level, !!sym(col_name))
  
  # Loose the summary_level column from the final return data frame as it isn't necessary
  return(subset(d12,select = -c(summary_level)))
}

# Remove Dummy patient numbers from the data
rxDoneAuditData <- rxDoneData %>% 
  filter((ID != "000-1" & ID != "00000-1")) %>%
  filter(RxDate >= as.Date(audit_start_date) & RxDate < as.Date(audit_end_date)) 
```


<!-- PCL: I had to do an ugly global variable hack to get audit_start_date and audit_end_date visible from this file, but it works-->
<h1>Ablation Waiting Time Audit</h1>
<br>
Audit Generated on: 
```{r}
renderText({
  format(Sys.time(), "%a %b %d %X %Y")
})
```
<br>
Audit Period from: `r audit_start_date` to: `r audit_end_date`<br><br>
Organs included in audit: `r paste(audit_organs)`<br>

<h2>Ablation Referral to DTT Times</h2>
```{r ref_dtt}
rxDoneAuditData %>%
  mutate(within10=ifelse(Ref_DTT<=10, 1,0),
         within21=ifelse(Ref_DTT<=21, 1, 0)) %>%
  overall_group("Organs") %>%
  summarise(mean=round(mean(Ref_DTT, na.rm=T), 1),
            median=round(median(Ref_DTT, na.rm=T), 1),
            w10=(sum(within10, na.rm=T)),
            w21=(sum(within21, na.rm=T)), 
            'w10%'=round(sum(within10, na.rm=T)/n()*100, 1),
            'w21%'=round(sum(within21, na.rm=T)/n()*100, 1), 
            n=n()) %>%
  
  mutate(Organs=if_else(is.na(Organs), 'All Organs', Organs),
    'Organ (n)'=paste(Organs, ' (N=', n,')', sep='')) %>%
  ungroup()%>%
  select('Organ (n)', mean, median, 'w10', 'w21', 'w10%', 'w21%') %>%
  kbl %>%
  kable_styling()
```

<h2>Ablation DTT to Rx Times</h2>
```{r dtt_rx}
rxDoneAuditData %>%
  mutate(within31=ifelse(DTT_Rx<=31, 1,0), within45=ifelse(DTT_Rx<=45, 1,0), within60=ifelse(DTT_Rx<=60, 1, 0)) %>%
  overall_group("Organs") %>%
  summarise(mean=round(mean(DTT_Rx, na.rm=T), 1),
            median=round(median(DTT_Rx, na.rm=T), 1),
            w45=(sum(within45, na.rm=T)),
            w60=(sum(within60, na.rm=T)), 
            'w31%'=round(sum(within31, na.rm=T)/n()*100, 1),
            'w45%'=round(sum(within45, na.rm=T)/n()*100, 1),
            'w60%'=round(sum(within60, na.rm=T)/n()*100, 1), 
            n=n()) %>%
  mutate(Organs=if_else(is.na(Organs), 'All Organs', Organs),
    'Organ (n)'=paste(Organs, ' (N=', n,')', sep='')) %>%
  ungroup()%>%
  select('Organ (n)', mean, median, 'w31%', 'w45%', 'w60%', n) %>%
  kbl %>%
  kable_styling()
```

<h2>Ablation Referral to Rx Times</h2>
```{r ref_rx}
rxDoneAuditData %>%
  mutate(within90=ifelse(Ref_RxDone<=90, 1,0)) %>%
  overall_group("Organs") %>%
  summarise(mean=round(mean(Ref_RxDone, na.rm=T), 1),
            median=round(median(Ref_RxDone, na.rm=T), 1),
            'w90'=round(sum(within90, na.rm=T), 1), 
            'w90%'=round(sum(within90, na.rm=T)/n()*100, 1),
            n=n(),
            ) %>%
  mutate(Organs=if_else(is.na(Organs), 'All Organs', Organs),
    'Organ (n)'=paste(Organs, ' (N=', n,')', sep='')) %>%
  ungroup()%>%
  filter(Organs != 'Multiple Organs') %>%
  select('Organ (n)', mean, median, 'w90%') %>%
  kbl %>%
  kable_styling()
```


<h2>Ablation Referral Days Stopped (Pre- or Post-DDT)</h2>
```{r daystopped_pre_or_post_dtt}
rxDoneAuditData %>% 
  mutate(
    clockstopped=if_else(
      is.na(ClockStopDaysPreDTT), 
      if_else(is.na(ClockStopDaysPostDTT), 'Not Stopped', 'Stopped Post DTT'),
      if_else(is.na(ClockStopDaysPostDTT), 'Stopped Pre DTT', 'Stopped Both Pre and Post DTT')),
    daysStopped=if_else(
      is.na(ClockStopDaysPreDTT),
      if_else(is.na(ClockStopDaysPostDTT), 0, ClockStopDaysPostDTT),
      if_else(is.na(ClockStopDaysPostDTT), ClockStopDaysPreDTT, ClockStopDaysPreDTT+ClockStopDaysPostDTT),
    ),
  ) %>% 
  group_by(clockstopped) %>% 
  #mutate(clockstopped=paste(clockstopped, ' (N=', n,')', sep='')) %>%
  summarise(n=n(), mean=round(mean(daysStopped), 1), median=round(median(daysStopped), 1))%>%
  kbl %>%
  kable_styling()
```


<h2>Ablation Referral Days Stopped (Pre- and Post-DDT Combined)</h2>
```{r daystopped_pre_and_post_dtt}
# This groups clock stops before and after DTT all into the same group
rxDoneAuditData %>% 
  mutate(
    clockstopped=if_else(
      is.na(ClockStopDaysPreDTT), 
      if_else(is.na(ClockStopDaysPostDTT), 'Not Stopped', 'Stopped'),
      if_else(is.na(ClockStopDaysPostDTT), 'Stopped', 'Stopped')),
    daysStopped=if_else(
      is.na(ClockStopDaysPreDTT),
      if_else(is.na(ClockStopDaysPostDTT), 0, ClockStopDaysPostDTT),
      if_else(is.na(ClockStopDaysPostDTT), ClockStopDaysPreDTT, ClockStopDaysPreDTT+ClockStopDaysPostDTT),
    ),
  ) %>% 
  group_by(clockstopped) %>% 
  summarise(n=n(), mean=round(mean(daysStopped), 1), median=round(median(daysStopped), 1))%>%
  kbl %>%
  kable_styling()
```


<h2>Ablation Referral Clockstops</h2>
```{r clockstop}
  rxDoneAuditData %>% mutate(
    clockstopped=if_else(
      is.na(ClockStopDaysPreDTT), 
      if_else(is.na(ClockStopDaysPostDTT), 'Not Stopped', 'Stopped Post DTT'),
      if_else(is.na(ClockStopDaysPostDTT), 'Stopped Pre DTT', 'Stopped Both Pre and Post DTT')),
    daysStopped=if_else(
      is.na(ClockStopDaysPreDTT),
      if_else(is.na(ClockStopDaysPostDTT), 0, ClockStopDaysPostDTT),
      if_else(is.na(ClockStopDaysPostDTT), ClockStopDaysPreDTT, ClockStopDaysPreDTT+ClockStopDaysPostDTT),
    ),
  ) %>% filter(clockstopped != 'Not Stopped') %>% select(ID, ClockStopWhy) %>%
  kbl %>%
  kable_styling()
```


## Including Plots
```{r ttt_plot, echo=FALSE}

rxDoneAuditDataplot <- ggplot(rxDoneAuditData, aes(x=RxDate, text=paste(ID, ' (',Organs,')\n', ClockStopWhy, sep=''))) +
      geom_point( aes(y=Ref_DTT,              color="Ref to DTT")) + 
      geom_point( aes(y=DTT_Rx,               color="DTT to Rx")) + 
      geom_point( aes(y=Ref_RxDone,           color="Ref to Rx")) +
      geom_point( aes(y=ClockStopDaysPreDTT,  color="Clock Stops Pre-DTT")) +
      geom_point( aes(y=ClockStopDaysPostDTT, color="Clock Stops Post-DTT")) +
      theme(legend.position="bottom") +
      scale_color_manual(values = rxdonePlotColors) +
      guides(color=guide_legend("Treated Patients...")) +
      labs(y="Number of Days") +
      ggtitle("Time to Treatment")
  
  # PCL: Not sure this makes sense now we can change dates of audit dynamically
  #break.vec <- seq(from = as.Date("2023-01-01"), to = as.Date("2024-01-01"),
  #                   by = "month")
  #labels.vec <- strftime(break.vec, "%b")
  #labels.vec[1] <- "Jan '23"
  #labels.vec[13] <- "Jan '24"
    
 rxDoneAuditDataplot 
 #    scale_x_date(limits = as.Date(c('2022-12-31', '2023-12-31'), format = "%d/%m/%Y", origin='1970-01-01'), #breaks=break.vec,  labels=labels.vec, expand=c(0.1,0)) +
 #    theme(legend.position="bottom")
 
```

```{r organ_pie}
rxDoneAuditData %>% 
  group_by(Organs) %>%
  summarise(n=n()) %>% 
  mutate(prop=n/sum(.$n) *100,
         ypos= cumsum(prop)- 0.5*prop,
         Organs=paste(Organs, ' (N=',n,')', sep='')) %>%
  ggplot(aes(x="", y=n, fill=Organs)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) + 
  theme_void() +
  scale_fill_brewer(palette="Set1", name="Tumour Type")

```

## Long waits
<h2>Ablation Long Waits</h2>
```{r longwaits}
rxDoneAuditData %>% 
  filter(Ref_RxDone > 120) %>%
  select(ID, Ref_RxDone, ClockStopDaysPreDTT, ClockStopDaysPostDTT) %>%
  kbl %>%
  kable_styling()

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
