---
title: "TARGET-UK: Ablation Waiting Time Audit Report"
output:
  html_document:
    toc: true
    self_contained: true
date: "`r format(Sys.Date(), '%d %B %Y')`"
params:
  audit_start_date: !r Sys.Date() - 365
  audit_end_date: !r Sys.Date()
  audit_organs: ["Liver", "Lung", "Kidney", "Adrenal", "Other"]
---

```{css, echo=FALSE}
/* Screen and print shared */
body { font-size: 14px; }
table { 
  font-size: 13px; 
  width: 100% !important;
  table-layout: auto;
}
th, td { 
  padding: 4px 8px !important;
  font-size: 13px;
}
img { max-width: 100% !important; height: auto !important; }

/* Print-specific: force landscape and control margins */
@media print {
  @page { 
    size: A4 portrait;
    margin: 8mm 6mm 8mm 6mm;
  }
  body { 
    font-size: 11px;
    width: 198mm;
  }
  table {
    font-size: 10px;
    page-break-inside: avoid;
    table-layout: auto;
  }
  th, td { padding: 2px 4px !important; font-size: 10px; }
  img, .plot { 
    max-width: 196mm !important; 
    width: 196mm !important;
    height: auto !important;
    page-break-inside: avoid;
  }
  .figure { 
    max-width: 196mm !important;
    page-break-inside: avoid;
  }
  h2 { page-break-before: auto; }
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(fig.width = 10, fig.height = 5, dpi = 120)
options(knitr.table.format = "html")
library(dplyr)
library(lubridate)
library(purrr)
library(kableExtra)

audit_start_date <- params$audit_start_date
audit_end_date   <- params$audit_end_date
audit_organs     <- params$audit_organs

auditStart <- as.Date(audit_start_date)
auditEnd   <- as.Date(audit_end_date)

# ---------------------------------------------------------------------------
# Build a list of annual windows covering the audit period.
# Each window is exactly one calendar year. The final window is the audit
# period itself (which may be < 1 year); all preceding windows are the
# same-length year immediately before the next window, with no overlap.
#
# E.g. audit 1 Jan 2021 -- 31 Dec 2023 produces:
#   Year 1: 2021-01-01 -- 2021-12-31
#   Year 2: 2022-01-01 -- 2022-12-31
#   Year 3: 2023-01-01 -- 2023-12-31
# ---------------------------------------------------------------------------
buildYearWindows <- function(start, end) {
  windows <- list()
  current <- start
  while (current < end) {
    window_end <- min(current + years(1) - days(1), end)
    yr_label   <- format(current, "%Y")
    # If window spans two calendar years use a range label
    if (format(current, "%Y") != format(window_end, "%Y")) {
      yr_label <- paste0(format(current, "%Y"), "/", format(window_end, "%Y"))
    }
    windows <- append(windows, list(list(
      label = yr_label,
      start = current,
      end   = window_end
    )))
    current <- window_end + days(1)
  }
  windows
}

yearWindows <- buildYearWindows(auditStart, auditEnd)
yearLabels  <- sapply(yearWindows, `[[`, "label")
nYears      <- length(yearWindows)

# ---------------------------------------------------------------------------
# Helper: overall_group -- adds an "All Organs" summary row
# ---------------------------------------------------------------------------
overall_group <- function(data, col_name) {
  d1 <- data %>% mutate(summary_level = "grouped")
  d2 <- data %>% mutate(summary_level = "ungrouped") %>%
    mutate(!!sym(col_name) := "All Organs")
  rbind(d1, d2) %>%
    group_by(summary_level, !!sym(col_name)) %>%
    { subset(., select = -c(summary_level)) }
}

add_year_separators <- function(tbl, group_width, nYears) {
  for (i in seq_len(nYears)) {
    tbl <- kableExtra::column_spec(tbl, 2 + (i - 1) * group_width, border_left = TRUE)
  }
  tbl
}

# ---------------------------------------------------------------------------
# Remove dummy patients and apply organ filter once, producing a clean base
# data frame, then split into per-year slices.
# ---------------------------------------------------------------------------
cleanBase <- function(data) {
  d <- data |>
    filter(!(ID %in% c("000-1", "00000-1", "000000-1")))
  if (!("All" %in% audit_organs)) {
    d <- d |> filter(Organs %in% audit_organs)
  }
  d
}

rxDoneClean <- cleanBase(rxDoneData)
rxWaitClean <- cleanBase(rxWaitData)

# List of per-year data frames
rxDoneByYear <- lapply(yearWindows, function(w) {
  rxDoneClean |> filter(RxDate >= w$start & RxDate <= w$end)
})
names(rxDoneByYear) <- yearLabels

# For wait-time plots we still need the full audit-period data frame
rxDoneAuditData    <- rxDoneClean |> filter(RxDate >= auditStart & RxDate <= auditEnd)
rxWaitAuditData    <- rxWaitClean

# ---------------------------------------------------------------------------
# Significance testing helpers
# Both now accept explicit data frames rather than relying on globals
# ---------------------------------------------------------------------------
t.significantMarker <- function(p.value) {
  if (is.na(p.value)) "" else if (p.value < 0.05) " *" else ""
}

z.significantMarker <- function(p.value) {
  if (is.na(p.value)) "" else if (p.value < 0.05) " +" else ""
}

getTTestPValueFromData <- function(current_data, preceding_data, organ, column) {
  tryCatch({
    x <- current_data   |> filter(organ == "All Organs" | Organs == organ) |> pull(!!sym(column))
    y <- preceding_data |> filter(organ == "All Organs" | Organs == organ) |> pull(!!sym(column))
    t.test(x, y)$p.value |> t.significantMarker()
  }, error = function(e) "")
}

getZTestPValueFromTables <- function(current_tbl, preceding_tbl, organ, count_col, n_col = "n") {
  tryCatch({
    prop.test(
      x = c(current_tbl[current_tbl$Organs == organ, count_col],
            preceding_tbl[preceding_tbl$Organs == organ, count_col]),
      n = c(current_tbl[current_tbl$Organs == organ, n_col],
            preceding_tbl[preceding_tbl$Organs == organ, n_col])
    )$p.value |> z.significantMarker()
  }, error = function(e) "")
}

# ---------------------------------------------------------------------------
# Generic multi-year table builder.
#
# summarise_fn : function(data_frame) -> summary tibble with columns
#                Organs, n, mean, median, and any percentage columns
# pct_cols     : character vector of percentage column names e.g. c("w10%","w21%")
# count_cols   : corresponding raw count column names for z-test e.g. c("w10","w21")
# raw_col      : column name in the raw data for the t-test e.g. "Ref_DTT"
# ---------------------------------------------------------------------------
buildMultiYearTable <- function(summarise_fn, pct_cols, count_cols, raw_col) {
  # Build per-year summary tables
  yr_tables <- lapply(rxDoneByYear, summarise_fn)

  # All organs + individual organ rows to test
  organs_to_test <- c(audit_organs, "All Organs")

  # Build comparison columns year-by-year (each vs its predecessor)
result <- yr_tables[[1]] |>
  mutate(
    `Organ Treated` = paste0(Organs, " (N=", n, ")"),
    !!paste0("n_", yearLabels[1]) := paste0("N=", n)
  ) |>
  select(`Organ Treated`, Organs, all_of(paste0("n_", yearLabels[1])), mean, median, all_of(pct_cols))

  colnames(result)[colnames(result) == "mean"]   <- paste0("mean_",   yearLabels[1])
  colnames(result)[colnames(result) == "median"] <- paste0("median_", yearLabels[1])
  for (pc in pct_cols) {
    colnames(result)[colnames(result) == pc] <- paste0(pc, "_", yearLabels[1])
  }

  for (i in seq_along(yearWindows)) {
    lbl      <- yearLabels[i]
    cur_tbl  <- yr_tables[[i]]
    cur_data <- rxDoneByYear[[i]]

    if (i > 1) {
      prev_lbl  <- yearLabels[i - 1]
      prev_tbl  <- yr_tables[[i - 1]]
      prev_data <- rxDoneByYear[[i - 1]]

      # Significance markers per organ
      sig_t  <- setNames(
        sapply(organs_to_test, function(org)
          getTTestPValueFromData(cur_data, prev_data, org, raw_col)),
        organs_to_test)

      sig_z <- lapply(seq_along(pct_cols), function(j) {
        setNames(
          sapply(organs_to_test, function(org)
            getZTestPValueFromTables(cur_tbl, prev_tbl, org, count_cols[j])),
          organs_to_test)
      })
      names(sig_z) <- pct_cols

      add <- cur_tbl |>
        select(Organs, n, mean, median, all_of(pct_cols)) |>
        mutate(
          !!paste0("n_",      lbl) := paste0("N=", n),
          !!paste0("mean_",   lbl) := paste0(mean,   " (", prev_tbl$mean[match(Organs, prev_tbl$Organs)],   ")",
                                              sapply(Organs, function(o) sig_t[o])),
          !!paste0("median_", lbl) := paste0(median, " (", prev_tbl$median[match(Organs, prev_tbl$Organs)], ")")
        )

      for (j in seq_along(pct_cols)) {
        pc       <- pct_cols[j]
        prev_pct <- prev_tbl[[pc]][match(cur_tbl$Organs, prev_tbl$Organs)]
        add <- add |>
          mutate(!!paste0(pc, "_", lbl) :=
                   paste0(!!sym(pc), " (", prev_pct, ")",
                          sapply(Organs, function(o) sig_z[[pc]][o])))
      }

      add <- add |> select(Organs, starts_with("n_"), starts_with("mean_"),
                           starts_with("median_"), ends_with(lbl))

      result <- result |> left_join(
        add |> select(
          Organs,
          all_of(c(
            paste0("n_", lbl),
            paste0("mean_", lbl),
            paste0("median_", lbl),
            paste0(pct_cols, "_", lbl)
          ))
        ),
        by = "Organs"
      )
    } else {
      # First year -- just add N column
      result <- result |>
        mutate(!!paste0("n_", lbl) := paste0("N=", yr_tables[[1]]$n[match(Organs, yr_tables[[1]]$Organs)]))
    }
  }

  result |> filter(Organs == "All Organs" | Organs %in% audit_organs)
}

# ---------------------------------------------------------------------------
# Generic multi-year boxplot builder
# ---------------------------------------------------------------------------
buildMultiYearBoxplot <- function(value_col, title_str, ylab_str, hlines = list()) {
  # Stack all years into one data frame with a Year column
  combined <- bind_rows(lapply(seq_along(yearWindows), function(i) {
    rxDoneByYear[[i]] |>
      select(Organs, !!sym(value_col)) |>
      mutate(
        Year = yearLabels[i],
        !!sym(value_col) := if_else(!!sym(value_col) < 0, NA_real_, !!sym(value_col))
      )
  }))

  p <- combined |>
    ggplot(aes(x = Organs, y = !!sym(value_col), color = Year)) +
    geom_boxplot(position = "dodge2")

  for (h in hlines) {
    p <- p + geom_hline(yintercept = h$y, linetype = "dashed", color = h$color)
  }

  auditPeriodText <- paste0(format(auditStart, "%e %b %Y"), " -- ", format(auditEnd, "%e %b %Y"))

  p + ggtitle(paste0(title_str, "\n", auditPeriodText)) +
    labs(y = ylab_str, x = "Organ Treated") +
    scale_color_brewer(palette = "Set1") +
    theme(
      legend.position = "bottom",
      axis.text.x     = element_text(
        angle = if (nYears > 2) 35 else 0,
        hjust = if (nYears > 2) 1 else 0.5
      ),
      plot.margin = margin(5, 10, 5, 5, "mm")
    )
}

# ---------------------------------------------------------------------------
# Period text for header
# ---------------------------------------------------------------------------
auditPeriodText <- paste0(
  format(auditStart, "%e %b %Y"), " -- ", format(auditEnd, "%e %b %Y"),
  " (", round(as.numeric(difftime(auditEnd, auditStart, units = "weeks")) / 52 * 12, 1), " month period)"
)
```

**Audit Generated on:** `r format(Sys.time(), "%a %b %d %X %Y")`<br>
**Audit Period:** `r format(audit_start_date, "%d %B %Y")` – `r format(audit_end_date, "%d %B %Y")`<br>
**Organs included in audit:** `r paste(audit_organs)`<br>
**Years in audit:** `r paste(yearLabels, collapse = ", ")`<br>

## Ablation Referral to DTT Times

```{r ref_dtt_table}
generateDTTTable <- function(doneData) {
  doneData |>
    mutate(Ref_DTT = if_else(Ref_DTT < 0, NA_real_, Ref_DTT)) |>
    mutate(
      within10 = ifelse(Ref_DTT <= 10, 1, 0),
      within21 = ifelse(Ref_DTT <= 21, 1, 0)
    ) |>
    overall_group("Organs") |>
    summarise(
      mean    = round(mean(Ref_DTT, na.rm = TRUE), 1),
      median  = round(median(Ref_DTT, na.rm = TRUE), 1),
      w10     = sum(within10, na.rm = TRUE),
      w21     = sum(within21, na.rm = TRUE),
      "w10%"  = round(sum(within10, na.rm = TRUE) / n() * 100, 1),
      "w21%"  = round(sum(within21, na.rm = TRUE) / n() * 100, 1),
      n = n()
    ) |>
    mutate(Organs = if_else(is.na(Organs), "All Organs", Organs)) |>
    ungroup() |>
    filter(Organs == "All Organs" | Organs %in% audit_organs)
}

if (nYears == 1) {
  # Single year: original simple table
  generateDTTTable(rxDoneAuditData) |>
    mutate(`Organ Treated` = paste0(Organs, " (N=", n, ")")) |>
    select(`Organ Treated`, mean, median, `w10%`, `w21%`) |>
    kbl(col.names = c("Organ Treated", "Mean time\n(days)", "Median\n(days)",
                      "% within 10 days\n(Local std.)", "% within 21 days\n(Local std.)")) |>
    add_header_above(data.frame(paste0("Time from Referral Received-to-DTT\n", auditPeriodText), 5)) |>
    kable_styling(bootstrap_options = c("striped","condensed","responsive"), full_width = TRUE)
} else {
  # Multi-year: build wide comparison table
  dttMulti <- buildMultiYearTable(
    summarise_fn = generateDTTTable,
    pct_cols     = c("w10%", "w21%"),
    count_cols   = c("w10",  "w21"),
    raw_col      = "Ref_DTT"
  )

  # Select display columns in year order
  display_cols <- c("Organ Treated",
    unlist(lapply(yearLabels, function(lbl) c(
      paste0("n_", lbl),
      paste0("mean_", lbl), paste0("median_", lbl),
      paste0("w10%_", lbl), paste0("w21%_", lbl)
    )))
  )
  
  col_headers <- c("Organ Treated",
    rep(c("N", "Mean\n(days)", "Median\n(days)", "% <=10 days", "% <=21 days"), nYears))
  
  span_headers <- c(setNames(1, " "), setNames(rep(5, nYears), yearLabels))

  dttMulti |>
    select(any_of(display_cols)) |>
    kbl(col.names = col_headers) |>
    add_header_above(span_headers) |>
    add_header_above(c("Time from Referral Received-to-DTT" = length(col_headers))) |>

    kable_styling(bootstrap_options = c("striped","condensed","responsive"), font_size = 9, full_width = TRUE) |>
    add_year_separators(5, nYears)
}
```

Mean, median (days) and percentage of referrals meeting defined time standards. Numbers in brackets show the preceding year's values. * t-test significant difference vs preceding year. + z-test significant difference vs preceding year.

```{r ref_dtt_boxplot, warning=FALSE}
buildMultiYearBoxplot(
  value_col = "Ref_DTT",
  title_str = "Time from Referral Received-to-DTT",
  ylab_str  = "Days",
  hlines    = list(
    list(y = 10, color = "orange"),
    list(y = 21, color = "red")
  )
)
```

## Ablation DTT to Rx Times

```{r dtt_rx_table}
generateDTTtoRxTable <- function(doneData) {
  doneData |>
    mutate(DTT_Rx = if_else(DTT_Rx < 0, NA_real_, DTT_Rx)) |>
    mutate(
      within31 = ifelse(DTT_Rx <= 31, 1, 0),
      within45 = ifelse(DTT_Rx <= 45, 1, 0),
      within60 = ifelse(DTT_Rx <= 60, 1, 0)
    ) |>
    overall_group("Organs") |>
    summarise(
      mean    = round(mean(DTT_Rx, na.rm = TRUE), 1),
      median  = round(median(DTT_Rx, na.rm = TRUE), 1),
      w31     = sum(within31, na.rm = TRUE),
      w45     = sum(within45, na.rm = TRUE),
      w60     = sum(within60, na.rm = TRUE),
      "w31%"  = round(sum(within31, na.rm = TRUE) / n() * 100, 1),
      "w45%"  = round(sum(within45, na.rm = TRUE) / n() * 100, 1),
      "w60%"  = round(sum(within60, na.rm = TRUE) / n() * 100, 1),
      n = n()
    ) |>
    mutate(Organs = if_else(is.na(Organs), "All Organs", Organs)) |>
    ungroup() |>
    filter(Organs == "All Organs" | Organs %in% audit_organs)
}

if (nYears == 1) {
  generateDTTtoRxTable(rxDoneAuditData) |>
    mutate(`Organ (n)` = paste0(Organs, " (N=", n, ")")) |>
    select(`Organ (n)`, mean, median, `w31%`, `w45%`, `w60%`) |>
    kbl(col.names = c("Organ Treated", "Mean time\n(days)", "Median\n(days)",
                      "% within 31 days\n(Cancer std.)", "% within 45 days\n(Local std.)",
                      "% within 60 days\n(Local std.)")) |>
    add_header_above(data.frame(paste0("Time from DTT-to-Ablation\n", auditPeriodText), 6)) |>
    kable_styling(bootstrap_options = c("striped","condensed","responsive"), font_size = 9, full_width = TRUE) |>
    add_year_separators(6, nYears)
} else
{
  dttRxMulti <- buildMultiYearTable(
    summarise_fn = generateDTTtoRxTable,
    pct_cols     = c("w31%", "w45%", "w60%"),
    count_cols   = c("w31",  "w45",  "w60"),
    raw_col      = "DTT_Rx"
  )

  display_cols <- c("Organ Treated",
    unlist(lapply(yearLabels, function(lbl) c(
      paste0("n_", lbl),
      paste0("mean_", lbl), paste0("median_", lbl),
      paste0("w31%_", lbl), paste0("w45%_", lbl), paste0("w60%_", lbl)
    )))
  )
  
  col_headers  <- c("Organ Treated",
    rep(c("N", "Mean\n(days)", "Median\n(days)", "% <=31 days", "% <=45 days", "% <=60 days"), nYears))
  span_headers <- c(setNames(1, " "), setNames(rep(6, nYears), yearLabels))

  dttRxMulti |>
    select(any_of(display_cols)) |>
    kbl(col.names = col_headers) |>
    add_header_above(span_headers) |>
    add_header_above(c("Time from DTT-to-Ablation" = length(col_headers))) |>
    kable_styling(bootstrap_options = c("striped","condensed","responsive"), font_size = 9, full_width = TRUE) |>
    add_year_separators(4, nYears)
}
```

Mean, median (days) and percentage of referrals meeting defined time standards from the decision to treat clinic date (DTT) and the day of ablation treatment.

```{r dtt_rx_boxplot, warning=FALSE}
buildMultiYearBoxplot(
  value_col = "DTT_Rx",
  title_str = "Time from DTT-to-Ablation",
  ylab_str  = "Days",
  hlines    = list(
    list(y = 31, color = "orange"),
    list(y = 45, color = "red"),
    list(y = 60, color = "darkred")
  )
)
```

## Ablation Referral to Rx Times

```{r ref_rx_table}
generateRefToRxTable <- function(doneData) {
  doneData |>
    mutate(Ref_RxDone = if_else(Ref_RxDone < 0, NA_real_, Ref_RxDone)) |>
    mutate(within90 = ifelse(Ref_RxDone <= 90, 1, 0)) |>
    overall_group("Organs") |>
    summarise(
      mean   = round(mean(Ref_RxDone, na.rm = TRUE), 1),
      median = round(median(Ref_RxDone, na.rm = TRUE), 1),
      w90    = sum(within90, na.rm = TRUE),
      "w90%" = round(sum(within90, na.rm = TRUE) / n() * 100, 1),
      n = n()
    ) |>
    mutate(Organs = if_else(is.na(Organs), "All Organs", Organs)) |>
    ungroup() |>
    filter(Organs == "All Organs" | Organs %in% audit_organs)
}

if (nYears == 1) {
  generateRefToRxTable(rxDoneAuditData) |>
    mutate(`Organ (n)` = paste0(Organs, " (N=", n, ")")) |>
    select(`Organ (n)`, mean, median, `w90%`) |>
    kbl(col.names = c("Organ Treated", "Mean time\n(days)", "Median\n(days)",
                      "% within 90 days\n(Local std.)")) |>
    add_header_above(data.frame(paste0("Time from Referral received-to-Ablation\n", auditPeriodText), 4)) |>
    kable_styling(bootstrap_options = c("striped","condensed","responsive"), full_width = TRUE)
} else {
  refRxMulti <- buildMultiYearTable(
    summarise_fn = generateRefToRxTable,
    pct_cols     = c("w90%"),
    count_cols   = c("w90"),
    raw_col      = "Ref_RxDone"
  )

  display_cols <- c("Organ Treated",
    unlist(lapply(yearLabels, function(lbl) c(
      paste0("n_", lbl),
      paste0("mean_", lbl), paste0("median_", lbl), paste0("w90%_", lbl)
    )))
  )
  
  col_headers  <- c("Organ Treated", rep(c("N", "Mean\n(days)", "Median\n(days)", "% <=90 days"), nYears))
  span_headers <- c(setNames(1, " "), setNames(rep(4, nYears), yearLabels))

  refRxMulti |>
    select(any_of(display_cols)) |>
    kbl(col.names = col_headers) |>
    add_header_above(span_headers) |>
    add_header_above(c("Time from Referral received-to-Ablation" = length(col_headers))) |>
    kable_styling(bootstrap_options = c("striped","condensed","responsive"), font_size = 9, full_width = TRUE)
}
```

Mean, median (days) and percentage of referrals meeting defined time standard from the referral received date to treatment date overall.

```{r ref_rx_boxplot, warning=FALSE}
buildMultiYearBoxplot(
  value_col = "Ref_RxDone",
  title_str = "Time from Referral received-to-Ablation",
  ylab_str  = "Days",
  hlines    = list(list(y = 90, color = "red"))
)
```

* Numbers in brackets represent the results in the preceding year
* \* Significant difference vs preceding year (t-test)
* + Significant difference vs preceding year (z-test for proportions)

## Clock Stops causing negative Referral to DTT and DTT to Rx times

```{r negative_clockstop}
rxDoneAuditData |>
  filter(Ref_DTT < 0 | DTT_Rx < 0) |>
  select(ID, Organs, Ref_DTT, DTT_Rx, ClockStopDaysPreDTT, ClockStopDaysPostDTT) |>
  kbl(col.names = c("ID", "Organ Treated", "Referral to DTT\n(days)", "DTT to Rx\n(days)",
                    "Clock Stop Pre DTT\n(days)", "Clock Stop Post DTT\n(days)")) |>
  kable_styling(bootstrap_options = c("striped","condensed","responsive"), full_width = FALSE) |>
  column_spec(1, width = "12em")
```

## Ablation Referral Days Stopped (Pre- or Post-DTT)

```{r daystopped_pre_or_post_dtt}
rxDoneAuditData |>
  mutate(
    clockstopped = if_else(
      is.na(ClockStopDaysPreDTT),
      if_else(is.na(ClockStopDaysPostDTT), "Not Stopped", "Stopped Post DTT"),
      if_else(is.na(ClockStopDaysPostDTT), "Stopped Pre DTT", "Stopped Both Pre and Post DTT")
    ),
    daysStopped = if_else(
      is.na(ClockStopDaysPreDTT),
      if_else(is.na(ClockStopDaysPostDTT), 0, abs(ClockStopDaysPostDTT)),
      if_else(is.na(ClockStopDaysPostDTT), abs(ClockStopDaysPreDTT),
              abs(ClockStopDaysPreDTT + ClockStopDaysPostDTT))
    )
  ) |>
  group_by(clockstopped) |>
  mutate(n = n(), clockstopped = paste0(clockstopped, " (N=", n, ")")) |>
  summarise(mean = round(mean(daysStopped), 1), median = round(median(daysStopped), 1)) |>
  kbl(col.names = c("Clock Status", "Mean time\n(days)", "Median\n(days)")) |>
  kable_styling(bootstrap_options = c("striped","condensed","responsive"), full_width = TRUE) |>
  column_spec(1, width = "30em") |>
  column_spec(2, width = "8em") |>
  column_spec(3, width = "8em")

```{r daystopped_pre_and_post_dtt}
rxDoneAuditData |>
  mutate(
    clockstopped = if_else(
      is.na(ClockStopDaysPreDTT) & is.na(ClockStopDaysPostDTT), "Not Stopped", "Stopped"
    ),
    daysStopped = if_else(
      is.na(ClockStopDaysPreDTT),
      if_else(is.na(ClockStopDaysPostDTT), 0, abs(ClockStopDaysPostDTT)),
      if_else(is.na(ClockStopDaysPostDTT), abs(ClockStopDaysPreDTT),
              abs(ClockStopDaysPreDTT + ClockStopDaysPostDTT))
    )
  ) |>
  group_by(clockstopped) |>
  mutate(n = n(), clockstopped = paste0(clockstopped, " (N=", n, ")")) |>
  summarise(mean = round(mean(daysStopped), 1), median = round(median(daysStopped), 1)) |>
  kbl(col.names = c("Clock Status", "Mean time\n(days)", "Median\n(days)")) |>
  kable_styling(bootstrap_options = c("striped","condensed","responsive"), full_width = TRUE) |>
  column_spec(1, width = "30em") |>
  column_spec(2, width = "8em") |>
  column_spec(3, width = "8em")

```{r clockstop}
rxDoneAuditData |>
  mutate(
    clockstopped = if_else(
      is.na(ClockStopDaysPreDTT),
      if_else(is.na(ClockStopDaysPostDTT), "Not Stopped", "Stopped Post DTT"),
      if_else(is.na(ClockStopDaysPostDTT), "Stopped Pre DTT", "Stopped Both Pre and Post DTT")
    )
  ) |>
  filter(clockstopped != "Not Stopped") |>
  select(ID, Organs, ClockStopWhy) |>
  kbl(col.names = c("ID", "Organ", "Reason for clock stop")) |>
  kable_styling(bootstrap_options = c("striped","condensed","responsive"), full_width = FALSE) |>
  column_spec(1, width = "8em") |>
  column_spec(2, width = "8em") |>
  column_spec(3, width = "60em")
```

## Time to Treatment Plot

```{r ttt_plot}
rxDoneAuditDataplot <- commonRxDonePlot(rxDoneAuditData) +
  ggtitle("Time to Treatment")
rxDoneAuditDataplot
```

## Organ Treatment Piechart

```{r organ_pie}
rxDoneAuditData %>%
  group_by(Organs) %>%
  summarise(n = n()) %>%
  mutate(
    prop   = n / sum(.$n) * 100,
    ypos   = cumsum(prop) - 0.5 * prop,
    Organs = paste0(Organs, " (N=", n, ")")
  ) %>%
  ggplot(aes(x = "", y = n, fill = Organs)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +
  scale_fill_brewer(palette = "Set1", name = "Tumour Type")
```

## Wait time plots

```{r wait_time_plots, warning=FALSE}
referralTimes <- processWaitTimesPerPeriod(
  rxDoneAuditData, rxWaitAuditData,
  audit_start_date, audit_end_date, "month"
)
```

```{r refToDTTMeanPlot, warning=FALSE}
refToDTTMeanPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
refToDTTCountPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
```

```{r dttToRxMeanPlot, warning=FALSE}
dttToRxMeanPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
dttToRxCountPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
```

```{r refToRxMeanPlot, warning=FALSE}
refToRxMeanPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
refToRxCountPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
```

## Long waits

```{r longwaits}
rxDoneAuditData %>%
  filter(Ref_RxDone > 120) %>%
  mutate(
    ClockStopDaysPreDTT  = if_else(is.na(ClockStopDaysPreDTT),  0, ClockStopDaysPreDTT),
    ClockStopDaysPostDTT = if_else(is.na(ClockStopDaysPostDTT), 0, ClockStopDaysPostDTT)
  ) %>%
  select(ID, Organs, Ref_RxDone, ClockStopDaysPreDTT, ClockStopDaysPostDTT) %>%
  kbl(col.names = c("ID", "Organ", "Referral to Ablation time\n(days)",
                    "Clock Stop Pre DTT\n(days)", "Clock Stop Post DTT\n(days)")) %>%
  kable_styling(
    bootstrap_options = c("striped","condensed","responsive"),
    full_width = TRUE
  ) |>
  column_spec(2, width = "10em")
```

## Credits

```{r reportLogo, warning=FALSE}
logo_src <- here("www", "TARGETPlotterLogo.png")
if (file.exists(logo_src)) {
  knitr::include_graphics(normalizePath(logo_src))
} else {
  cat("<!-- TARGETPlotterLogo.png logo not available -->")
}
```

<br>
Audit Report Developers: Dr. Andrew Thornton, Dr. Paul Lyon<br>
TARGET-UK Lead: Dr. Paul Lyon, FRCR

