---
title: "TARGET-UK: Ablation Waiting Time Audit Report"
output:
  html_document:
    toc: true
    self_contained: true
date: "`r format(Sys.Date(), '%d %B %Y')`"
params:
  audit_start_date: !r Sys.Date() - 365
  audit_end_date: !r Sys.Date()
  audit_financial_year: FALSE
  audit_primary_cancers_only: FALSE
  audit_split_primary_secondary: TRUE
  audit_organs: ["Liver", "Lung", "Kidney", "Adrenal", "Other"]
  audit_rx_pathway_anonymised: TRUE
---

```{css, echo=FALSE}
/* Screen and print shared */
body { font-size: 14px; }
table { 
  font-size: 13px; 
  width: 100% !important;
  table-layout: auto;
}
th, td { 
  padding: 4px 8px !important;
  font-size: 13px;
}
img { max-width: 100% !important; height: auto !important; }

/* Print-specific: force landscape and control margins */
@media print {
  @page { 
    size: A4 portrait;
    margin: 8mm 6mm 8mm 6mm;
  }
  body { 
    font-size: 11px;
    width: 198mm;
  }
  table {
    font-size: 10px;
    page-break-inside: avoid;
    table-layout: auto;
  }
  th, td { padding: 2px 4px !important; font-size: 10px; }
  img, .plot { 
    max-width: 196mm !important; 
    width: 196mm !important;
    height: auto !important;
    page-break-inside: avoid;
  }
  .figure { 
    max-width: 196mm !important;
    page-break-inside: avoid;
  }
  h2 { page-break-before: auto; }
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(fig.width = 10, fig.height = 5, dpi = 120)
options(knitr.table.format = "html")
library(dplyr)
library(lubridate)
library(purrr)
library(kableExtra)

audit_start_date      <- params$audit_start_date
audit_end_date        <- params$audit_end_date
audit_financial_year  <- isTRUE(params$audit_financial_year)
splitPrimarySecondary <- isTRUE(params$audit_split_primary_secondary)
audit_organs          <- params$audit_organs
reportAnonymised      <- isTRUE(params$audit_rx_pathway_anonymised)

auditStart <- as.Date(audit_start_date)
auditEnd   <- as.Date(audit_end_date)

audit_primary_cancers_only <- isTRUE(params$audit_primary_cancers_only)


# ---------------------------------------------------------------------------
# Build a list of annual windows covering the audit period.
# Each window is exactly one calendar year. The final window is the audit
# period itself (which may be < 1 year); all preceding windows are the
# same-length year immediately before the next window, with no overlap.
#
# If the year start date is not the financial year
# E.g. audit 1 Jan 2021 -- 31 Dec 2023 produces:
#   Year 1: 2021-01-01 -- 2021-12-31
#   Year 2: 2022-01-01 -- 2022-12-31
#   Year 3: 2023-01-01 -- 2023-12-31
# ---------------------------------------------------------------------------
buildYearWindows <- function(start, end, financial_year = FALSE) {

  windows <- list()
  current <- start

  while (current <= end) {

    if (isTRUE(financial_year)) {

      # First boundary after current date
      year <- as.integer(format(current, "%Y"))
      fy_start_this_year <- as.Date(paste0(year, "-04-06"))

      next_start <- if (current < fy_start_this_year) {
        fy_start_this_year
      } else {
        as.Date(paste0(year + 1, "-04-06"))
      }

      window_end <- min(next_start - days(1), end)

      yr_label <- paste0(
        format(current, "%Y"),
        "/",
        format(window_end, "%Y")
      )

    } else {

      year <- as.integer(format(current, "%Y"))
      next_start <- as.Date(paste0(year + 1, "-01-01"))

      window_end <- min(next_start - days(1), end)

      yr_label <- format(current, "%Y")
    }

    windows <- append(
      windows,
      list(list(
        label = yr_label,
        start = current,
        end = window_end
      ))
    )

    current <- window_end + days(1)
  }

  windows
}

buildYearWindows.old <- function(start, end, financial_year = FALSE) {
  windows <- list()

  if (isTRUE(financial_year)) {
    # Anchor the first window to 6 April on/before the audit start date,
    # so every subsequent window naturally falls on 6 Apr - 5 Apr boundaries
    fyStartThisCalYear <- as.Date(paste0(format(start, "%Y"), "-04-06"))
    current <- if (start >= fyStartThisCalYear) {
      fyStartThisCalYear
    } else {
      as.Date(paste0(as.integer(format(start, "%Y")) - 1, "-04-06"))
    }
  } else {
    current <- start
  }

  while (current < end) {
    window_end <- min(current + years(1) - days(1), end)
    yr_label   <- format(current, "%Y")
    # If window spans two calendar years use a range label
    if (format(current, "%Y") != format(window_end, "%Y")) {
      yr_label <- paste0(format(current, "%Y"), "/", format(window_end, "%Y"))
    }
    windows <- append(windows, list(list(
      label = yr_label,
      start = current,
      end   = window_end
    )))
    current <- window_end + days(1)
  }
  windows
}

yearWindows <- buildYearWindows(auditStart, auditEnd, audit_financial_year)
yearLabels  <- sapply(yearWindows, `[[`, "label")
nYears      <- length(yearWindows)
yearBasisText <- if (audit_financial_year) "Financial Year (6 Apr\u20135 Apr)" else "Calendar Year (1 Jan\u201331 Dec)"

# ---------------------------------------------------------------------------
# Helper: overall_group -- adds an "All Organs" summary row
# ---------------------------------------------------------------------------

overall_group <- function(data, col_name) {

  grouped <- data |>
    group_by(!!sym(col_name)) |>
    mutate(summary_level = "grouped")

  all_organs <- data |>
    mutate(
      !!sym(col_name) := "All Organs",
      summary_level = "ungrouped"
    )

  bind_rows(grouped, all_organs)
}

add_year_separators <- function(kable, cols)
{
  n_positions <- grep("^n_", cols)
  for (pos in n_positions) {
    kable <- column_spec(
      kable,
      pos,
      extra_css = "border-left:1px solid #666;"
    )
  }
  kable
}

# ---------------------------------------------------------------------------
# Remove dummy patients and apply organ filter once, producing a clean base
# data frame, then split into per-year slices.
# ---------------------------------------------------------------------------
cleanBase <- function(data) {

  d <- data |>
    filter(!(ID %in% c("000-1", "00000-1", "000000-1")))

  if (!("All" %in% audit_organs)) {
    d <- d |> filter(Organ %in% audit_organs)
  }

  if (audit_primary_cancers_only && "DiagnosisType" %in% names(d)) {
    d <- d |> filter(DiagnosisType == "P")
  }

  # Split selected organs by diagnosis type
  if (isTRUE(splitPrimarySecondary) &&
      "DiagnosisType" %in% names(d)) {
  
    d <- d |>
      mutate(
        Organ = paste0(
          Organ,
          case_when(
            DiagnosisType == "P" ~ "-Primary",
            DiagnosisType == "S" ~ "-Secondary",
            DiagnosisType == "B" ~ "-Benign",
            DiagnosisType == "U" ~ "-Unknown",
            TRUE ~ ""
          )
        )
      )
  }
  
  d
}

rxWaitClean <- cleanBase(rxWaitData)
rxDoneClean <- cleanBase(rxDoneData)

# Organs after optional Primary/Secondary splitting
table_organs <- sort(unique(rxDoneClean$Organ))

# List of per-year data frames
rxDoneByYear <- lapply(yearWindows, function(w) {
  rxDoneClean |> filter(RxDate >= w$start & RxDate <= w$end)
})
names(rxDoneByYear) <- yearLabels

# For wait-time plots we still need the full audit-period data frame
rxDoneAuditData    <- bind_rows(rxDoneByYear)
rxWaitAuditData    <- rxWaitClean

if (reportAnonymised)
{
  if (reportAnonymised) {
    rxDoneAuditData <- rxDoneAuditData |>
      mutate(ID = anonymise_ptid(ID))
  
    rxWaitAuditData <- rxWaitAuditData |>
      mutate(ID = anonymise_ptid(ID))
  }
}

# ---------------------------------------------------------------------------
# Significance testing helpers
# Both now accept explicit data frames rather than relying on globals
# ---------------------------------------------------------------------------
t.significantMarker <- function(p.value) {
  if (is.na(p.value)) "" else if (p.value < 0.05) " *" else ""
}

z.significantMarker <- function(p.value) {
  if (is.na(p.value)) "" else if (p.value < 0.05) " +" else ""
}

getTTestPValueFromData <- function(current_data, preceding_data, organ, column) {
  tryCatch({
    x <- current_data   |> filter(organ == "All Organs" | Organ == organ) |> pull(!!sym(column))
    y <- preceding_data |> filter(organ == "All Organs" | Organ == organ) |> pull(!!sym(column))
    t.test(x, y)$p.value |> t.significantMarker()
  }, error = function(e) "")
}

getZTestPValueFromTables <- function(current_tbl, preceding_tbl, organ, count_col, n_col = "n") {
  tryCatch({
    prop.test(
      x = c(current_tbl[current_tbl$Organ == organ, count_col],
            preceding_tbl[preceding_tbl$Organ == organ, count_col]),
      n = c(current_tbl[current_tbl$Organ == organ, n_col],
            preceding_tbl[preceding_tbl$Organ == organ, n_col])
    )$p.value |> z.significantMarker()
  }, error = function(e) "")
}

# ---------------------------------------------------------------------------
# Generic multi-year table builder.
#
# summarise_fn : function(data_frame) -> summary tibble with columns
#                Organ, n, mean, median, and any percentage columns
# pct_cols     : character vector of percentage column names e.g. c("w10%","w21%")
# count_cols   : corresponding raw count column names for z-test e.g. c("w10","w21")
# raw_col      : column name in the raw data for the t-test e.g. "Ref_DTT"
# ---------------------------------------------------------------------------
buildMultiYearTable <- function(summarise_fn, pct_cols, count_cols, raw_col) {
  # Build per-year summary tables
  yr_tables <- lapply(rxDoneByYear, summarise_fn)

  # All organs + individual organ rows to test
  organs_to_test <- c(table_organs, "All Organs")

  # First column totals — must use the date-filtered audit data, not the
  # unfiltered full-history rxDoneClean, or the headline N will include
  # referrals from outside the audit period entirely.
  overall_counts <- rxDoneAuditData |>
    mutate(
      !!raw_col := if_else(.data[[raw_col]] < 0,
                           NA_real_,
                           .data[[raw_col]])
    ) |>
    group_by(Organ) |>
    summarise(
      total_n = sum(!is.na(.data[[raw_col]])),
      .groups = "drop"
    ) |>
    bind_rows(
      rxDoneAuditData |>
        mutate(
          !!raw_col := if_else(.data[[raw_col]] < 0,
                               NA_real_,
                               .data[[raw_col]])
        ) |>
        summarise(
          Organ = "All Organs",
          total_n = sum(!is.na(.data[[raw_col]]))
        )
    )

  result <- NULL
    
  for (i in seq_along(yearWindows))
  {
    lbl <- yearLabels[i]
    cur_tbl <- yr_tables[[i]]
    prev_tbl <- if (i > 1) yr_tables[[i-1]] else NULL
  
    add <- cur_tbl |>
      select(Organ, n, mean, sd, median, all_of(pct_cols)) |>
      mutate(
        !!paste0("n_", lbl) := paste0("N=", n),
        !!paste0("mean_", lbl) := paste0(
          mean,
          if (i > 1) {
            sapply(Organ, function(org)
              getTTestPValueFromData(
                rxDoneByYear[[i]],
                rxDoneByYear[[i-1]],
                org,
                raw_col
              )
            )
          } else "",
          " (SD=", sd, ")"
        ),
        !!paste0("median_", lbl) := median
      )
  
    for (pc in pct_cols) {
      add <- add |>
        mutate(
          !!paste0(pc, "_", lbl) := .data[[pc]]
        )
    }
  
    add <- add |>
      select(
        Organ,
        starts_with("n_"),
        starts_with("mean_"),
        starts_with("median_"),
        ends_with(lbl)
      )
  
    if (is.null(result)) {
      result <- add
    } else {
      result <- result |> left_join(add, by = "Organ")
    }
  }
  result <- result |>
    left_join(overall_counts, by = "Organ") |>
    mutate(
      `Organ Treated` = paste0(Organ, " (N=", total_n, ")")
    ) |>
    select(`Organ Treated`, everything())
  
  result |> filter(Organ == "All Organs" | Organ %in% table_organs)
}

# ---------------------------------------------------------------------------
# Generic multi-year boxplot builder
# ---------------------------------------------------------------------------
buildMultiYearBoxplot <- function(value_col, title_str, ylab_str, hlines = list()) {
  
  combined <- bind_rows(lapply(seq_along(yearWindows), function(i) {
    rxDoneByYear[[i]] |>
      select(Organ, !!sym(value_col)) |>
      mutate(
        Organ = factor(Organ),
        Year = factor(yearLabels[i], levels = yearLabels),
        !!sym(value_col) := if_else(!!sym(value_col) < 0,
                                    NA_real_,
                                    !!sym(value_col))
      )
  }))

  # Position dodge used later
  dodge_width <- 0.8
  pd <- position_dodge(width = dodge_width) 
  
  p <- ggplot(
    combined,
    aes(
      x = Organ,
      y = .data[[value_col]],
      colour = Year
    )
  ) +
  geom_boxplot(position = pd) +
  labs(
    colour = if (audit_financial_year)
      "Financial Year"
    else
      "Calendar Year"
  )
    
  # Extract actual boxplot positions and heights
  # N and mean labels
  counts <- combined |>
    filter(!is.na(.data[[value_col]])) |>
    group_by(Organ, Year) |>
    summarise(
      N = n(),
      meanVal = mean(.data[[value_col]], na.rm = TRUE),
      box_top = quantile(.data[[value_col]], 0.75, na.rm = TRUE),
      .groups = "drop"
    ) |>
    mutate(
      label = sprintf("N=%d (%.1f)", N, meanVal)
    )
  
  # One common height for ALL labels: highest box in entire plot
  global_top <- max(counts$box_top, na.rm = TRUE)
  
  counts <- counts |>
    mutate(
      y = min(combined[[value_col]], na.rm = TRUE) -
          0.30 * diff(range(combined[[value_col]], na.rm = TRUE))
    )
  
  # Match the dodged x position of each year
  nYears <- length(yearLabels)
  
  label_shift <- -0.10   # move labels left; adjust this value
  
  box_width <- dodge_width / nYears
  
  # Match actual geom_boxplot dodge positions
  nYears <- length(yearLabels)

  counts <- counts |>
  mutate(
    y = min(combined[[value_col]], na.rm = TRUE) -
        0.30 * diff(range(combined[[value_col]], na.rm = TRUE))
  )
  
  # actual geom_boxplot default width
  box_width <- 0.75 * (dodge_width / nYears)
  
  counts <- counts |>
    group_by(Organ) |>
    mutate(
      nYearsHere = n(),
      year_num = row_number(),
      organ_num = as.numeric(Organ),
  
      box_width = dodge_width / nYearsHere,
  
      box_centre = organ_num - dodge_width/2 +
        (year_num - 0.5) * (dodge_width/nYearsHere),
  
      x_label = box_centre - (0.75 * box_width)/2 + 0.03
    ) |>
    ungroup()
  
  counts <- counts |>
    mutate(
      Year = factor(Year, levels = yearLabels)
    )
  
  p <- p +
    geom_text(
      data = counts,
      aes(
        x = x_label,
        y = y,
        label = label
      ),
      angle = 90,
      size = 3.2,
      colour = "black",
      inherit.aes = FALSE,
      hjust = 0,
      vjust = 0.5
    ) +
    labs(
      colour = if (audit_financial_year)
        "Financial Year"
      else
        "Calendar Year"
  )

  for (h in hlines) {
    p <- p +
      geom_hline(yintercept = h$y,
                 linetype = "dashed",
                 colour = h$color)
  }

  auditPeriodText <- paste0(
    format(auditStart, "%e %b %Y"),
    " -- ",
    format(auditEnd, "%e %b %Y")
  )

  p +
    ggtitle(paste0(title_str, " (", yearBasisText, ")\n", auditPeriodText)) +
    labs(y = ylab_str, x = "Organ Treated") +
    scale_color_brewer(palette = "Set1") +
    scale_y_continuous(expand = expansion(mult = c(0.15, 0.05))) +
    coord_cartesian(clip = "off") +
    theme(
      legend.position = "bottom",
      axis.text.x = element_text(
        angle = if (nYears > 2) 35 else 0,
        hjust = if (nYears > 2) 1 else 0.5
      ),
      plot.margin = margin(15, 10, 25, 10)
    )
}

# ---------------------------------------------------------------------------
# Period text for header
# ---------------------------------------------------------------------------
auditPeriodText <- paste0(
  format(auditStart, "%e %b %Y"), " -- ", format(auditEnd, "%e %b %Y"),
  " (", round(as.numeric(difftime(auditEnd, auditStart, units = "weeks")) / 52 * 12, 1), " month period)"
)

missing_date_legend.old <- function(data, date_col, label) {

  missing_ids <- data |>
    filter(is.na(.data[[date_col]])) |>
    pull(ID) |>
    unique()

  if (length(missing_ids) == 0) {
    return("")
  }

  paste0(
    "<br><br><strong>Missing ",
    label,
    " date (N=",
    length(missing_ids),
    "):</strong> ",
    paste(missing_ids, collapse = ", ")
  )
}

missing_date_legend_by_organ <- function(data, date_col, label_prefix = "Missing Dates:") {

  missing <- data |>
    filter(is.na(.data[[date_col]])) |>
    select(ID, Organ)

  if (nrow(missing) == 0) {
    return(NULL)
  }

  legend_text <- missing |>
    group_by(Organ) |>
    summarise(
      TreatmentIDs = paste(ID, collapse = ", "),
      N = n(),
      .groups = "drop"
    ) |>
    mutate(
      legend = paste0(
        Organ,
        " (N=",
        N,
        "): ",
        TreatmentIDs
      )
    ) |>
    pull(legend)

  paste(
    c(
      label_prefix,
      legend_text
    ),
    collapse = "\n"
  )
}

# Companion to missing_date_legend_by_organ() -- reports rows where value_col
# is *present but negative* (a dating error e.g. Rx before referral, DTT
# before referral), rather than genuinely missing. These are treated as
# invalid/excluded data throughout the wait-time tables (NA'd, not zeroed),
# so they must be surfaced here for transparency, in the same style as the
# missing-date legend above.
negative_value_legend_by_organ <- function(data, value_col, label_prefix = "Excluded (negative dates):") {

  negative <- data |>
    filter(!is.na(.data[[value_col]]) & .data[[value_col]] < 0) |>
    select(ID, Organ)

  if (nrow(negative) == 0) {
    return(NULL)
  }

  legend_text <- negative |>
    group_by(Organ) |>
    summarise(
      TreatmentIDs = paste(ID, collapse = ", "),
      N = n(),
      .groups = "drop"
    ) |>
    mutate(
      legend = paste0(
        Organ,
        " (N=",
        N,
        "): ",
        TreatmentIDs
      )
    ) |>
    pull(legend)

  paste(
    c(
      label_prefix,
      legend_text
    ),
    collapse = "\n"
  )
}

# Combines the missing-date and negative-value legends into a single
# footnote string, so both exclusion reasons appear together under each
# table. Returns NULL only if there is nothing to report at all.
wait_time_exclusion_footnote <- function(data, value_col, missing_label, negative_label) {
  parts <- c(
    missing_date_legend_by_organ(data, value_col, missing_label),
    negative_value_legend_by_organ(data, value_col, negative_label)
  )
  parts <- parts[!vapply(parts, is.null, logical(1))]
  if (length(parts) == 0) return(NULL)
  paste(parts, collapse = "\n\n")
}
```

**Audit Generated on:** `r format(Sys.time(), "%a %b %d %X %Y")`<br>
**Audit Period:** `r format(audit_start_date, "%d %B %Y")` – `r format(audit_end_date, "%d %B %Y")`<br>
**Organ included in audit:** `r paste(audit_organs, collapse = ", ")`<br>
**Primary cancers only:** `r if (audit_primary_cancers_only) "Yes" else "No"`<br>
**Split primary/secondary cancers:** `r if (splitPrimarySecondary) "Yes" else "No"`<br>
**Organs included:** `r paste(audit_organs, collapse = ", ")`<br>**Year basis:** `r yearBasisText`<br>
**Years in audit:** `r paste(yearLabels, collapse = ", ")`<br>

## Audit Summary

```{r audit_summary, results='asis'}
summaryData <- rxDoneAuditData |>
  mutate(
    Ref_DTT    = if_else(Ref_DTT    < 0, NA_real_, Ref_DTT),
    DTT_Rx     = if_else(DTT_Rx     < 0, NA_real_, DTT_Rx),
    Ref_RxDone = if_else(Ref_RxDone < 0, NA_real_, Ref_RxDone)
  )

n_patients  <- as.integer(summaryData |>
  mutate(PtID = sub("-[0-9]+$", "", ID)) |>
  pull(PtID) |>
  dplyr::n_distinct())

n_referrals_total <- as.integer(nrow(summaryData))

n_referrals_valid_ref_rx <- as.integer(
  summaryData |>
    filter(!is.na(Ref_RxDone)) |>
    nrow()
)

n_referrals_excluded <- n_referrals_total - n_referrals_valid_ref_rx

n_referrals_missing_dtt <- as.integer(summaryData |> filter(is.na(Ref_DTT)) |> nrow())

n_tumours <- if ("TumourCount" %in% names(summaryData)) {
  as.integer(sum(summaryData$TumourCount, na.rm = TRUE))
} else {
  NA_integer_
}

pct_within <- function(x, threshold) {
  x <- x[!is.na(x)]
  if (length(x) == 0) return(NA_real_)
  round(sum(x <= threshold) / length(x) * 100, 1)
}

# Build each formatted value individually, with a scalar-length guard
mk_val <- function(name, x) {
  if (length(x) != 1) {
    stop(sprintf("audit_summary: '%s' produced length %d, expected 1", name, length(x)))
  }
  x
}

val_referrals_total    <- mk_val("n_referrals_total",format(n_referrals_total, big.mark = ","))
val_referrals_valid    <- mk_val("n_referrals_valid_ref_rx",format(n_referrals_valid_ref_rx, big.mark = ","))
val_patients           <- mk_val("n_patients", format(n_patients, big.mark = ","))
val_tumours            <- mk_val("n_tumours", format(n_tumours, big.mark = ","))
val_referrals_excluded <- mk_val("n_referrals_excluded",format(n_referrals_excluded, big.mark = ","))
val_referrals_missing_dtt <- mk_val("n_referrals_missing_dtt", format(n_referrals_missing_dtt, big.mark = ","))

val_mean_refdtt <- mk_val("mean_Ref_DTT", sprintf("%.1f", mean(summaryData$Ref_DTT, na.rm = TRUE)))
val_w10        <- mk_val("w10",  sprintf("%.1f", pct_within(summaryData$Ref_DTT, 10)))
val_w21        <- mk_val("w21",  sprintf("%.1f", pct_within(summaryData$Ref_DTT, 21)))
val_mean_dttrx <- mk_val("mean_DTT_Rx",   sprintf("%.1f", mean(summaryData$DTT_Rx, na.rm = TRUE)))
val_w31        <- mk_val("w31",  sprintf("%.1f", pct_within(summaryData$DTT_Rx, 31)))
val_w45        <- mk_val("w45",  sprintf("%.1f", pct_within(summaryData$DTT_Rx, 45)))
val_w60        <- mk_val("w60",  sprintf("%.1f", pct_within(summaryData$DTT_Rx, 60)))
val_mean_refrx <- mk_val("mean_Ref_RxDone", sprintf("%.1f", mean(summaryData$Ref_RxDone, na.rm = TRUE)))
val_w90        <- mk_val("w90",  sprintf("%.1f", pct_within(summaryData$Ref_RxDone, 90)))

summary_tbl <- tibble::tibble(
  Metric = c(
    "Total Referrals Analysed",
    "Valid Referrals: Total Treatments (w/Ref + Rx Dates)",
    "Valid Referrals: Total Tumours Treated",
    "Valid Referrals: Total Patients Treated",
    "Excluded Referrals (missing Ref or Rx Date)",
    "Referrals missing DTT date",
    "Mean Referral-to-DTT (days)",
    "% Referral-to-DTT \u2264 10 days",
    "% Referral-to-DTT \u2264 21 days",
    "Mean DTT-to-Ablation (days)",
    "% DTT-to-Ablation \u2264 31 days",
    "% DTT-to-Ablation \u2264 45 days",
    "% DTT-to-Ablation \u2264 60 days",
    "Mean Referral-to-Ablation (days)",
    "% Referral-to-Ablation \u2264 90 days"
  ),
  Value = c(
    val_referrals_total, val_referrals_valid, val_tumours, val_patients,
    val_referrals_excluded, val_referrals_missing_dtt,
    val_mean_refdtt, val_w10, val_w21,
    val_mean_dttrx, val_w31, val_w45, val_w60,
    val_mean_refrx, val_w90
  )
)

summary_tbl |>
  kbl(
    col.names = c("Metric", "Value"),
    caption = paste0("Audit Headline Summary (", auditPeriodText, ")")
  ) |>
  kable_styling(
    bootstrap_options = c("striped", "condensed", "responsive"),
    full_width = FALSE
  )
```


## Ablation Referral to DTT Times

```{r ref_dtt_table}

generateDTTTable <- function(doneData) {

  # Handle completely empty year
  if (nrow(doneData) == 0) {
    return(
      tibble(
        Organ  = c("All Organs", table_organs),
        n       = 0,
        mean    = NA_real_,
        sd      = NA_real_,
        median  = NA_real_,
        w10     = 0,
        w21     = 0,
        `w10%`  = NA_real_,
        `w21%`  = NA_real_
      )
    )
  }

  doneData |>
    mutate(
      Ref_DTT = if_else(Ref_DTT < 0, NA_real_, Ref_DTT), # Negative = data error, treat as missing/invalid, not a real 0-day wait
      within10 = if_else(!is.na(Ref_DTT) & Ref_DTT <= 10, 1L, 0L),
      within21 = if_else(!is.na(Ref_DTT) & Ref_DTT <= 21, 1L, 0L)
    ) |>
    overall_group("Organ") |>
    summarise(
      n      = sum(!is.na(Ref_DTT)),
      mean   = round(mean(Ref_DTT, na.rm = TRUE), 1),
      sd     = round(sd(Ref_DTT, na.rm = TRUE), 1),
      median = round(median(Ref_DTT, na.rm = TRUE), 1),
      w10    = sum(within10),
      w21    = sum(within21),
      `w10%` = ifelse(n == 0, NA_real_, round(100 * w10 / n, 1)),
      `w21%` = ifelse(n == 0, NA_real_, round(100 * w21 / n, 1))
    )  |>
    mutate(
      Organ = if_else(is.na(Organ), "All Organs", Organ)
    ) |>
    ungroup() |>
    tidyr::complete(
      Organ = unique(c("All Organs", table_organs)),
      fill = list(
        n = 0,
        mean = NA_real_,
        sd = NA_real_,
        median = NA_real_,
        w10 = 0,
        w21 = 0,
        `w10%` = NA_real_,
        `w21%` = NA_real_
      )
    )
}

if (nYears == 1) {
  # Single year: original simple table
  generateDTTTable(rxDoneAuditData) |>
    mutate(`Organ Treated` = paste0(Organ, " (N=", n, ")")) |>
    select(`Organ Treated`, mean, sd, median, `w10%`, `w21%`) |>
    kbl(col.names = c("Organ Treated", "Mean time\n(SD)", "Median\n",
                      "% within 10 days\n(Local std.)", "% within 21 days\n(Local std.)")) |>
    add_header_above(data.frame(paste0("Time from Referral Received-to-DTT (", yearBasisText, ")\n", auditPeriodText), 5)) |>
    footnote(wait_time_exclusion_footnote(rxDoneAuditData, "Ref_DTT", "Missing Ref-to-DTT Dates:", "Excluded (negative Ref-to-DTT):")) |>
    kable_styling(bootstrap_options = c("striped","condensed","responsive"), full_width = TRUE)
} else {
  # Multi-year: build wide comparison table
  dttMulti <- buildMultiYearTable(
    summarise_fn = generateDTTTable,
    pct_cols     = c("w10%", "w21%"),
    count_cols   = c("w10",  "w21"),
    raw_col      = "Ref_DTT"
  )

  # Select display columns in year order
  display_cols <- c("Organ Treated",
    unlist(lapply(yearLabels, function(lbl) c(
      paste0("n_", lbl),
      paste0("mean_", lbl), paste0("median_", lbl),
      paste0("w10%_", lbl), paste0("w21%_", lbl)
    )))
  )
  
  col_headers <- c("Organ Treated",
    rep(c("N", "Mean\n(SD)", "Median\n", "% <=10 days", "% <=21 days"), nYears))
  
  span_headers <- c(setNames(1, " "), setNames(rep(5, nYears), yearLabels))

  dttMulti |>
    select(any_of(display_cols)) |>
    kbl(col.names = col_headers) |>
    add_header_above(span_headers) |>
    add_header_above(setNames(length(col_headers), paste0("Time from Referral Received-to-DTT (", yearBasisText, ")"))) |>
    footnote(wait_time_exclusion_footnote(rxDoneAuditData, "Ref_DTT", "Missing Ref-to-DTT Dates:", "Excluded (negative Ref-to-DTT):")) |>
    kable_styling(bootstrap_options = c("striped","condensed","responsive"), font_size = 9, full_width = TRUE) |>
    add_year_separators(display_cols)
  }
```

<strong>Table 1</strong>: Referral to Decision to Treat Time (days). Mean (SD), median (in days) and percentage of referrals meeting defined time standards. * Significant difference compared with the preceding year (two-sided independent samples t-test, p < 0.05).


```{r ref_dtt_boxplot, warning=FALSE}
buildMultiYearBoxplot(
  value_col = "Ref_DTT",
  title_str = "Time from Referral Received-to-DTT",
  ylab_str  = "Days",
  hlines    = list(
    list(y = 10, color = "orange"),
    list(y = 21, color = "red")
  )
)
```

<strong>Plot 1</strong>: Referral received to Decision to Treat (DTT) Box-and-Whisker plot. Box represents the interquartile range (Q1–Q3). Horizontal line represents the median. Whiskers represent the highest and lowest values within 1.5×IQR of the upper and lower quartiles. Points beyond whiskers represent outliers. Labels show sample size (N) and mean value (days).


## Ablation DTT to Rx Times

```{r dtt_rx_table, results='asis'}
generateDTTtoRxTable <- function(doneData) {

  # Empty year
  if (nrow(doneData) == 0) {
    return(
      tibble(
        Organ = c("All Organs", table_organs),
        n = 0,
        mean = NA_real_,
        sd = NA_real_,
        median = NA_real_,
        w31 = 0,
        w45 = 0,
        w60 = 0,
        `w31%` = NA_real_,
        `w45%` = NA_real_,
        `w60%` = NA_real_
      )
    )
  }

  doneData |>
    mutate(
      DTT_Rx = if_else(DTT_Rx < 0, NA_real_, DTT_Rx), # Negative = data error, treat as missing/invalid, not a real 0-day wait
      within31 = if_else(!is.na(DTT_Rx) & DTT_Rx <= 31, 1L, 0L),
      within45 = if_else(!is.na(DTT_Rx) & DTT_Rx <= 45, 1L, 0L),
      within60 = if_else(!is.na(DTT_Rx) & DTT_Rx <= 60, 1L, 0L)
    ) |>
    overall_group("Organ") |>
    summarise(
      n      = sum(!is.na(DTT_Rx)),
      mean   = round(mean(DTT_Rx, na.rm = TRUE), 1),
      sd     = round(sd(DTT_Rx, na.rm = TRUE), 1),
      median = round(median(DTT_Rx, na.rm = TRUE), 1),
      w31    = sum(within31),
      w45    = sum(within45),
      w60    = sum(within60),
      `w31%` = ifelse(n == 0, NA_real_, round(100 * w31 / n, 1)),
      `w45%` = ifelse(n == 0, NA_real_, round(100 * w45 / n, 1)),
      `w60%` = ifelse(n == 0, NA_real_, round(100 * w60 / n, 1))
    ) |>
    mutate(Organ = if_else(is.na(Organ), "All Organs", Organ)) |>
    ungroup() |>
    tidyr::complete(
      Organ = unique(c("All Organs", table_organs)),
      fill = list(
        n = 0,
        mean = NA_real_,
        sd = NA_real_,
        median = NA_real_,
        w31 = 0,
        w45 = 0,
        w60 = 0,
        `w31%` = NA_real_,
        `w45%` = NA_real_,
        `w60%` = NA_real_
      )
    )
}

if (nYears == 1) {
  generateDTTtoRxTable(rxDoneAuditData) |>
    mutate(`Organ (n)` = paste0(Organ, " (N=", n, ")")) |>
    select(`Organ (n)`, mean, median, `w31%`, `w45%`, `w60%`) |>
    kbl(col.names = c("Organ Treated", "Mean time\n(SD)", "Median\n",
                      "% within 31 days\n(Cancer std.)", "% within 45 days\n(Local std.)",
                      "% within 60 days\n(Local std.)")) |>
    add_header_above(data.frame(paste0("Time from DTT-to-Ablation (", yearBasisText, ")\n", auditPeriodText), 6)) |>
    footnote(wait_time_exclusion_footnote(rxDoneAuditData, "DTT_Rx", "Missing DTT-to-Rx Dates:", "Excluded (negative DTT-to-Rx):")) |>
    kable_styling(bootstrap_options = c("striped","condensed","responsive"), font_size = 9, full_width = TRUE)
} else
{
  dttRxMulti <- buildMultiYearTable(
    summarise_fn = generateDTTtoRxTable,
    pct_cols     = c("w31%", "w45%", "w60%"),
    count_cols   = c("w31",  "w45",  "w60"),
    raw_col      = "DTT_Rx"
  )

  display_cols <- c("Organ Treated",
    unlist(lapply(yearLabels, function(lbl) c(
      paste0("n_", lbl),
      paste0("mean_", lbl), paste0("median_", lbl),
      paste0("w31%_", lbl), paste0("w45%_", lbl), paste0("w60%_", lbl)
    )))
  )
  
  col_headers  <- c("Organ Treated",
    rep(c("N", "Mean\n(SD)", "Median\n", "% <=31 days", "% <=45 days", "% <=60 days"), nYears))
  span_headers <- c(setNames(1, " "), setNames(rep(6, nYears), yearLabels))

  dttRxMulti |>
    select(any_of(display_cols)) |>
    kbl(col.names = col_headers) |>
    add_header_above(span_headers) |>
    add_header_above(setNames(length(col_headers), paste0("Time from DTT-to-Ablation (", yearBasisText, ")"))) |>
    footnote(wait_time_exclusion_footnote(rxDoneAuditData, "DTT_Rx", "Missing DTT-to-Rx Dates:", "Excluded (negative DTT-to-Rx):")) |>
    kable_styling(bootstrap_options = c("striped","condensed","responsive"), font_size = 9, full_width = TRUE) |>
    add_year_separators(display_cols)
}
```

<strong>Table 2</strong>: Decision to Treat to Treatment Time (days). Mean (SD), median (in days) and percentage of referrals meeting defined time standards. * Significant difference compared with the preceding year (two-sided independent samples t-test, p < 0.05).

```{r dtt_rx_boxplot, warning=FALSE}
buildMultiYearBoxplot(
  value_col = "DTT_Rx",
  title_str = "Time from DTT-to-Ablation",
  ylab_str  = "Days",
  hlines    = list(
    list(y = 31, color = "orange"),
    list(y = 45, color = "red"),
    list(y = 60, color = "darkred")
  )
)
```

<strong>Plot 2</strong>: Decision to Treat (DTT) to Treatment Date Box-and-Whisker plot. Box represents the interquartile range (Q1–Q3). Horizontal line represents the median. Whiskers represent the highest and lowest values within 1.5×IQR of the upper and lower quartiles. Points beyond whiskers represent outliers. Labels show sample size (N) and mean value (days).

## Ablation Referral to Rx Times

```{r ref_rx_table, results='asis'}
generateRefToRxTable <- function(doneData) {

  # Handle completely empty year
  if (nrow(doneData) == 0) {
    return(
      tibble(
        Organ = c("All Organs", table_organs),
        n = 0,
        mean = NA_real_,
        sd = NA_real_,
        median = NA_real_,
        w90 = 0,
        `w90%` = NA_real_
      )
    )
  }

  doneData |>
    mutate(
      Ref_RxDone = if_else(Ref_RxDone < 0, NA_real_, Ref_RxDone), # Negative = data error, treat as missing/invalid, not a real 0-day wait
      within90 = if_else(!is.na(Ref_RxDone) & Ref_RxDone <= 90, 1L, 0L)
    ) |>
    overall_group("Organ") |>
    summarise(
      n      = sum(!is.na(Ref_RxDone)),
      mean   = round(mean(Ref_RxDone, na.rm = TRUE), 1),
      sd     = round(sd(Ref_RxDone, na.rm = TRUE), 1),
      median = round(median(Ref_RxDone, na.rm = TRUE), 1),
      w90    =    sum(within90),
      `w90%` = ifelse(n == 0, NA_real_, round(100 * w90 / n, 1))
    ) |>
    mutate(Organ = if_else(is.na(Organ), "All Organs", Organ)) |>
    ungroup() |>
    tidyr::complete(
      Organ = unique(c("All Organs", table_organs)),
      fill = list(
        n = 0,
        mean = NA_real_,
        sd = NA_real_,
        median = NA_real_,
        w90 = 0,
        `w90%` = NA_real_
      )
    )
}

if (nYears == 1) {
  generateRefToRxTable(rxDoneAuditData) |>
    mutate(`Organ (n)` = paste0(Organ, " (N=", n, ")")) |>
    select(`Organ (n)`, mean, median, `w90%`) |>
    kbl(col.names = c("Organ Treated", "Mean time\n(SD)", "Median\n",
                      "% within 90 days\n(Local std.)")) |>
    add_header_above(data.frame(paste0("Time from Referral Received-to-Ablation (", yearBasisText, ")\n", auditPeriodText), 4)) |>
    footnote(wait_time_exclusion_footnote(rxDoneAuditData, "Ref_RxDone", "Missing Ref-to-Rx Dates:", "Excluded (negative Ref-to-Rx):")) |>
    kable_styling(bootstrap_options = c("striped","condensed","responsive"), full_width = TRUE)
} else {
  refRxMulti <- buildMultiYearTable(
    summarise_fn = generateRefToRxTable,
    pct_cols     = c("w90%"),
    count_cols   = c("w90"),
    raw_col      = "Ref_RxDone"
  )

  display_cols <- c("Organ Treated",
    unlist(lapply(yearLabels, function(lbl) c(
      paste0("n_", lbl),
      paste0("mean_", lbl), paste0("median_", lbl), paste0("w90%_", lbl)
    )))
  )
  
  col_headers  <- c("Organ Treated", rep(c("N", "Mean\n(SD)", "Median\n", "% <=90 days"), nYears))
  span_headers <- c(setNames(1, " "), setNames(rep(4, nYears), yearLabels))

  refRxMulti |>
    select(any_of(display_cols)) |>
    kbl(col.names = col_headers) |>
    add_header_above(span_headers) |>
    add_header_above(setNames(length(col_headers), paste0("Time from Referral Received-to-Ablation (", yearBasisText, ")"))) |>
    footnote(wait_time_exclusion_footnote(rxDoneAuditData, "Ref_RxDone", "Missing Ref-to-Rx Dates:", "Excluded (negative Ref-to-Rx):")) |>
    kable_styling(bootstrap_options = c("striped","condensed","responsive"), font_size = 9, full_width = TRUE) |>
    add_year_separators(display_cols)
  }
```

<strong>Table 3</strong>: Referral to Treatment Time (days). Mean (SD), median (in days) and percentage of referrals meeting defined time standards. * Significant difference compared with the preceding year (two-sided independent samples t-test, p < 0.05).

```{r ref_rx_boxplot, warning=FALSE}
buildMultiYearBoxplot(
  value_col = "Ref_RxDone",
  title_str = "Time from Referral received-to-Ablation",
  ylab_str  = "Days",
  hlines    = list(list(y = 90, color = "red"))
)
```

<strong>Plot 3</strong>: Referral Date to Treatment Date Box-and-Whisker plot. Box represents the interquartile range (Q1–Q3). Horizontal line represents the median. Whiskers represent the highest and lowest values within 1.5×IQR of the upper and lower quartiles. Points beyond whiskers represent outliers. Labels show sample size (N) and mean value (days).

## Clock Stops causing negative Referral to DTT and DTT to Rx times

```{r negative_clockstop}
negativeClockstop <- rxDoneAuditData |>
  filter(Ref_DTT < 0 | DTT_Rx < 0) |>
  select(
    ID, Organ, Ref_DTT, DTT_Rx,
    ClockStopDaysPreDTT, ClockStopDaysPostDTT
  )

if (nrow(negativeClockstop) > 0) {
  negativeClockstop |>
    kbl(
      col.names = c(
        "ID",
        "Organ Treated",
        "Referral to DTT\n(days)",
        "DTT to Rx\n(days)",
        "Clock Stop Pre DTT\n(days)",
        "Clock Stop Post DTT\n(days)"
      )
    ) |>
    kable_styling(
      bootstrap_options = c("striped", "condensed", "responsive"),
      full_width = FALSE
    ) |>
    column_spec(1, width = "12em")
} else {
  cat("No negative referral-to-DTT or DTT-to-Rx intervals identified.")
}
```

## Ablation Referral Days Stopped (Pre- or Post-DTT)

```{r daystopped_pre_or_post_dtt}
rxDoneAuditData |>
  mutate(
    clockstopped = if_else(
      is.na(ClockStopDaysPreDTT),
      if_else(is.na(ClockStopDaysPostDTT), "Not Stopped", "Stopped Post DTT"),
      if_else(is.na(ClockStopDaysPostDTT), "Stopped Pre DTT", "Stopped Both Pre and Post DTT")
    ),
    daysStopped = if_else(
      is.na(ClockStopDaysPreDTT),
      if_else(is.na(ClockStopDaysPostDTT), 0, abs(ClockStopDaysPostDTT)),
      if_else(is.na(ClockStopDaysPostDTT), abs(ClockStopDaysPreDTT),
              abs(ClockStopDaysPreDTT + ClockStopDaysPostDTT))
    )
  ) |>
  group_by(clockstopped) |>
  mutate(n = n(), clockstopped = paste0(clockstopped, " (N=", n, ")")) |>
  summarise(mean = round(mean(daysStopped), 1), median = round(median(daysStopped), 1)) |>
  kbl(col.names = c("Clock Status", "Mean time\n(SD)", "Median\n")) |>
  kable_styling(bootstrap_options = c("striped","condensed","responsive"), full_width = TRUE) |>
  column_spec(1, width = "30em") |>
  column_spec(2, width = "8em") |>
  column_spec(3, width = "8em")
```

```{r daystopped_pre_and_post_dtt}
rxDoneAuditData |>
  mutate(
    clockstopped = if_else(
      is.na(ClockStopDaysPreDTT) & is.na(ClockStopDaysPostDTT), "Not Stopped", "Stopped"
    ),
    daysStopped = if_else(
      is.na(ClockStopDaysPreDTT),
      if_else(is.na(ClockStopDaysPostDTT), 0, abs(ClockStopDaysPostDTT)),
      if_else(is.na(ClockStopDaysPostDTT), abs(ClockStopDaysPreDTT),
              abs(ClockStopDaysPreDTT + ClockStopDaysPostDTT))
    )
  ) |>
  group_by(clockstopped) |>
  mutate(n = n(), clockstopped = paste0(clockstopped, " (N=", n, ")")) |>
  summarise(mean = round(mean(daysStopped), 1), median = round(median(daysStopped), 1)) |>
  kbl(col.names = c("Clock Status", "Mean time\n(SD)", "Median\n(days)")) |>
  kable_styling(bootstrap_options = c("striped","condensed","responsive"), full_width = TRUE) |>
  column_spec(1, width = "30em") |>
  column_spec(2, width = "8em") |>
  column_spec(3, width = "8em")
```

```{r clockstop}
rxDoneAuditData |>
  mutate(
    clockstopped = if_else(
      is.na(ClockStopDaysPreDTT),
      if_else(is.na(ClockStopDaysPostDTT), "Not Stopped", "Stopped Post DTT"),
      if_else(is.na(ClockStopDaysPostDTT), "Stopped Pre DTT", "Stopped Both Pre and Post DTT")
    )
  ) |>
  filter(clockstopped != "Not Stopped") |>
  select(ID, Organ, ClockStopWhy) |>
  kbl(col.names = c("ID", "Organ", "Reason for clock stop")) |>
  kable_styling(bootstrap_options = c("striped","condensed","responsive"), full_width = FALSE) |>
  column_spec(1, width = "8em") |>
  column_spec(2, width = "8em") |>
  column_spec(3, width = "60em")
```

## Time to Treatment Plot

```{r ttt_plot}
rxDoneAuditDataplot <- commonRxDonePlot(rxDoneAuditData) +
  ggtitle("Time to Treatment")
rxDoneAuditDataplot
```


## Treatment Volume Plot

```{r treatment_volume_plot, fig.height=6}
# Use monthly bins for audit periods of up to 12 months; otherwise quarterly.
monthlyEnd <- seq(auditStart, by = "1 year", length.out = 2)[2] - 1

volumePlotDuration <- if (auditEnd <= monthlyEnd) {
  "month"
} else {
  "quarter"
}

makeRxVolumePlot(rxDoneAuditData, volumePlotDuration)
```

## Organ Treatment Piechart

```{r organ_pie}
rxDoneAuditData %>%
  group_by(Organ) %>%
  summarise(n = n()) %>%
  mutate(
    prop   = n / sum(.$n) * 100,
    ypos   = cumsum(prop) - 0.5 * prop,
    Organ = paste0(Organ, " (N=", n, ")")
  ) %>%
  ggplot(aes(x = "", y = n, fill = Organ)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +
  scale_fill_brewer(palette = "Set1", name = "Tumour Type")
```

## Wait time plots

```{r wait_time_plots, warning=FALSE}
referralTimes <- processWaitTimesPerPeriod(
  rxDoneAuditData, rxWaitAuditData,
  audit_start_date, audit_end_date, "month"
)
```

```{r refToDTTMeanPlot, warning=FALSE}
refToDTTMeanPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
refToDTTCountPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
```

```{r dttToRxMeanPlot, warning=FALSE}
dttToRxMeanPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
dttToRxCountPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
```

```{r refToRxMeanPlot, warning=FALSE}
refToRxMeanPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
refToRxCountPlot(referralTimes, "Month", selectedGroup = "Ablation Date")
```

## Long waits

```{r longwaits}
longWaitData <- rxDoneAuditData %>%
  filter(Ref_RxDone > 120) %>%
  mutate(
    ClockStopDaysPreDTT  = if_else(
      is.na(ClockStopDaysPreDTT), 0, ClockStopDaysPreDTT
    ),
    ClockStopDaysPostDTT = if_else(
      is.na(ClockStopDaysPostDTT), 0, ClockStopDaysPostDTT
    )
  ) %>%
  select(
    ID,
    Organ,
    Ref_RxDone,
    ClockStopDaysPreDTT,
    ClockStopDaysPostDTT
  )

if (nrow(longWaitData) > 0) {

  longWaitData %>%
    kbl(
      col.names = c(
        "ID",
        "Organ",
        "Referral to Ablation time\n(days)",
        "Clock Stop Pre DTT\n(days)",
        "Clock Stop Post DTT\n(days)"
      )
    ) %>%
    kable_styling(
      bootstrap_options = c("striped", "condensed", "responsive"),
      full_width = TRUE
    ) %>%
    column_spec(2, width = "10em")

} else {
  cat("No referrals with a referral-to-ablation time greater than 120 days.")
}
```

## Credits

```{r reportLogo, warning=FALSE}
logo_src <- here("www", "TARGETPlotterLogo.png")
if (file.exists(logo_src)) {
  knitr::include_graphics(normalizePath(logo_src))
} else {
  cat("<!-- TARGETPlotterLogo.png logo not available -->")
}
```

<br>
Audit Report Developers: Dr. Andrew Thornton, Dr. Paul Lyon<br>
TARGET-UK Lead: Dr. Paul Lyon, FRCR

