---
title: "TARGET-UK: Cancer Outcomes Report"
output:
  html_document:
    toc: true
    self_contained: true
date: "`r format(Sys.Date(), '%d %B %Y')`"
params:
  report_start_date: !r Sys.Date() - 365
  report_end_date: !r Sys.Date()
  report_organs: "All"
  report_diagnosis_type: "All"
  report_subtypes: ["All"]
  report_genders: ["Female", "Male", "Unknown"]
  report_modality: "All"
  report_ignore_first_ltp: TRUE
  report_min_months_followup: 3
  report_max_years_followup: 5
---

```{css, echo=FALSE}
body { font-size: 14px; }
table {
  font-size: 13px;
  width: 100% !important;
  table-layout: auto;
}
th, td {
  padding: 4px 8px !important;
  font-size: 13px;
}
img { max-width: 100% !important; height: auto !important; }

@media print {
  @page {
    size: A4 portrait;
    margin: 8mm 6mm 8mm 6mm;
  }
  body {
    font-size: 11px;
    width: 198mm;
  }
  table {
    font-size: 10px;
    page-break-inside: avoid;
    table-layout: auto;
  }
  th, td { padding: 2px 4px !important; font-size: 10px; }
  img, .plot {
    max-width: 196mm !important;
    width: 196mm !important;
    height: auto !important;
    page-break-inside: avoid;
  }
  .figure {
    max-width: 196mm !important;
    page-break-inside: avoid;
  }
  h2 { page-break-before: auto; }
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(fig.width = 10, fig.height = 5, dpi = 120)
options(knitr.table.format = "html")

library(dplyr)
library(ggplot2)
library(survival)
library(ggsurvfit)
library(scales)
library(kableExtra)

report_start_date <- params$report_start_date
report_end_date   <- params$report_end_date
report_organs     <- params$report_organs
report_diagnosis_type <- params$report_diagnosis_type
report_subtypes   <- params$report_subtypes
report_genders    <- params$report_genders
report_modality   <- params$report_modality
report_ignore_first_ltp <- isTRUE(params$report_ignore_first_ltp)
report_max_years_followup <- as.numeric(params$report_max_years_followup)[1]
report_min_months_followup <- as.numeric(params$report_min_months_followup)[1]

reportStart <- as.Date(report_start_date)
reportEnd   <- as.Date(report_end_date)

if (!exists("makeSurvivalPlot", mode = "function")) {
  stop("makeSurvivalPlot() is not available in the report environment. Source the app plotting methods before rendering this Rmd.")
}
if (!exists("makeRecurrencePlot", mode = "function")) {
  stop("makeRecurrencePlot() is not available in the report environment. Source the app plotting methods before rendering this Rmd.")
}

normalise_organs <- function(x) {
  if (is.null(x) || length(x) == 0 || anyNA(x)) return("All")
  if (length(x) == 1 && identical(x, "All")) return("All")
  x
}

report_organs <- normalise_organs(report_organs)

filter_patient_rows <- function(df) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)
  
  d <- df |>
    filter(!is.na(FirstRxDate)) |>
    filter(FirstRxDate >= reportStart, FirstRxDate <= reportEnd)
    
  if (!identical(report_organs, "All")) {
    d <- d |> filter(Organ %in% report_organs)
  }

  if (!identical(report_diagnosis_type, "All")) {
    switch(substring(report_diagnosis_type, 1, 1),
      "P" = { d <- d |> filter(Diagnosis1o %in% report_subtypes) },
      "S" = { d <- d |> filter(Diagnosis2o %in% report_subtypes) },
      "B" = { d <- d |> filter(DiagnosisBn %in% report_subtypes) },
      "U" = { d <- d |> filter(DiagnosisUn %in% report_subtypes) }
    )
  }

  if (!identical(report_modality, "All")) {
    d <- d |> filter(grepl(report_modality, RxModalities, fixed = TRUE))
  }

  d
}

filter_lesion_rows <- function(df) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  d <- df |>
    filter(!is.na(RxDate)) |>
    filter(RxDate >= reportStart, RxDate <= reportEnd)

  if (!identical(report_organs, "All")) {
    d <- d |> filter(Organ %in% report_organs)
  }

  if (!identical(report_diagnosis_type, "All")) {
    switch(substring(report_diagnosis_type, 1, 1),
      "P" = { d <- d |> filter(Diagnosis1o %in% report_subtypes) },
      "S" = { d <- d |> filter(Diagnosis2o %in% report_subtypes) },
      "B" = { d <- d |> filter(DiagnosisBn %in% report_subtypes) },
      "U" = { d <- d |> filter(DiagnosisUn %in% report_subtypes) }
    )
  }

  if (!identical(report_modality, "All")) {
    d <- d |> filter(grepl(report_modality, RxModality, fixed = TRUE))
  }

  d
}

filter_ae_rows <- function(df) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  d <- df

  if ("DateofOnset" %in% names(d)) {
    d$DateofOnset <- suppressWarnings(as.Date(d$DateofOnset, tryFormats = c("%d-%m-%Y", "%Y-%m-%d", "%d/%m/%Y")))
  }
  if ("DateofResolution" %in% names(d)) {
    d$DateofResolution <- suppressWarnings(as.Date(d$DateofResolution, tryFormats = c("%d-%m-%Y", "%Y-%m-%d", "%d/%m/%Y")))
  }

  if ("DateofOnset" %in% names(d) || "DateofResolution" %in% names(d)) {
    onset_ok <- if ("DateofOnset" %in% names(d)) !is.na(d$DateofOnset) &
      d$DateofOnset >= reportStart & d$DateofOnset <= reportEnd else rep(FALSE, nrow(d))
    res_ok <- if ("DateofResolution" %in% names(d)) !is.na(d$DateofResolution) &
      d$DateofResolution >= reportStart & d$DateofResolution <= reportEnd else rep(FALSE, nrow(d))
    d <- d[onset_ok | res_ok, , drop = FALSE]
  }

  if (nrow(d) == 0) return(d)

  if (!identical(report_organs, "All") && "Organ" %in% names(d)) {
    d <- d |> filter(Organ %in% report_organs)
  }

  if (!identical(report_diagnosis_type, "All")) {
    if (report_diagnosis_type == "1o & 2o") {
      if (all(c("Diagnosis1o", "Diagnosis2o") %in% names(d))) {
        d <- d |> filter(Diagnosis1o %in% report_subtypes | Diagnosis2o %in% report_subtypes)
      }
    } else {
      diag_col <- switch(
        substring(report_diagnosis_type, 1, 1),
        "P" = "Diagnosis1o",
        "S" = "Diagnosis2o",
        "B" = "DiagnosisBn",
        "U" = "DiagnosisUn",
        ""
      )
      if (nzchar(diag_col) && diag_col %in% names(d)) {
        d <- d |> filter(.data[[diag_col]] %in% report_subtypes)
      }
    }
  }

  if ("Grade" %in% names(d)) {
    grade_num <- suppressWarnings(as.integer(as.character(d$Grade)))
    d <- d[!is.na(grade_num) & grade_num %in% c(3L, 4L, 5L), , drop = FALSE]
  }

  d
}

patient_data <- if (exists("cancerPerPatientData") && is.data.frame(cancerPerPatientData)) {
  filter_patient_rows(cancerPerPatientData)
} else {
  data.frame()
}

lesion_data <- if (exists("cancerPerLesionData") && is.data.frame(cancerPerLesionData)) {
  filter_lesion_rows(cancerPerLesionData)
} else {
  data.frame()
}

if (nrow(patient_data) > 0 && "MaxTumourSize" %in% names(patient_data)) {
  patient_data$MaxTumourSize <- suppressWarnings(as.numeric(patient_data$MaxTumourSize))
}
if (nrow(lesion_data) > 0 && "TumourSize" %in% names(lesion_data)) {
  lesion_data$TumourSize <- suppressWarnings(as.numeric(lesion_data$TumourSize))
}

cat("\n===== AE DATA COLUMN NAMES =====\n")
print(names(aeData))
cat("NA names:", which(is.na(names(aeData))), "\n")
cat("Blank names:", which(names(aeData) == ""), "\n")

ae_data <- if (exists("aeData") && is.data.frame(aeData)) {
  filter_ae_rows(aeData)
} else {
  data.frame()
}

patient_sex_summary <- if (nrow(patient_data) > 0 && "Gender" %in% names(patient_data)) {
  patient_data |>
    filter(!is.na(Gender) & Gender != "") |>
    count(Gender, name = "n") |>
    mutate(pct = n / sum(n))
} else {
  tibble::tibble(Gender = character(0), n = integer(0), pct = numeric(0))
}

rxDoneReferralLevel <- if (exists("rxDoneData") && is.data.frame(rxDoneData)) {
  d <- rxDoneData
  bad <- is.na(names(d)) | names(d) == ""
  if (any(bad)) names(d)[bad] <- paste0("unnamed_col_", seq_len(sum(bad)))
  d |>
    filter(!(ID %in% c("000-1", "00000-1", "000000-1"))) |>
    distinct(ID, .keep_all = TRUE)
} else {
  data.frame()
}

meanTreatmentsPerPatient <-
  rxDoneReferralLevel |>
  mutate(PtID = sub("-[0-9]+$", "", ID)) |>
  count(PtID) |>
  summarise(mean = mean(n, na.rm = TRUE)) |>
  pull(mean)

meanTumoursPerPatient <-
  rxDoneReferralLevel |>
  mutate(PtID = sub("-[0-9]+$", "", ID)) |>
  group_by(PtID) |>
  summarise(Tumours = sum(TumourCount, na.rm = TRUE), .groups = "drop") |>
  summarise(mean = mean(Tumours, na.rm = TRUE)) |>
  pull(mean)

tumour_summary <- if (nrow(lesion_data) > 0 && "TumourSize" %in% names(lesion_data)) {
  lesion_data |>
    summarise(
      n = sum(!is.na(TumourSize)),
      median = median(TumourSize, na.rm = TRUE),
      sd = sd(TumourSize, na.rm = TRUE),
      mean = mean(TumourSize, na.rm = TRUE)
    )
} else {
  tibble::tibble(n = 0, median = NA_real_, sd = NA_real_, mean = NA_real_)
}

followup_days <- report_max_years_followup * 365.25

get_ltp_rate <- function(df, time_col, status_col) {
  if (!is.data.frame(df) || nrow(df) == 0) return(NA_real_)
  if (!(time_col %in% names(df)) || !(status_col %in% names(df))) return(NA_real_)
  d <- df |> filter(!is.na(.data[[time_col]]), !is.na(.data[[status_col]]))
  if (nrow(d) == 0) return(NA_real_)
  fit <- survfit(Surv(d[[time_col]], d[[status_col]] == 2) ~ 1, data = d)
  s <- summary(fit, times = followup_days, extend = TRUE)
  if (length(s$surv) == 0) return(NA_real_)
  s$surv[1]
}

get_os_rate <- function(df, time_col, status_col) {
  if (!is.data.frame(df) || nrow(df) == 0) return(NA_real_)
  if (!(time_col %in% names(df)) || !(status_col %in% names(df))) return(NA_real_)
  d <- df |> filter(!is.na(.data[[time_col]]), !is.na(.data[[status_col]]))
  if (nrow(d) == 0) return(NA_real_)
  fit <- survfit(Surv(d[[time_col]], d[[status_col]]) ~ 1, data = d)
  s <- summary(fit, times = followup_days, extend = TRUE)
  if (length(s$surv) == 0) return(NA_real_)
  s$surv[1]
}

apply_ltp_rule_patient <- function(df, ignore_first_ltp = FALSE) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)
  d <- df
  if (isTRUE(ignore_first_ltp) && "LTPCountMax" %in% names(d)) {
    idx <- !is.na(d$LTPCountMax) & d$LTPCountMax == 1
    d$StatusLTPF[idx] <- 1
  }
  d
}

apply_ltp_rule_lesion <- function(df, ignore_first_ltp = FALSE) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)
  d <- df
  if (isTRUE(ignore_first_ltp) && all(c("PtID", "LTPDate", "StatusLTPEpisode") %in% names(d))) {
    # use the same logic as your plot code:
    # censor episodes with only one subsequent Rx after LTP
    for (i in which(!is.na(d$LTPDate) & d$StatusLTPEpisode == 2)) {
      ptID <- d$PtID[i]
      ltpDt <- d$LTPDate[i]

      laterRxCount <- length(unique(
        lesion_data$RxNo[
          lesion_data$PtID == ptID &
            !is.na(lesion_data$RxDate) &
            lesion_data$RxDate > ltpDt
        ]
      ))

      if (laterRxCount == 1) {
        d$StatusLTPEpisode[i] <- 1
      }
    }
  }
  d
}

patient_data_ltp <- apply_ltp_rule_patient(patient_data, report_ignore_first_ltp)
lesion_data_ltp  <- apply_ltp_rule_lesion(lesion_data, report_ignore_first_ltp)
patient_ltp <- get_ltp_rate(patient_data_ltp, "TimeLTPF", "StatusLTPF")
lesion_ltp  <- get_ltp_rate(lesion_data_ltp, "TimeLTPEpisode", "StatusLTPEpisode")
patient_os  <- get_os_rate(patient_data, "TimeSurvival", "StatusOverallSurvival")
patient_ltpf_os <- get_os_rate(patient_data, "TimeLTPFOS", "StatusLTPFOS")

km_risk_title <- function(x) if (is.na(x)) "NA" else scales::percent(x, accuracy = 0.1)

make_female_male_unknown_table <- function(df) {
  if (!is.data.frame(df) || nrow(df) == 0 || !("Gender" %in% names(df))) {
    return(tibble::tibble(Gender = character(0), n = integer(0), pct = numeric(0)))
  }
  df |>
    filter(!is.na(Gender) & Gender != "") |>
    count(Gender, name = "n") |>
    mutate(pct = n / sum(n))
}

fmt_param <- function(x) {
  x <- setdiff(as.character(x), "All")
  if (length(x) == 0) "All" else paste(x, collapse = ", ")
}
```

## Report Details

| Parameter | Value |
|:----------|:------|
| **Report generated** | `r format(Sys.time(), "%a %d %B %Y %H:%M")` |
| **Report period** | `r format(reportStart, "%d %B %Y")` – `r format(reportEnd, "%d %B %Y")` |
| **Organ(s)** | `r if (identical(report_organs, "All")) "All" else paste(report_organs, collapse = ", ")` |
| **Diagnosis type** | `r fmt_param(report_diagnosis_type)` |
| **Subtype(s)** | `r fmt_param(report_subtypes)` |
| **Gender(s)** | `r paste(report_genders, collapse = ", ")` |
| **Modality** | `r report_modality` |
| **Minimum follow-up** | `r report_min_months_followup` months |
| **Maximum follow-up** | `r report_max_years_followup` years |
| **LTP definition** | `r if (report_ignore_first_ltp) "Allow 2xRx before LTP (ignore first LTP)" else "Standard LTP definition"` |

---

## Overview

```{r overview-table, echo=FALSE}
overview_tbl <- tibble::tibble(
  Metric = c(
    "Patients",
    "Tumours treated",
    "Mean treatments per referral",
    "Mean tumours ablated per treatment",
    "Median tumour size (mm)",
    "SD tumour size (mm)",
    paste0(report_max_years_followup, "-year OS"),
    paste0(report_max_years_followup, "-year LTP-free OS"),
    paste0(report_max_years_followup, "-year LTP (per patient)"),
    paste0(report_max_years_followup, "-year LTP (per lesion)")
  ),
  Value = c(
    nrow(patient_data),
    nrow(lesion_data),
    round(meanTreatmentsPerPatient, 2),
    round(meanTumoursPerPatient, 2),
    round(tumour_summary$median[1], 1),
    round(tumour_summary$sd[1], 1),
    km_risk_title(patient_os),
    km_risk_title(patient_ltpf_os),
    km_risk_title(patient_ltp),
    km_risk_title(lesion_ltp)
  )
)

kable(overview_tbl, caption = "Cancer outcomes summary") |>
  kableExtra::kable_styling(full_width = FALSE)
```

## Tumour size and sex distribution

```{r tumour-size-hist, echo=FALSE, fig.height=4.5}
if (nrow(lesion_data) > 0 && "TumourSize" %in% names(lesion_data)) {
  ggplot(lesion_data |> filter(!is.na(TumourSize)), aes(x = TumourSize)) +
    geom_histogram(bins = 20) +
    labs(
      title = "Tumour size distribution",
      x = "Tumour size (mm)",
      y = "Count"
    ) +
    theme_minimal(base_size = 12)
} else {
  ggplot() +
    annotate("text", x = 0.5, y = 0.5, label = "No tumour size data available", size = 6) +
    theme_void()
}
```

```{r tumour-size-summary, echo=FALSE}
tumour_tbl <- tibble::tibble(
  Metric = c("Count with size recorded", "Median size (mm)", "SD size (mm)", "Mean size (mm)"),
  Value = c(
    tumour_summary$n[1],
    round(tumour_summary$median[1], 1),
    round(tumour_summary$sd[1], 1),
    round(tumour_summary$mean[1], 1)
  )
)

kable(tumour_tbl, caption = "Tumour size summary") |>
  kableExtra::kable_styling(full_width = FALSE)
```

```{r sex-dist-plot, echo=FALSE, fig.height=4.2}
if (nrow(patient_sex_summary) > 0) {
  ggplot(patient_sex_summary, aes(x = Gender, y = n)) +
    geom_col() +
    geom_text(aes(label = n), vjust = -0.3) +
    labs(
      title = "Sex distribution",
      x = NULL,
      y = "Patients"
    ) +
    theme_minimal(base_size = 12)
} else {
  ggplot() +
    annotate("text", x = 0.5, y = 0.5, label = "No sex data available", size = 6) +
    theme_void()
}
```

```{r sex-summary-table, echo=FALSE}
sex_tbl <- if (nrow(patient_sex_summary) > 0) {
  patient_sex_summary |>
    mutate(pct = scales::percent(pct, accuracy = 1))
} else {
  tibble::tibble(Gender = character(0), n = integer(0), pct = character(0))
}

kable(sex_tbl, caption = "Sex distribution") |>
  kableExtra::kable_styling(full_width = FALSE)
```


## LTP curves at `r report_max_years_followup` years (`r if (report_ignore_first_ltp) "ignore first LTP" else "allow up to 2 Rx before LTP"`)

```{r ltp-patient-plot, echo=FALSE, fig.height=4.8}
makeRecurrencePlot(
  strStart = format(reportStart, "%d/%m/%Y"),
  strEnd = format(reportEnd, "%d/%m/%Y"),
  selectedOrgans = report_organs,
  selectedDiagnosisType = report_diagnosis_type,
  selectedSubtypes = report_subtypes,
  selectedGenders = report_genders,
  selectedModality = report_modality,
  minMonthsFollowup = report_min_months_followup,
  maxYearsFollowup = report_max_years_followup,
  ignoreFirstLTP = report_ignore_first_ltp,
  ltpAnalysisUnit = "patient"
)
```

```{r ltp-lesion-plot, echo=FALSE, fig.height=4.8}
makeRecurrencePlot(
  strStart = format(reportStart, "%d/%m/%Y"),
  strEnd = format(reportEnd, "%d/%m/%Y"),
  selectedOrgans = report_organs,
  selectedDiagnosisType = report_diagnosis_type,
  selectedSubtypes = report_subtypes,
  selectedGenders = report_genders,
  selectedModality = report_modality,
  minMonthsFollowup = report_min_months_followup,
  maxYearsFollowup = report_max_years_followup,
  ignoreFirstLTP = report_ignore_first_ltp,
  ltpAnalysisUnit = "lesion"
)
```

## Survival curves at `r report_max_years_followup` years

```{r os-plot, echo=FALSE, fig.height=4.8}
makeSurvivalPlot(
  strStart = format(reportStart, "%d/%m/%Y"),
  strEnd = format(reportEnd, "%d/%m/%Y"),
  selectedOrgans = report_organs,
  selectedDiagnosisType = report_diagnosis_type,
  selectedSubtypes = report_subtypes,
  selectedGenders = report_genders,
  selectedModality = report_modality,
  survivalType = 0,
  minMonthsFollowup = report_min_months_followup,
  maxYearsFollowup = report_max_years_followup,
  ignoreFirstLTP = report_ignore_first_ltp
)
```

```{r ltpf-os-plot, echo=FALSE, fig.height=4.8}
makeSurvivalPlot(
  strStart = format(reportStart, "%d/%m/%Y"),
  strEnd = format(reportEnd, "%d/%m/%Y"),
  selectedOrgans = report_organs,
  selectedDiagnosisType = report_diagnosis_type,
  selectedSubtypes = report_subtypes,
  selectedGenders = report_genders,
  selectedModality = report_modality,
  survivalType = 2,
  minMonthsFollowup = report_min_months_followup,
  maxYearsFollowup = report_max_years_followup,
  ignoreFirstLTP = report_ignore_first_ltp
)
```

## Grade 3-5 adverse events

```{r grade-3-5-ae-table, echo=FALSE}

if (nrow(ae_data) > 0) {
  ae_tbl <- ae_data |>
    mutate(
      Grade = suppressWarnings(as.integer(as.character(Grade)))
    ) |>
    filter(Grade %in% c(3L, 4L, 5L))

  if (nrow(ae_tbl) > 0) {
    keep_cols <- intersect(
      c("ID", "PtID", "Organ", "DiagnosisType", "Diagnosis1o", "Diagnosis2o", "DiagnosisBn", "DiagnosisUn",
        "Complication", "Grade", "DateofOnset", "DateofResolution", "Duration"),
      names(ae_tbl)
    )

    ae_tbl <- ae_tbl |>
      select(all_of(keep_cols))

    if ("DateofOnset" %in% names(ae_tbl)) {
      ae_tbl <- ae_tbl |>
        arrange(Grade, desc(DateofOnset))
    } else {
      ae_tbl <- ae_tbl |>
        arrange(Grade)
    }

    kable(ae_tbl, caption = "Grade 3-5 adverse events") |>
      kableExtra::kable_styling(full_width = FALSE)
  } else {
    cat("No grade 3-5 adverse events in the selected cohort.")
  }
} else {
  cat("No adverse event data available.")
}
```



## Credits

```{r reportLogo, warning=FALSE}
logo_src <- here("www", "TARGETPlotterLogo.png")
if (file.exists(logo_src)) {
  knitr::include_graphics(normalizePath(logo_src))
} else {
  cat("<!-- TARGETPlotterLogo.png logo not available -->")
}
```

<br>
Report Report Developer: Dr. Paul Lyon<br>
TARGET-UK Lead: Dr. Paul Lyon, FRCR
