---
title: "TARGET-UK: Cancer Outcomes Report"
output:
  html_document:
    toc: true
    self_contained: true
date: "`r format(Sys.Date(), '%d %B %Y')`"
params:
  report_start_date: !r Sys.Date() - 365
  report_end_date: !r Sys.Date()
  report_organs: "All"
  report_diagnosis_type: "All"
  report_subtypes: ["All"]
  report_genders: ["Female", "Male", "Unknown"]
  report_modality: "All"
  report_min_tumour_size: 0
  report_max_tumour_size: 100
  report_include_ignore_first_ltp: FALSE
  report_min_months_followup: 3
  report_max_years_followup: 5
  report_cancer_anonymised: TRUE
---

```{css, echo=FALSE}
body { font-size: 14px; }
table {
  font-size: 13px;
  width: 100% !important;
  table-layout: auto;
}
th, td {
  padding: 4px 8px !important;
  font-size: 13px;
}
img { max-width: 100% !important; height: auto !important; }

@media print {
  @page {
    size: A4 portrait;
    margin: 8mm 6mm 8mm 6mm;
  }
  body {
    font-size: 11px;
    width: 198mm;
  }
  table {
    font-size: 10px;
    page-break-inside: avoid;
    table-layout: auto;
  }
  th, td { padding: 2px 4px !important; font-size: 10px; }
  img, .plot {
    max-width: 196mm !important;
    width: 196mm !important;
    height: auto !important;
    page-break-inside: avoid;
  }
  .figure {
    max-width: 196mm !important;
    page-break-inside: avoid;
  }
  h2 { page-break-before: auto; }
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(fig.width = 10, fig.height = 5, dpi = 120)
options(knitr.table.format = "html")

library(dplyr)
library(ggplot2)
library(survival)
library(ggsurvfit)
library(scales)
library(kableExtra)
library(htmltools)
library(gridExtra)

report_start_date               <- params$report_start_date
report_end_date                 <- params$report_end_date
report_organs                   <- params$report_organs
report_diagnosis_type           <- params$report_diagnosis_type
report_subtypes                 <- params$report_subtypes
report_genders                  <- params$report_genders
report_modality                 <- params$report_modality
report_min_tumour_size          <- params$report_min_tumour_size
report_max_tumour_size          <- params$report_max_tumour_size
report_include_ignore_first_ltp <- isTRUE(params$report_include_ignore_first_ltp)
report_max_years_followup       <- as.numeric(params$report_max_years_followup)
report_min_months_followup      <- as.numeric(params$report_min_months_followup)
reportStart                     <- as.Date(report_start_date)
reportEnd                       <- as.Date(report_end_date)
reportAnonymised                <- isTRUE(params$report_cancer_anonymised)

if (!exists("makeSurvivalPlot", mode = "function")) {
  stop("makeSurvivalPlot() is not available in the report environment. Source the app plotting methods before rendering this Rmd.")
}
if (!exists("makeRecurrencePlot", mode = "function")) {
  stop("makeRecurrencePlot() is not available in the report environment. Source the app plotting methods before rendering this Rmd.")
}

DEBUG_MODE <- toupper(Sys.getenv("DEBUG_MODE", unset = "FALSE")) == "TRUE"

debug_log <- function(...) {
  if (isTRUE(DEBUG_MODE)) {
    cat(sprintf(...), "\n", file = stderr(), sep = "")
  }
}

debug_table <- function(label, x) {
  if (isTRUE(DEBUG_MODE)) {
    cat(label, "\n", file = stderr(), sep = "")
    cat(capture.output(print(table(x, useNA = "ifany"))), sep = "\n", file = stderr())
  }
}

filter_by_report_diagnosis <- function(d, report_diagnosis_type, report_subtypes) {
  if (!is.data.frame(d) || nrow(d) == 0) return(d)
  if (is.null(report_diagnosis_type) || identical(report_diagnosis_type, "All")) return(d)

  if (is.null(report_subtypes)) report_subtypes <- "All"
  report_subtypes <- setdiff(as.character(report_subtypes), "All")

  if (report_diagnosis_type == "1o & 2o") {
    return(
      d |>
        filter(
          (DiagnosisType == "P" & Diagnosis1o %in% report_subtypes) |
          (DiagnosisType == "S" & Diagnosis2o %in% report_subtypes)
        )
    )
  }

  diag_code <- switch(
    report_diagnosis_type,
    "Primary"   = "P",
    "Secondary" = "S",
    "Benign"    = "B",
    "Unknown"   = "U",
    ""
  )

  diag_col <- switch(
    diag_code,
    "P" = "Diagnosis1o",
    "S" = "Diagnosis2o",
    "B" = "DiagnosisBn",
    "U" = "DiagnosisUn",
    ""
  )

  if (nzchar(diag_col) && all(c("DiagnosisType", diag_col) %in% names(d))) {
    d |>
      filter(
        DiagnosisType == diag_code,
        .data[[diag_col]] %in% report_subtypes
      )
  } else {
    d
  }
}

filter_by_tumour_size <- function(df, size_col, min_size, max_size) {
  if (!is.data.frame(df) || nrow(df) == 0 || !size_col %in% names(df)) return(df)

  df[[size_col]] <- suppressWarnings(as.numeric(df[[size_col]]))

  df |>
    dplyr::filter(
      is.na(.data[[size_col]]) |
        dplyr::between(.data[[size_col]], min_size, max_size)
    )
}

normalise_organs <- function(x) {
  if (is.null(x) || length(x) == 0 || anyNA(x)) return("All")
  if (length(x) == 1 && identical(x, "All")) return("All")
  x
}

report_organs <- normalise_organs(report_organs)

filter_patient_rows <- function(df) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  n0 <- nrow(df)
  debug_log("[FUNNEL] Start: %d rows", n0)

  d <- df |> filter(!is.na(FirstRxDate))
  debug_log("[FUNNEL] After non-NA FirstRxDate: %d (dropped %d)", nrow(d), n0 - nrow(d))

  n1 <- nrow(d)
  d <- d |> filter(FirstRxDate >= reportStart, FirstRxDate <= reportEnd)
  debug_log("[FUNNEL] After date range (%s to %s): %d (dropped %d)",
            reportStart, reportEnd, nrow(d), n1 - nrow(d))

  if (!identical(report_organs, "All")) {
    n2 <- nrow(d)
    d <- d |> filter(Organ %in% report_organs)
    debug_log("[FUNNEL] After organ filter (%s): %d (dropped %d)",
              paste(report_organs, collapse=","), nrow(d), n2 - nrow(d))
  }

  n3 <- nrow(d)
  d_before_diag <- d
  d <- filter_by_report_diagnosis(d, report_diagnosis_type, report_subtypes)
  debug_log("[FUNNEL] After diagnosis/subtype filter (%s / %s): %d (dropped %d)",
            report_diagnosis_type, paste(report_subtypes, collapse=","), nrow(d), n3 - nrow(d))

  if (isTRUE(DEBUG_MODE)) {
    dropped_rows <- dplyr::anti_join(d_before_diag, d, by = "ID")
    debug_table("[FUNNEL] Breakdown of dropped rows by DiagnosisType:", dropped_rows$DiagnosisType)
  }

  if (!identical(report_modality, "All")) {
    n4 <- nrow(d)
    d <- d |> filter(grepl(report_modality, RxModalities, fixed = TRUE))
    debug_log("[FUNNEL] After modality filter (%s): %d (dropped %d)",
              report_modality, nrow(d), n4 - nrow(d))
  }
  
  d
}

filter_patient_rows.old <- function(df) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  d <- df |>
    filter(!is.na(FirstRxDate)) |>
    filter(FirstRxDate >= reportStart, FirstRxDate <= reportEnd)

  if (!identical(report_organs, "All")) {
    d <- d |> filter(Organ %in% report_organs)
  }

  d <- filter_by_report_diagnosis(d, report_diagnosis_type, report_subtypes)

  if (!identical(report_modality, "All")) {
    d <- d |> filter(grepl(report_modality, RxModalities, fixed = TRUE))
  }

  d
}

filter_lesion_rows <- function(df) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  d <- df |>
    filter(!is.na(RxDate)) |>
    filter(RxDate >= reportStart, RxDate <= reportEnd)

  if (!identical(report_organs, "All")) {
    d <- d |> filter(Organ %in% report_organs)
  }

  d <- filter_by_report_diagnosis(d, report_diagnosis_type, report_subtypes)

  if (!identical(report_modality, "All")) {
    d <- d |> filter(grepl(report_modality, RxModality, fixed = TRUE))
  }

  d
}

filter_ae_rows <- function(df) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  d <- df

  if ("Grade" %in% names(d)) {
  d <- d |>
    mutate(
      GradeRaw = as.character(Grade),
      GradeNum = suppressWarnings(as.integer(GradeRaw)),
      GradeDisplay = dplyr::case_when(
        is.na(GradeRaw) | trimws(GradeRaw) == "" ~ "Unspecified",
        TRUE ~ GradeRaw
      )
    )
  }
  
  if ("DateofOnset" %in% names(d)) {
    d$DateofOnset <- suppressWarnings(as.Date(d$DateofOnset, tryFormats = c("%d-%m-%Y", "%Y-%m-%d", "%d/%m/%Y")))
  }
  if ("DateofResolution" %in% names(d)) {
    d$DateofResolution <- suppressWarnings(as.Date(d$DateofResolution, tryFormats = c("%d-%m-%Y", "%Y-%m-%d", "%d/%m/%Y")))
  }

  if ("DateofOnset" %in% names(d) || "DateofResolution" %in% names(d)) {
    onset_ok <- if ("DateofOnset" %in% names(d)) {
      !is.na(d$DateofOnset) & d$DateofOnset >= reportStart & d$DateofOnset <= reportEnd
    } else {
      rep(FALSE, nrow(d))
    }

    res_ok <- if ("DateofResolution" %in% names(d)) {
      !is.na(d$DateofResolution) & d$DateofResolution >= reportStart & d$DateofResolution <= reportEnd
    } else {
      rep(FALSE, nrow(d))
    }

    d <- d[onset_ok | res_ok, , drop = FALSE]
  }

  if (nrow(d) == 0) return(d)

  if (!identical(report_organs, "All") && "Organ" %in% names(d)) {
    d <- d |> filter(Organ %in% report_organs)
  }

  d <- filter_by_report_diagnosis(d, report_diagnosis_type, report_subtypes)

  if ("Grade" %in% names(d)) {
    d <- d |>
      mutate(
        Grade = as.character(Grade)
      )
  }

  d
}

# Get the filtered patient data and select only those where the MaxTumourSize is in reporting range
patient_data <- if (exists("cancerPerPatientData") && is.data.frame(cancerPerPatientData)) {
  filter_patient_rows(cancerPerPatientData)
} else {
  data.frame()
}

if (nrow(patient_data) > 0) {
  n_before_size <- nrow(patient_data)
  patient_data <- filter_by_tumour_size(
    patient_data,
    "MaxTumourSize",
    report_min_tumour_size,
    report_max_tumour_size
  )
  if (isTRUE(DEBUG_MODE)) {
    cat(sprintf("[FUNNEL] After tumour size filter (%s-%s mm): %d (dropped %d)\n",
            report_min_tumour_size, report_max_tumour_size, nrow(patient_data), n_before_size - nrow(patient_data)),
    file = stderr())
    missing_ltp_data <- patient_data |> filter(is.na(TimeLTPF) | is.na(StatusLTPF))
    debug_log("[FUNNEL] Of %d final patients, %d are missing TimeLTPF/StatusLTPF", nrow(patient_data), nrow(missing_ltp_data))
    
    if (nrow(missing_ltp_data) > 0) {
      debug_log("[FUNNEL] Missing-outcome patient ID(s): %s", paste(missing_ltp_data$ID, collapse = ", "))
    }
  }
  

  # Derive the bare patient ID (referral suffix stripped) unconditionally -
  # lesion_data and ae_data are keyed on PtID without the "-N" referral
  # suffix, so keep_ids must be in the same bare format to match correctly.
  patient_data <- patient_data |>
    dplyr::mutate(PtID = sub("-[0-9]+$", "", ID))

  # Add age from cancerData using the patient-level ID
  if (exists("cancerData") && is.data.frame(cancerData)) {
    age_lookup <- cancerData |>
      dplyr::transmute(
        PtID = as.character(ID),
        AgeOnFirstRx = suppressWarnings(as.numeric(AgeOnFirstRx))
      ) |>
      dplyr::distinct(PtID, .keep_all = TRUE)
  
    patient_data <- patient_data |>
      dplyr::mutate(PtID = as.character(sub("-[0-9]+$", "", ID))) |>
      dplyr::left_join(age_lookup, by = "PtID")
    
  }

  cat("\n===== AGE DIAGNOSTIC =====\n")
  cat("cancerData exists:", exists("cancerData"), "\n")
  if (exists("cancerData")) {
    cat("cancerData is.data.frame:", is.data.frame(cancerData), "\n")
    if (is.data.frame(cancerData)) {
      cat("cancerData columns:", paste(names(cancerData), collapse = ", "), "\n")
      cat("cancerData rows:", nrow(cancerData), "\n")
    }
  }
  cat("AgeOnFirstRx in patient_data:", "AgeOnFirstRx" %in% names(patient_data), "\n")
  if ("AgeOnFirstRx" %in% names(patient_data)) {
    cat("Non-NA age count:", sum(!is.na(patient_data$AgeOnFirstRx)), "of", nrow(patient_data), "\n")
  }

  keep_ids <- unique(patient_data$PtID)

lesion_data <- if (exists("cancerPerLesionData") && is.data.frame(cancerPerLesionData)) {
  filter_lesion_rows(cancerPerLesionData) |>
    dplyr::filter(PtID %in% keep_ids)
} else {
  data.frame()
}

lesion_data <- filter_by_tumour_size(
  lesion_data,
  "TumourSize",
  report_min_tumour_size,
  report_max_tumour_size
)

ae_data <- if (exists("aeData") && is.data.frame(aeData)) {
    filter_ae_rows(aeData) |>
      dplyr::filter(PtID %in% keep_ids)
  } else {
    data.frame()
  }
} else {
  lesion_data <- data.frame()
  ae_data <- data.frame()
}

if (nrow(patient_data) > 0 && "MaxTumourSize" %in% names(patient_data)) {
  patient_data$MaxTumourSize <- suppressWarnings(as.numeric(patient_data$MaxTumourSize))
}
if (nrow(lesion_data) > 0 && "TumourSize" %in% names(lesion_data)) {
  lesion_data$TumourSize <- suppressWarnings(as.numeric(lesion_data$TumourSize))
}

# TimeSurvival and TimeLTPFOS are stored in years at source, unlike
# TimeLTPF/TimeLTPEpisode which are already in days. Convert to days here,
# once, so every downstream consumer (get_os_rate(), followup_days) is
# working on a consistent time scale.
if (nrow(patient_data) > 0 && "TimeSurvival" %in% names(patient_data)) {
  patient_data$TimeSurvival <- suppressWarnings(as.numeric(patient_data$TimeSurvival)) * 365.25
}
if (nrow(patient_data) > 0 && "TimeLTPFOS" %in% names(patient_data)) {
  patient_data$TimeLTPFOS <- suppressWarnings(as.numeric(patient_data$TimeLTPFOS)) * 365.25
}

cat("\n===== AE DATA COLUMN NAMES =====\n")
print(names(aeData))
cat("NA names:", which(is.na(names(aeData))), "\n")
cat("Blank names:", which(names(aeData) == ""), "\n")

ae_data <- if (exists("aeData") && is.data.frame(aeData)) {
  filter_ae_rows(aeData)
} else {
  data.frame()
}

patient_sex_summary <- if (nrow(patient_data) > 0 && "Gender" %in% names(patient_data)) {
  sex_counts <- patient_data |>
    filter(!is.na(Gender) & Gender != "") |>
    count(Gender, name = "n") |>
    ungroup()

  sex_total <- sum(sex_counts$n)

  sex_counts |>
    mutate(pct = if (sex_total > 0) n / sex_total else NA_real_)
} else {
  tibble::tibble(Gender = character(0), n = integer(0), pct = numeric(0))
}

rxDoneReferralLevel <- if (exists("rxDoneData") && is.data.frame(rxDoneData)) {
  d <- rxDoneData
  bad <- is.na(names(d)) | names(d) == ""
  if (any(bad)) names(d)[bad] <- paste0("unnamed_col_", seq_len(sum(bad)))
  d |>
    filter(!(ID %in% c("000-1", "00000-1", "000000-1"))) |>
    distinct(ID, .keep_all = TRUE)
} else {
  data.frame()
}

meanTreatmentsPerPatient <-
  rxDoneReferralLevel |>
  mutate(PtID = sub("-[0-9]+$", "", ID)) |>
  count(PtID) |>
  summarise(mean = mean(n, na.rm = TRUE)) |>
  pull(mean)

meanReferralsPerPatient <-
  rxDoneReferralLevel |>
  mutate(PtID = sub("-[0-9]+$", "", ID)) |>
  count(PtID) |>
  summarise(mean = mean(n, na.rm = TRUE)) |>
  pull(mean)

meanTumoursPerPatient <-
  rxDoneReferralLevel |>
  mutate(PtID = sub("-[0-9]+$", "", ID)) |>
  group_by(PtID) |>
  summarise(Tumours = sum(TumourCount, na.rm = TRUE), .groups = "drop") |>
  summarise(mean = mean(Tumours, na.rm = TRUE)) |>
  pull(mean)

tumour_summary <- if (nrow(lesion_data) > 0 && "TumourSize" %in% names(lesion_data)) {
  lesion_data |>
    summarise(
      n = sum(!is.na(TumourSize)),
      median = median(TumourSize, na.rm = TRUE),
      sd = sd(TumourSize, na.rm = TRUE),
      mean = mean(TumourSize, na.rm = TRUE)
    )
} else {
  tibble::tibble(n = 0, median = NA_real_, sd = NA_real_, mean = NA_real_)
}

followup_days <- report_max_years_followup * 365.25

status_to_event <- function(status) {
  x <- status[!is.na(status)]
  if (length(x) == 0) return(logical(0))
  ux <- sort(unique(x))
  if (all(ux %in% c(0, 1))) return(status == 1)
  if (all(ux %in% c(1, 2))) return(status == 2)
  if (is.logical(status)) return(status)
  status != 0
}

get_ltp_rate <- function(df, time_col, status_col) {
  if (!is.data.frame(df) || nrow(df) == 0) return(NA_real_)
  if (!(time_col %in% names(df)) || !(status_col %in% names(df))) return(NA_real_)
  d <- df |> filter(!is.na(.data[[time_col]]), !is.na(.data[[status_col]]))
  if (nrow(d) == 0) return(NA_real_)
  cat("rows:", nrow(d), "\n")
print(table(d[[status_col]], useNA = "ifany"))

  fit <- survfit2(Surv(d[[time_col]], status_to_event(d[[status_col]])) ~ 1, data = d)
  s <- summary(fit, times = followup_days, extend = TRUE)
  if (length(s$surv) == 0) return(NA_real_)
  s$surv[1]
}

get_os_rate <- function(df, time_col, status_col) {
  if (!is.data.frame(df) || nrow(df) == 0) return(NA_real_)
  if (!(time_col %in% names(df)) || !(status_col %in% names(df))) return(NA_real_)
  d <- df |> filter(!is.na(.data[[time_col]]), !is.na(.data[[status_col]]))
  if (nrow(d) == 0) return(NA_real_)
  fit <- survfit2(Surv(d[[time_col]], status_to_event(d[[status_col]])) ~ 1, data = d)
  s <- summary(fit, times = followup_days, extend = TRUE)
  if (length(s$surv) == 0) return(NA_real_)
  s$surv[1]
}

apply_ltp_rule_patient <- function(df, ignore_first_ltp = FALSE) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)
  d <- df
  if (isTRUE(ignore_first_ltp) && "LTPCountMax" %in% names(d)) {
    idx <- !is.na(d$LTPCountMax) & d$LTPCountMax == 1
    d$StatusLTPF[idx] <- 1
  }
  d
}

apply_ltp_rule_lesion <- function(df, ignore_first_ltp = FALSE) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)
  d <- df
  if (isTRUE(ignore_first_ltp) && all(c("PtID", "LTPDate", "StatusLTPEpisode") %in% names(d))) {
    # use the same logic as your plot code:
    # censor episodes with only one subsequent Rx after LTP
    for (i in which(!is.na(d$LTPDate) & d$StatusLTPEpisode == 2)) {
      ptID <- d$PtID[i]
      ltpDt <- d$LTPDate[i]

      laterRxCount <- length(unique(
        lesion_data$RxNo[
          lesion_data$PtID == ptID &
            !is.na(lesion_data$RxDate) &
            lesion_data$RxDate > ltpDt
        ]
      ))

      if (laterRxCount == 1) {
        d$StatusLTPEpisode[i] <- 1
      }
    }
  }
  d
}

patient_data_ltp <- apply_ltp_rule_patient(patient_data, FALSE)
lesion_data_ltp  <- apply_ltp_rule_lesion(lesion_data, FALSE)
patient_ltp <- get_ltp_rate(patient_data_ltp, "TimeLTPF", "StatusLTPF")
#lesion_ltp  <- get_ltp_rate(lesion_data_ltp, "TimeLTPEpisode", "StatusLTPEpisode")
lesion_ltp <- get_ltp_rate(filteredSurvivalData, "TimeLTPF", "StatusLTPF")

patient_os  <- get_os_rate(patient_data, "TimeSurvival", "StatusOverallSurvival")
patient_ltpf_os <- get_os_rate(patient_data, "TimeLTPFOS", "StatusLTPFOS")

km_risk_title <- function(x) if (is.na(x)) "NA" else scales::percent(x, accuracy = 0.1)

make_female_male_unknown_table <- function(df) {
  if (!is.data.frame(df) || nrow(df) == 0 || !("Gender" %in% names(df))) {
    return(tibble::tibble(Gender = character(0), n = integer(0), pct = numeric(0)))
  }
  df |>
    filter(!is.na(Gender) & Gender != "") |>
    count(Gender, name = "n") |>
    mutate(pct = n / sum(n))
}

fmt_param <- function(x) {
  x <- setdiff(as.character(x), "All")
  if (length(x) == 0) "All" else paste(x, collapse = ", ")
}

anonymise_ptid <- function(x) {
  vapply(as.character(x), function(id) {

    parts <- strsplit(id, "-", fixed = TRUE)[[1]]

    pt <- parts[1]
    chars <- strsplit(pt, "", fixed = TRUE)[[1]]
    chars[c(TRUE, FALSE)] <- "\\*"
    pt_masked <- paste(chars, collapse = "")

    if (length(parts) > 1) {
      paste0(pt_masked, "-", paste(parts[-1], collapse = "-"))
    } else {
      pt_masked
    }

  }, character(1))
}
```

## Report Parameters

| Parameter | Value |
|:----------|:------|
| **Report generated** | `r format(Sys.time(), "%a %d %B %Y %H:%M")` |
| **Report period** | `r format(reportStart, "%d %B %Y")` – `r format(reportEnd, "%d %B %Y")` |
| **Organ(s)** | `r if (identical(report_organs, "All")) "All" else paste(report_organs, collapse = ", ")` |
| **Diagnosis type** | `r fmt_param(report_diagnosis_type)` |
| **Subtype(s)** | `r fmt_param(report_subtypes)` |
| **Tumour Size Range** | `r fmt_param(paste0(report_min_tumour_size, "-", report_max_tumour_size," mm"))` |
| **Gender(s)** | `r paste(report_genders, collapse = ", ")` |
| **Modality** | `r report_modality` |
| **Minimum follow-up** | `r report_min_months_followup` months |
| **Maximum follow-up** | `r report_max_years_followup` years |
| **Relaxed LTP definition** | `r if (report_include_ignore_first_ltp) "Included" else "Not included"` |

---

## Outcome Summary

```{r overview-table, echo=FALSE}
overview_tbl <- tibble::tibble(
  Metric = c(
    "Patients",
    "Tumours treated",
    "Mean referrals per patient",
    "Mean tumours treated per patient",
    "Median tumour size (mm)",
    "SD tumour size (mm)",
    paste0(report_max_years_followup, "-year OS"),
    paste0(report_max_years_followup, "-year LTP-free OS"),
    paste0(report_max_years_followup, "-year LTP (per patient)"),
    paste0(report_max_years_followup, "-year LTP (per lesion)")
  ),
  Value = c(
    nrow(patient_data),
    nrow(lesion_data),
    round(meanReferralsPerPatient, 2),
    round(meanTumoursPerPatient, 2),
    round(tumour_summary$median[1], 1),
    round(tumour_summary$sd[1], 1),
    km_risk_title(patient_os),
    km_risk_title(patient_ltpf_os),
    km_risk_title(patient_ltp),
    km_risk_title(lesion_ltp)
  )
)

kable(overview_tbl, caption = "Cancer outcomes summary") |>
  kableExtra::kable_styling(full_width = FALSE)
```

## Tumour size and sex distribution

```{r tumour-size-and-demographics, echo=FALSE, results='asis'}

# Tumour size table
tumour_tbl <- tibble::tibble(
  Metric = c(
    "Count with size recorded",
    "Median size (mm)",
    "SD size (mm)",
    "Mean size (mm)"
  ),
  Value = c(
    tumour_summary$n[1],
    round(tumour_summary$median[1], 1),
    round(tumour_summary$sd[1], 1),
    round(tumour_summary$mean[1], 1)
  )
)

# Demographics table
age_vals <- numeric(0)

if (exists("cancerData") && is.data.frame(cancerData) && nrow(patient_data) > 0) {
  pt_ids <- unique(trimws(as.character(sub("-[0-9]+$", "", patient_data$ID))))

  age_lookup <- cancerData[, c("ID", "AgeOnFirstRx")]
  age_lookup$ID <- trimws(as.character(age_lookup$ID))
  age_lookup$AgeOnFirstRx <- suppressWarnings(as.numeric(age_lookup$AgeOnFirstRx))

  age_vals <- age_lookup$AgeOnFirstRx[match(pt_ids, age_lookup$ID)]
  age_vals <- age_vals[is.finite(age_vals)]
}
demo_counts <- if (nrow(patient_data) > 0 && "Gender" %in% names(patient_data)) {
  patient_data |>
    dplyr::mutate(Gender = ifelse(is.na(Gender) | Gender == "", "Unknown", Gender)) |>
    dplyr::count(Gender, name = "n")
} else {
  tibble::tibble(Gender = character(0), n = integer(0))
}

female_n  <- if ("Female"  %in% demo_counts$Gender) demo_counts$n[demo_counts$Gender == "Female"]  else 0
male_n    <- if ("Male"    %in% demo_counts$Gender) demo_counts$n[demo_counts$Gender == "Male"]    else 0
unknown_n <- if ("Unknown" %in% demo_counts$Gender) demo_counts$n[demo_counts$Gender == "Unknown"] else 0
demo_total <- sum(demo_counts$n)

demo_tbl <- tibble::tibble(
  Metric = c("Female", "Male", "Unknown", "Mean age (years)", "SD age (years)"),
  Value = c(
    sprintf("%d (%.1f%%)", female_n,  if (demo_total > 0) 100 * female_n  / demo_total else 0),
    sprintf("%d (%.1f%%)", male_n,    if (demo_total > 0) 100 * male_n    / demo_total else 0),
    sprintf("%d (%.1f%%)", unknown_n, if (demo_total > 0) 100 * unknown_n / demo_total else 0),
    if (length(age_vals) > 0) sprintf("%.1f", mean(age_vals)) else "NA",
    if (length(age_vals) > 1) sprintf("%.1f", sd(age_vals)) else "NA"
  )
)

tumour_html <- kable(tumour_tbl, caption = "Tumour size") |>
  kableExtra::kable_styling(full_width = FALSE) |>
  as.character()

demo_html <- kable(demo_tbl, caption = "Demographics") |>
  kableExtra::kable_styling(full_width = FALSE) |>
  as.character()

cat(
  '<div style="display:flex; gap:25px; align-items:flex-start;">',
  '<div style="flex:1;">', tumour_html, '</div>',
  '<div style="flex:1;">', demo_html, '</div>',
  '</div>'
)
```


```{r tumour-size-hist, echo=FALSE, fig.height=4.5}
if (nrow(lesion_data) > 0 && "TumourSize" %in% names(lesion_data)) {
  ggplot(lesion_data |> filter(!is.na(TumourSize)), aes(x = TumourSize)) +
    geom_histogram(bins = 20) +
    labs(
      title = "Tumour size distribution",
      x = "Tumour size (mm)",
      y = "Count"
    ) +
    theme_minimal(base_size = 12)
} else {
  ggplot() +
    annotate("text", x = 0.5, y = 0.5, label = "No tumour size data available", size = 6) +
    theme_void()
}
```

```{r sex-dist-plot, echo=FALSE, fig.height=4.2}
if (nrow(patient_sex_summary) > 0) {
ggplot(
  patient_sex_summary |>
    mutate(Gender = factor(Gender,
      levels = c("Female", "Male", "Unknown"))),
  aes(x = Gender, y = n)
) +
  geom_col() +
  geom_text(aes(label = n), vjust = -0.3) +
  scale_x_discrete(drop = FALSE) +
  labs(
    title = "Sex distribution",
    x = NULL,
    y = "Patients"
  ) +
  theme_minimal(base_size = 12)
} else {
  ggplot() +
    annotate("text", x = 0.5, y = 0.5, label = "No sex data available", size = 6) +
    theme_void()
}
```



## LTP curves at `r report_max_years_followup` years

```{r ltp-patient-plot, echo=FALSE, fig.height=4.8}
  makeRecurrencePlot(
    strStart = format(reportStart, "%d/%m/%Y"),
    strEnd = format(reportEnd, "%d/%m/%Y"),
    selectedOrgans = report_organs,
    selectedDiagnosisType = report_diagnosis_type,
    selectedSubtypes = report_subtypes,
    selectedGenders = report_genders,
    selectedModality = report_modality,
    minMonthsFollowup = report_min_months_followup,
    maxYearsFollowup = report_max_years_followup,
    minTumourSize = report_min_tumour_size,
    maxTumourSize = report_max_tumour_size,
    ignoreFirstLTP = FALSE,
    ltpAnalysisUnit = "patient"
  )

  if (report_include_ignore_first_ltp)
  {
    makeRecurrencePlot(
      strStart = format(reportStart, "%d/%m/%Y"),
      strEnd = format(reportEnd, "%d/%m/%Y"),
      selectedOrgans = report_organs,
      selectedDiagnosisType = report_diagnosis_type,
      selectedSubtypes = report_subtypes,
      selectedGenders = report_genders,
      selectedModality = report_modality,
      minMonthsFollowup = report_min_months_followup,
      maxYearsFollowup = report_max_years_followup,
      minTumourSize = report_min_tumour_size,
      maxTumourSize = report_max_tumour_size,
      ignoreFirstLTP = TRUE,
      ltpAnalysisUnit = "patient"
    )
  }
```

```{r ltp-lesion-plot, echo=FALSE, fig.height=4.8}
makeRecurrencePlot(
  strStart = format(reportStart, "%d/%m/%Y"),
  strEnd = format(reportEnd, "%d/%m/%Y"),
  selectedOrgans = report_organs,
  selectedDiagnosisType = report_diagnosis_type,
  selectedSubtypes = report_subtypes,
  selectedGenders = report_genders,
  selectedModality = report_modality,
  minMonthsFollowup = report_min_months_followup,
  maxYearsFollowup = report_max_years_followup,
  minTumourSize = report_min_tumour_size,
  maxTumourSize = report_max_tumour_size,
  ignoreFirstLTP = FALSE,
  ltpAnalysisUnit = "lesion"
)

if (report_include_ignore_first_ltp)
{
  makeRecurrencePlot(
    strStart = format(reportStart, "%d/%m/%Y"),
    strEnd = format(reportEnd, "%d/%m/%Y"),
    selectedOrgans = report_organs,
    selectedDiagnosisType = report_diagnosis_type,
    selectedSubtypes = report_subtypes,
    selectedGenders = report_genders,
    selectedModality = report_modality,
    minMonthsFollowup = report_min_months_followup,
    maxYearsFollowup = report_max_years_followup,
    minTumourSize = report_min_tumour_size,
    maxTumourSize = report_max_tumour_size,
    ignoreFirstLTP = TRUE,
    ltpAnalysisUnit = "lesion"
  )
}
```

## Survival curves at `r report_max_years_followup` years

```{r os-plot, echo=FALSE, fig.height=4.8}
  makeSurvivalPlot(
    strStart = format(reportStart, "%d/%m/%Y"),
    strEnd = format(reportEnd, "%d/%m/%Y"),
    selectedOrgans = report_organs,
    selectedDiagnosisType = report_diagnosis_type,
    selectedSubtypes = report_subtypes,
    selectedGenders = report_genders,
    selectedModality = report_modality,
    survivalType = 0,
    minMonthsFollowup = report_min_months_followup,
    maxYearsFollowup = report_max_years_followup,
    minTumourSize = report_min_tumour_size,
    maxTumourSize = report_max_tumour_size,
    ignoreFirstLTP = FALSE
  )

  if (report_include_ignore_first_ltp) {
    makeSurvivalPlot(
    strStart = format(reportStart, "%d/%m/%Y"),
    strEnd = format(reportEnd, "%d/%m/%Y"),
    selectedOrgans = report_organs,
    selectedDiagnosisType = report_diagnosis_type,
    selectedSubtypes = report_subtypes,
    selectedGenders = report_genders,
    selectedModality = report_modality,
    survivalType = 0,
    minMonthsFollowup = report_min_months_followup,
    maxYearsFollowup = report_max_years_followup,
    minTumourSize = report_min_tumour_size,
    maxTumourSize = report_max_tumour_size,
    ignoreFirstLTP = TRUE
  )
}
```

```{r ltpf-os-plot, echo=FALSE, fig.height=4.8}

  makeSurvivalPlot(
    strStart = format(reportStart, "%d/%m/%Y"),
    strEnd = format(reportEnd, "%d/%m/%Y"),
    selectedOrgans = report_organs,
    selectedDiagnosisType = report_diagnosis_type,
    selectedSubtypes = report_subtypes,
    selectedGenders = report_genders,
    selectedModality = report_modality,
    survivalType = 2,
    minMonthsFollowup = report_min_months_followup,
    maxYearsFollowup = report_max_years_followup,
    minTumourSize = report_min_tumour_size,
    maxTumourSize = report_max_tumour_size,
    ignoreFirstLTP = FALSE
  )

if (report_include_ignore_first_ltp)
{
  makeSurvivalPlot(
    strStart = format(reportStart, "%d/%m/%Y"),
    strEnd = format(reportEnd, "%d/%m/%Y"),
    selectedOrgans = report_organs,
    selectedDiagnosisType = report_diagnosis_type,
    selectedSubtypes = report_subtypes,
    selectedGenders = report_genders,
    selectedModality = report_modality,
    survivalType = 2,
    minMonthsFollowup = report_min_months_followup,
    maxYearsFollowup = report_max_years_followup,
    minTumourSize = report_min_tumour_size,
    maxTumourSize = report_max_tumour_size,
    ignoreFirstLTP = TRUE
  )
}

```

## Adverse events

```{r adverse-events-summary-table, echo=FALSE, results='asis'}

if (nrow(ae_data) > 0)
{
  ae_tbl <- ae_data

  if (!"GradeDisplay" %in% names(ae_tbl)) {
    if ("Grade" %in% names(ae_tbl)) {
      ae_tbl$GradeDisplay <- ifelse(
        is.na(ae_tbl$Grade) | trimws(as.character(ae_tbl$Grade)) == "",
        "Unspecified",
        as.character(ae_tbl$Grade)
      )
    } else {
      ae_tbl$GradeDisplay <- "Unspecified"
    }
  }
  report_ptids <- patient_data |>
    mutate(PtID = sub("-[0-9]+$", "", ID)) |>
    pull(PtID) |>
    unique()

  rxDoneReport <- rxDoneReferralLevel |>
    mutate(PtID = sub("-[0-9]+$", "", ID)) |>
    filter(PtID %in% report_ptids)

  if ("RxDate" %in% names(rxDoneReport)) {
    rxDoneReport <- rxDoneReport |>
      filter(RxDate >= reportStart, RxDate <= reportEnd)
  }

  n_patients <- nrow(patient_data)
  n_treatments <- nrow(rxDoneReport)
  n_tumours <- nrow(lesion_data)
  n_ae <- nrow(ae_tbl)
  n_ae_patients <- dplyr::n_distinct(ae_tbl$PtID)

  grade_counts <- c(
    `Grade 5` = sum(ae_tbl$GradeDisplay == "5", na.rm = TRUE),
    `Grade 4` = sum(ae_tbl$GradeDisplay == "4", na.rm = TRUE),
    `Grade 3` = sum(ae_tbl$GradeDisplay == "3", na.rm = TRUE),
    `Grade 2` = sum(ae_tbl$GradeDisplay == "2", na.rm = TRUE),
    `Grade 1` = sum(ae_tbl$GradeDisplay == "1", na.rm = TRUE),
    `Unspecified` = sum(ae_tbl$GradeDisplay == "Unspecified", na.rm = TRUE)
  )


  ae_summary <- tibble::tibble(
    Metric = c(
      "Patients",
      "Treatments",
      "Tumours treated",
      "Patients with ≥1 AE",
      "Total adverse events"
      ),
    Value = c(
      n_patients,
      n_treatments,
      n_tumours,
      sprintf("%d (%.1f%%)", n_ae_patients, 100 * n_ae_patients / n_patients),
      n_ae
    )
  )

  severity_tbl <- ae_tbl |>
    mutate(
      Severity = dplyr::case_when(
        GradeDisplay == "Unspecified" ~ "Unspecified",
        TRUE ~ paste0("Grade ", GradeDisplay)
      )
    ) |>
    count(Severity, name = "n") |>
    mutate(
      pct = n / sum(n),
      Severity = factor(Severity, levels = c("Unspecified", "Grade 5", "Grade 4", "Grade 3", "Grade 2", "Grade 1"))
    ) |>
    arrange(Severity) |>
    mutate(pct = scales::percent(pct, accuracy = 1.1))
  
  summary_html <-
    kable(ae_summary, caption = "Adverse event summary") |>
    kableExtra::kable_styling(full_width = FALSE) |>
    as.character()
  
  severity_html <-
    kable(severity_tbl, caption = "Severity distribution") |>
    kableExtra::kable_styling(full_width = FALSE) |>
    as.character()
  
  cat(
    '<div style="display:flex; gap:25px; align-items:flex-start;">',
    '<div style="flex:1;">', summary_html, '</div>',
    '<div style="flex:1;">', severity_html, '</div>',
    '</div>'
  )
}
```



```{r adverse-events-table, echo=FALSE, results='asis'}

if (nrow(ae_data) > 0) {
  
  ae_tbl <- ae_data

  keep_cols <- intersect(
    c("ID", "PtID", "Organ", "DiagnosisType", "Diagnosis1o", "Diagnosis2o",
      "DiagnosisBn", "DiagnosisUn", "Complication", "GradeDisplay",
      "DateofOnset", "DateofResolution", "Duration"),
    names(ae_tbl)
  )

  ae_tbl <- ae_tbl |>
    select(all_of(keep_cols)) |>
    mutate(
      GradeOrder = dplyr::case_when(
        GradeDisplay == "5" ~ 1L,
        GradeDisplay == "4" ~ 2L,
        GradeDisplay == "3" ~ 3L,
        GradeDisplay == "2" ~ 4L,
        GradeDisplay == "1" ~ 5L,
        TRUE ~ 6L   # Unspecified (and anything else) goes last
      )
    ) |>
    arrange(GradeOrder, desc(DateofOnset)) |>
    select(-GradeOrder)
  
    if (nrow(ae_tbl) > 0) {
      
      if (reportAnonymised) {
        if ("PtID" %in% names(ae_tbl)) {
          ae_tbl$PtID <- anonymise_ptid(ae_tbl$PtID)
        }
        if ("ID" %in% names(ae_tbl)) {
          ae_tbl$ID <- anonymise_ptid(ae_tbl$ID)
        }
        for (col in c("DateofOnset", "DateofResolution")) {
          if (col %in% names(ae_tbl)) {
            ae_tbl[[col]] <- ifelse(
              is.na(ae_tbl[[col]]),
              "",
              format(as.Date(ae_tbl[[col]]), "%b %Y")
            )
          }
        }
      }
      
      kable(
        ae_tbl,
        caption = "Adverse events",
        row.names = FALSE) |>
        kableExtra::kable_styling(full_width = FALSE)

    } else {
      cat("No adverse events in the selected cohort.")
    }
  }
```



## Credits

```{r reportLogo, warning=FALSE}
logo_src <- here("www", "TARGETPlotterLogo.png")
if (file.exists(logo_src)) {
  knitr::include_graphics(normalizePath(logo_src))
} else {
  cat("<!-- TARGETPlotterLogo.png logo not available -->")
}
```

<br>
Report Report Developer: Dr. Paul Lyon<br>
TARGET-UK Lead: Dr. Paul Lyon, FRCR
