---
title: "TARGET-UK: Renal Function Report"
output:
  html_document:
    toc: true
    self_contained: true
date: "`r format(Sys.Date(), '%d %B %Y')`"
params:
  report_start_date: !r Sys.Date() - 365
  report_end_date: !r Sys.Date()
  report_organs: "All"
  report_diagnosis_type: "All"
  report_subtypes: ["All"]
  report_genders: ["Female", "Male", "Unknown"]
  report_modality: "All"
  report_min_tumour_size: 0
  report_max_tumour_size: 100
  report_min_months_followup: 3
  report_max_months_followup: 5
  report_include_aki_bin: FALSE
  report_renal_fn_anonymised: FALSE
  report_renal_fn_pt_plots: FALSE
---

```{css, echo=FALSE}
body { font-size: 14px; }
table {
  font-size: 13px;
  width: 100% !important;
  table-layout: auto;
}
th, td {
  padding: 4px 8px !important;
  font-size: 13px;
}
img { max-width: 100% !important; height: auto !important; }

@media print {
  @page {
    size: A4 portrait;
    margin: 8mm 6mm 8mm 6mm;
  }
  body {
    font-size: 11px;
    width: 198mm;
  }
  table {
    font-size: 10px;
    page-break-inside: avoid;
    table-layout: auto;
  }
  th, td { padding: 2px 4px !important; font-size: 10px; }
  img, .plot {
    max-width: 196mm !important;
    width: 196mm !important;
    height: auto !important;
    page-break-inside: avoid;
  }
  .figure {
    max-width: 196mm !important;
    page-break-inside: avoid;
  }
  h2 { page-break-before: auto; }
}
```


```{r setup, include=FALSE}

DEBUG_MODE <- toupper(Sys.getenv("DEBUG_MODE", unset = "FALSE")) == "TRUE"
DEBUG_MODE=TRUE

if (isTRUE(DEBUG_MODE))
{
  options(error = function() {
    debug_log("ERROR OCCURRED")
    debug_log(paste(capture.output(traceback()), collapse="\n"))
  })
}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(fig.width = 10, fig.height = 5, dpi = 120)
options(knitr.table.format = "html")

library(dplyr)
library(ggplot2)
library(scales)
library(kableExtra)
library(htmltools)
library(gridExtra)
library(later)
library(patchwork)
library(ggrepel)

report_start_date               <- params$report_start_date
report_end_date                 <- params$report_end_date
report_organs                   <- params$report_organs
report_diagnosis_type           <- params$report_diagnosis_type
report_subtypes                 <- params$report_subtypes
report_genders                  <- params$report_genders
report_modality                 <- unique(params$report_modality)
report_min_tumour_size          <- params$report_min_tumour_size
report_max_tumour_size          <- params$report_max_tumour_size
report_max_months_followup      <- as.numeric(params$report_max_months_followup)
report_min_months_followup      <- as.numeric(params$report_min_months_followup)
reportStart                     <- as.Date(params$report_start_date)
reportEnd                       <- as.Date(params$report_end_date)
report_include_aki_bin          <- isTRUE(params$report_include_aki_bin)
reportAnonymised                <- isTRUE(params$report_renal_fn_anonymised)
reportIndividualPtPlots         <- isTRUE(params$report_renal_fn_pt_plots)

if (is.null(report_modality) || length(report_modality) == 0)
{
  report_modality <- "All"
}
report_modality <- as.character(report_modality)
if ("All" %in% report_modality) # If All selected, ignore other selections
{
  report_modality <- "All"
}

debug_log <- function(...) {
  if (isTRUE(DEBUG_MODE)) {
    txt <- paste(
      capture.output(...),
      collapse = "\n"
    )
    cat(txt, "\n", file = stderr())
  }
}

debug_table <- function(label, x) {
  if (isTRUE(DEBUG_MODE)) {
    cat(label, "\n", file = stderr(), sep = "")
    cat(capture.output(print(table(x, useNA = "ifany"))), sep = "\n", file = stderr())
  }
}

filter_by_report_diagnosis <- function(d, report_diagnosis_type, report_subtypes) {
  if (!is.data.frame(d) || nrow(d) == 0) return(d)
  if (is.null(report_diagnosis_type) || identical(report_diagnosis_type, "All")) return(d)

  if (is.null(report_subtypes)) report_subtypes <- "All"
  report_subtypes <- setdiff(as.character(report_subtypes), "All")

  if (report_diagnosis_type == "1o & 2o") {
    return(
      d |>
        filter(
          (DiagnosisType == "P" & Diagnosis1o %in% report_subtypes) |
          (DiagnosisType == "S" & Diagnosis2o %in% report_subtypes)
        )
    )
  }

  diag_code <- switch(
    report_diagnosis_type,
    "Primary"   = "P",
    "Secondary" = "S",
    "Benign"    = "B",
    "Unknown"   = "U",
    ""
  )

  diag_col <- switch(
    diag_code,
    "P" = "Diagnosis1o",
    "S" = "Diagnosis2o",
    "B" = "DiagnosisBn",
    "U" = "DiagnosisUn",
    ""
  )

  if (nzchar(diag_col) && all(c("DiagnosisType", diag_col) %in% names(d))) {
    d |>
      filter(
        DiagnosisType == diag_code,
        .data[[diag_col]] %in% report_subtypes
      )
  } else {
    d
  }
}

# Builds FollowUp interval breaks/labels dynamically, scaled to
# report_max_months_followup, rather than a fixed 5-year scaffold.
# Always starts with a -6 to 0 month "Baseline" window, then 3/6-month
# resolution out to 1 year, then yearly thereafter, truncated (and closed)
# exactly at report_max_months_followup.
build_followup_bins <- function(max_months_followup,
                                include_aki_bin = FALSE) {

  candidates <- c(0, 3, 6, 12, 24, 36, 48, 60, 72, 84, 96, 108, 120)

  max_months_followup <- suppressWarnings(as.numeric(max_months_followup))

  if (is.na(max_months_followup) || max_months_followup <= 0) {
    max_months_followup <- 60
  }

  # 2 weeks expressed in months
  aki_months <- 14 / 30.44

  if (isTRUE(include_aki_bin)) {
    candidates <- sort(unique(c(0, aki_months, candidates)))
  }

  breaks <- candidates[candidates <= max_months_followup]

  if (length(breaks) == 0 || breaks[length(breaks)] < max_months_followup) {
    breaks <- c(breaks, max_months_followup)
  }

  if (breaks[1] != 0) {
    breaks <- c(0, breaks)
  }

  breaks <- unique(breaks)

  # Prepend baseline window
  breaks <- c(-6, breaks)

  label_interval <- function(a, b) {
  
    if (a == -6 && b == 0)
      return("Baseline")
  
    if (a == 0 && b < 1)
      return("0-2 wk")
  
    if (b == 3)
      return("2 wk-3 m")
  
    if (b <= 12)
      return(paste0(round(a), "-", round(b), " m"))
  
    if (a %% 12 == 0 && b %% 12 == 0)
      return(paste0(a / 12, "-", b / 12, " y"))
  
    paste0(round(a, 2), "-", round(b, 2), " m")
  }

  labels <- vapply(
    seq_len(length(breaks) - 1),
    function(i) label_interval(breaks[i], breaks[i + 1]),
    character(1)
  )

  list(
    breaks = breaks,
    labels = labels
  )
}

followup_bins <- build_followup_bins(report_max_months_followup, report_include_aki_bin)

filter_by_tumour_size <- function(df, size_col, min_size, max_size) {
  if (!is.data.frame(df) || nrow(df) == 0 || !size_col %in% names(df)) return(df)

  df[[size_col]] <- suppressWarnings(as.numeric(df[[size_col]]))

  df |>
    dplyr::filter(
      is.na(.data[[size_col]]) |
        dplyr::between(.data[[size_col]], min_size, max_size)
    )
}

normalise_organs <- function(x) {
  if (is.null(x) || length(x) == 0 || anyNA(x)) return("All")
  if (length(x) == 1 && identical(x, "All")) return("All")
  x
}

report_organs <- normalise_organs(report_organs)

filter_patient_rows <- function(df) {
  
debug_log("filter_patient_rows input columns:")
  debug_log(names(df))

  debug_log("Rows:")
  debug_log(nrow(df))

  # initialise counters
  renal_filter_counts <<- list()

  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  # starting cohort
d <- df |> 
  filter(!is.na(TreatmentDate))

  renal_filter_counts$start <- d %>%
    distinct(TreatmentID, PtID) %>%
    nrow()

  # report date filter
  d <- d |> 
    filter(TreatmentDate >= reportStart,
           TreatmentDate <= reportEnd)

  renal_filter_counts$report_period <- d %>%
    distinct(TreatmentID, PtID) %>%
    nrow()

  # organ filter
  if (!identical(report_organs, "All")) {
    d <- d |> 
      filter(
        grepl(
          paste(report_organs, collapse="|"),
          Organ
        )
      )
    }

  renal_filter_counts$organ <- d %>%
    distinct(TreatmentID, PtID) %>%
    nrow()

  # diagnosis filter
  d <- filter_by_report_diagnosis(
    d,
    report_diagnosis_type,
    report_subtypes
  )

  renal_filter_counts$diagnosis <- d %>%
    distinct(ID) %>%
    nrow()

renal_filter_counts$organ <- d %>%
  distinct(TreatmentID, PtID) %>%
  nrow()

  d
}

filter_lesion_rows <- function(df)
{
  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  d <- df |>
    filter(!is.na(RxDate)) |>
    filter(RxDate >= reportStart, RxDate <= reportEnd)

  if (!identical(report_organs, "All")) {
    d <- d |> filter(Organ %in% report_organs)
  }

  d <- filter_by_report_diagnosis(d, report_diagnosis_type, report_subtypes)

  if (!identical(report_modality, "All") &&
      "RxModality" %in% names(d)) {
  
    d <- d |>
      filter(
        Reduce(
          `|`,
          lapply(report_modality, function(m)
            grepl(m, RxModality, fixed = TRUE)
          )
        )
      )
  }
  d
}


# ------------------------------------------------------------
# Apply renal report filters in a single reproducible pipeline
# ------------------------------------------------------------

apply_renal_filters <- function(df) {

  if (!is.data.frame(df) || nrow(df) == 0) {
    return(list(
      raw = df,
      date = df,
      organ = df,
      diagnosis = df,
      modality = df,
      final = df
    ))
  }


  # Date filter
  date_filtered <- df %>%
    filter(
      TreatmentDate >= reportStart,
      TreatmentDate <= reportEnd
    )


  # Organ filter
  if (identical(report_organs, "All")) {

    organ_filtered <- date_filtered

  } else {

    organ_filtered <- date_filtered %>%
      filter(
        vapply(
          Organ,
          function(x) {

            if (is.na(x))
              return(FALSE)

            organs <- trimws(
              unlist(strsplit(x, ","))
            )

            all(organs %in% report_organs)

          },
          logical(1)
        )
      )
  }


  # Diagnosis filter
  diagnosis_filtered <- filter_by_report_diagnosis(
    organ_filtered,
    report_diagnosis_type,
    report_subtypes
  )


  # Modality filter
  if (identical(report_modality, "All")) {

    modality_filtered <- diagnosis_filtered

  } else {

    modality_filtered <- diagnosis_filtered %>%
      filter(
        vapply(
          RxModality,
          function(x) {

            if (is.na(x))
              return(FALSE)

            any(
              vapply(
                report_modality,
                function(m)
                  grepl(m, x, fixed = TRUE),
                logical(1)
              )
            )

          },
          logical(1)
        )
      )
  }
  
# Tumour size filter — deliberately LAST
# Note if tumour size is not specified on the treatment data it remains IN not OUT
if ("TumourSizes" %in% names(modality_filtered)) {

  tumour_filtered <- modality_filtered %>%
    dplyr::filter(
      vapply(
        TumourSizes,
        function(x) {

          if (is.na(x) || !nzchar(trimws(x))) {
            return(FALSE)
          }

          sizes <- suppressWarnings(
            as.numeric(
              trimws(
                unlist(strsplit(x, ","))
              )
            )
          )

          # Exclude treatment if ANY tumour is outside the range
          all(
            !is.na(sizes) &
            dplyr::between(
              sizes,
              report_min_tumour_size,
              report_max_tumour_size
            )
          )
        },
        logical(1)
      )
    )

} else {

  tumour_filtered <- modality_filtered

}

  list(
    raw = df,
    date = date_filtered,
    organ = organ_filtered,
    diagnosis = diagnosis_filtered,
    modality = modality_filtered,
    tumour_size = tumour_filtered,
    final = tumour_filtered
  )
}

# Get the filtered patient data and select only those where the MaxTumourSize is in reporting range
treatment_data <- if (exists("rxDoneData") && is.data.frame(rxDoneData)) {

  rxDoneData %>%
    dplyr::mutate(
      TreatmentID = ID,
      PtID = sub("-[0-9]+$", "", ID),
      TreatmentDate = as.Date(RxDate)
    )

} else {
  tibble::tibble(
    TreatmentID = character(),
    PtID = character(),
    TreatmentDate = as.Date(character())
  )
}

# Initial patient cohort
patient_data <- treatment_data

# ------------------------------------------------------------------
# Permanent renal cohort accounting counters for report summary
# ------------------------------------------------------------------

if (exists("renalFn.df") && is.data.frame(renalFn.df)) {
  debug_log("renalFn.df columns:")
  debug_log(names(renalFn.df))
}

debug_log("renalFn.df exists:", exists("renalFn.df"))

if (exists("renalFn.df") && is.data.frame(renalFn.df)) {
  debug_log("renalFn.df class:", paste(class(renalFn.df), collapse=", "))
  debug_log("renalFn.df names:", paste(names(renalFn.df), collapse=", "))
  debug_log("renalFn.df nrow:", nrow(renalFn.df))
}

# All patients with eGFR entries
renal_egfr_ids <- renalFn.df %>%
  filter(!is.na(eGFR)) %>%
  dplyr::mutate(
    PtID = as.character(PtID),
    PtID = sub("-[0-9]+$", "", PtID)
  ) %>%
  distinct(PtID)

# Patients represented in cancerPerPatientData
cancer_ids <- cancerPerPatientData %>%
  dplyr::mutate(PtID = sub("-[0-9]+$", "", ID)) %>%
  distinct(PtID)

# ------------------------------------------------------------
# DEBUG: identify exactly which cohort filter removes
# renal-function patients
# ------------------------------------------------------------

if (isTRUE(DEBUG_MODE) &&
    exists("renalFn.df") &&
    is.data.frame(renalFn.df) &&
    exists("cancerPerPatientData") &&
    is.data.frame(cancerPerPatientData)) {

  renal_ids <- renalFn.df %>%
    filter(!is.na(eGFR)) %>%
    dplyr::mutate(PtID = as.character(PtID)) %>%
    distinct(PtID)

  # Start with all cancer patients
  
debug_log("cancerPerPatientData columns:")
debug_log(names(cancerPerPatientData))
debug_log("treatment_data columns:")
debug_log(names(treatment_data))

test <- cancerPerPatientData %>%
  left_join(
    treatment_data %>%
      select(ID, TreatmentID, PtID, TreatmentDate, RxModality),
    by = "ID"
  ) 
  
  renal_test <- test %>%
    semi_join(renal_ids, by = "PtID")

  debug_log(
    "Renal eGFR patients in cancerPerPatientData:",
    n_distinct(renal_test$PtID)
  )

  # ----------------------------------------------------------
  # 1. TreatmentDate filter
  # ----------------------------------------------------------

  debug_log("FIXME renal_test columns:")
  debug_log(names(renal_test))

  after_date <- test %>%
    filter(
      !is.na(TreatmentDate),
      TreatmentDate >= reportStart,
      TreatmentDate <= reportEnd
    )

  debug_log(
    "After TreatmentDate/report-period filter:",
    n_distinct(after_date$PtID)
  )

  debug_log(
    "Lost by TreatmentDate/report-period filter:",
    n_distinct(renal_test$PtID) -
      n_distinct(after_date$PtID)
  )

  debug_log(
    "DEBUG report_organs:",
    paste(report_organs, collapse = " | ")
  )
  
  debug_log(
    "DEBUG Organ values in renal cohort:",
    paste(
      head(sort(unique(after_date$Organ)), 20),
      collapse = " | "
    )
  )

  
  # ----------------------------------------------------------
  # 2. Organ filter
  # ----------------------------------------------------------

  if (identical(report_organs, "All")) {

    after_organ <- after_date

  } else {

    after_organ <- after_date %>%
      filter(
        vapply(
          Organ,
          function(x) {
            any(
              sapply(
                report_organs,
                function(o) grepl(o, x, fixed = TRUE)
              )
            )
          },
          logical(1)
        )
      )
  }

  debug_log(
    "After organ filter:",
    n_distinct(after_organ$PtID)
  )

  debug_log(
    "Lost by organ filter:",
    n_distinct(after_date$PtID) -
      n_distinct(after_organ$PtID)
  )

  # ----------------------------------------------------------
  # 3. Diagnosis filter
  # ----------------------------------------------------------

  after_diagnosis <- filter_by_report_diagnosis(
    after_organ,
    report_diagnosis_type,
    report_subtypes
  )

  debug_log(
    "After diagnosis filter:",
    n_distinct(after_diagnosis$PtID)
  )

  debug_log(
    "Lost by diagnosis filter:",
    n_distinct(after_organ$PtID) -
      n_distinct(after_diagnosis$PtID)
  )



  # ----------------------------------------------------------
  # 4. Modality filter
  # ----------------------------------------------------------

  if (identical(report_modality, "All")) {

    after_modality <- after_diagnosis

  } else {

    after_modality <- after_diagnosis %>%
      filter(
        vapply(
          RxModality,
          function(x) {

            if (is.na(x) || length(x) == 0)
              return(FALSE)

            any(
              vapply(
                report_modality,
                function(m)
                  grepl(m, x, fixed = TRUE),
                logical(1)
              )
            )
          },
          logical(1)
        )
      )
  }


  debug_log(
    "After modality filter:",
    n_distinct(after_modality$PtID)
  )

  debug_log(
    "Lost by modality filter:",
    n_distinct(after_diagnosis$PtID) -
      n_distinct(after_modality$PtID)
  )

  debug_log(
    "Final renal eGFR patients surviving patient filters:",
    n_distinct(after_modality$PtID)
  )

  debug_log(
    "Current report_organs:",
    paste(report_organs, collapse = ", ")
  )

  debug_log(
    "Current report_diagnosis_type:",
    report_diagnosis_type
  )

  debug_log(
    "Current report_subtypes:",
    paste(report_subtypes, collapse = ", ")
  )

  debug_log(
    "Current report_modality:",
    paste(report_modality, collapse = ", ")
  )
}

lesion_data <- if (exists("cancerPerLesionData") &&
                   is.data.frame(cancerPerLesionData)) {

  cancerPerLesionData %>%
    inner_join(
      treatment_data %>%
        select(
          ID,
          TreatmentID,
          TreatmentDate
        ),
      by = "ID"
    )

} else {
  data.frame()
}

# Renal patients before tumour-size filtering.
# Tumour size is deliberately applied LAST in apply_renal_filters().
renal_filter_ids <- treatment_data %>%
  semi_join(
    renal_egfr_ids,
    by = "PtID"
  )

debug_log(
  "Patients after tumour size filter:",
  n_distinct(renal_filter_ids$PtID)
)


# Apply modality filter to the treatment cohort before renal extraction

if (!identical(report_modality, "All") &&
    "RxModality" %in% names(patient_data)) {

  patient_data <- patient_data %>%
    filter(
      vapply(
        RxModality,
        function(x) {

          if (is.na(x))
            return(FALSE)

          any(
            vapply(
              report_modality,
              function(m)
                grepl(m, x, fixed = TRUE),
              logical(1)
            )
          )

        },
        logical(1)
      )
    )
}


if (!identical(report_organs, "All")) {
  lesion_data <- lesion_data %>%
    filter(Organ %in% report_organs)
}

if (!identical(report_modality, "All") &&
    "RxModality" %in% names(lesion_data)) {
  lesion_data <- lesion_data %>%
    filter(
      grepl(
        paste(report_modality, collapse="|"),
        RxModality
      )
    )
}

renalFn_data <- if (exists("renalFn.df") &&
                    is.data.frame(renalFn.df) &&
                    "PtID" %in% names(renalFn.df)) {

  renalFn.df |>
    dplyr::mutate(
      PtID = as.character(PtID),
      PtID = sub("-[0-9]+$", "", PtID)
    ) |>
    left_join(
      treatment_data |>
        select(
          TreatmentID,
          PtID,
          TreatmentDate
        ),
      by = "PtID"
    )

} else {

  warning("renalFn.df missing or PtID column missing")
  data.frame()

}

renalFn_data <- renalFn_data %>%
 dplyr::mutate(
   RxDate = TreatmentDate
 )


renal_egfr_ids_final <- renalFn_data %>%
  filter(!is.na(eGFR)) %>%
  distinct(PtID)


if (nrow(renalFn_data) > 0) {

  renalFn_data <- renalFn_data %>%
    dplyr::mutate(
      Date = as.Date(sapply(Date, convertToDate)),
      TreatmentDate = as.Date(TreatmentDate),
      eGFR = as.numeric(eGFR),
      DaysFromRx = as.numeric(Date - TreatmentDate),
      MonthsFromRx = DaysFromRx / 30.44
    ) %>%
    
    # Restrict to the guaranteed minimum follow-up window: any reading taken
    # more than report_min_months_followup months AFTER treatment is dropped,
    # so every patient contributes an equal, unbiased follow-up window
    # rather than patients with longer follow-up dominating later
    # timepoints. Baseline / pre-treatment readings (MonthsFromRx <= 0) are
    # never affected -- only post-treatment readings are capped.
    filter(
      MonthsFromRx <= 0 | MonthsFromRx <= report_max_months_followup
    )
}







# ------------------------------------------------------------------
# DEBUG: renal baseline/post-treatment patient accounting
# ------------------------------------------------------------------

if (isTRUE(DEBUG_MODE) && nrow(renalFn_data) > 0) {

  renal_valid <- renalFn_data %>%
    filter(!is.na(eGFR), !is.na(PtID))

  baseline_ids_debug <- renal_valid %>%
    filter(
      DaysFromRx < 0,
      DaysFromRx >= -182.6
    ) %>%
    distinct(PtID)

  post_3m_ids_debug <- renal_valid %>%
    filter(
      DaysFromRx >= 0,
      DaysFromRx <= 3 * 30.44
    ) %>%
    distinct(PtID)

  both_debug <- intersect(
    baseline_ids_debug$PtID,
    post_3m_ids_debug$PtID
  )

  debug_log("==========================================")
  debug_log("RENAL BASELINE / POST-3M ACCOUNTING")
  debug_log("==========================================")

  debug_log(
    "Unique patients with any valid eGFR:",
    n_distinct(renal_valid$PtID)
  )

  debug_log(
    "Patients with baseline eGFR:",
    n_distinct(baseline_ids_debug$PtID)
  )

  debug_log(
    "Patients with post-treatment eGFR within 3 months:",
    n_distinct(post_3m_ids_debug$PtID)
  )

  debug_log(
    "Patients with BOTH baseline and post-treatment eGFR within 3 months:",
    length(both_debug)
  )

  debug_log(
    "Baseline patients WITHOUT post-3m eGFR:",
    length(setdiff(
      baseline_ids_debug$PtID,
      post_3m_ids_debug$PtID
    ))
  )

  debug_log(
    "Post-3m patients WITHOUT baseline eGFR:",
    length(setdiff(
      post_3m_ids_debug$PtID,
      baseline_ids_debug$PtID
    ))
  )

  debug_log(
    "Patients with post-treatment eGFR after 3 months:",
    n_distinct(
      renal_valid %>%
        filter(DaysFromRx > 3 * 30.44) %>%
        pull(PtID)
    )
  )

  debug_log("==========================================")
}






fmt_modality <- function(modality, df = NULL) {
  if (!identical(modality, "All")) {
    return(modality)
  }

  if (!is.data.frame(df) || !"RxModalities" %in% names(df)) {
    return("All")
  }

  mods <- unique(unlist(strsplit(
    as.character(df$RxModalities),
    split = ",|;|\\+|\\s+"
  )))

  mods <- trimws(mods)
  mods <- mods[mods != "" & !is.na(mods)]

  if (length(mods) == 0) {
    "All"
  } else {
    paste(sort(unique(mods)), collapse = ", ")
  }
}

fmt_param <- function(x) {
  x <- setdiff(as.character(x), "All")
  if (length(x) == 0) "All" else paste(x, collapse = ", ")
}

```

## Report Parameters

| Parameter | Value |
|:----------|:------|
| **Report generated** | `r format(Sys.time(), "%a %d %B %Y %H:%M")` |
| **Report period** | `r format(reportStart, "%d %B %Y")` – `r format(reportEnd, "%d %B %Y")` |
| **Organ(s)** | `r if (identical(report_organs, "All")) "All" else paste(report_organs, collapse = ", ")` |
| **Diagnosis type** | `r fmt_param(report_diagnosis_type)` |
| **Subtype(s)** | `r fmt_param(report_subtypes)` |
| **Tumour Size Range** | `r fmt_param(paste0(report_min_tumour_size, "-", report_max_tumour_size," mm"))` |
| **Gender(s)** | `r paste(report_genders, collapse = ", ")` |
| **Modality** | `r fmt_modality(report_modality, patient_data)` |
| **Minimum follow-up** | `r report_min_months_followup` months |
| **Maximum follow-up** | `r report_max_months_followup` months |
| **AKI Bin (0..2wk) Included** | `r if(report_include_aki_bin) "Yes" else "No"` |
| **Pt IDs anonymised** | `r if(reportAnonymised) "Yes" else "No"` |
| **Individual Pt. Plots** | `r if(reportIndividualPtPlots) "Yes" else "No"` |

---

```{r generate-all-plots, echo=FALSE, fig.height=4.8}
# Secret code to generate all the plots but dont plot them yet!


progress <- shiny::Progress$new()
progress$set(
  value = 0.2,
  message = "Setting things up..."
)

```


## Outcome Summary
```{r overview-table, echo=FALSE, results='asis'}

progress$set(
  value = 0.3,
  message = "Generating renal function report summary ..."
)

lesion_data_filtered <- lesion_data

tumour_summary <- if (nrow(lesion_data) > 0 && "TumourSize" %in% names(lesion_data)) {
  lesion_data |>
    summarise(
      n = sum(!is.na(TumourSize)),
      median = median(TumourSize, na.rm = TRUE),
      sd = sd(TumourSize, na.rm = TRUE),
      mean = mean(TumourSize, na.rm = TRUE)
    )
} else {
  tibble::tibble(n = 0, median = NA_real_, sd = NA_real_, mean = NA_real_)
}

# --- Renal function data completeness metrics -----------------------------
# Moved up from later in the report so these can feed the summary table.
# "Baseline" = an eGFR reading in the 6 months (182.6 days) before TreatmentDate
# "Valid delta" = a patient who has both a baseline reading AND at least one
# post-treatment reading (DaysFromRx >= 0), i.e. a genuine before/after
# comparison rather than just a lone baseline value.









# ------------------------------------------------------------------
# Renal-function filter accounting
# Recalculate from the actual patient cohort so values cannot be NA
# ------------------------------------------------------------------

renal_filter_ids <- treatment_data %>%
  semi_join(
    renal_egfr_ids,
    by = "PtID"
  )

# ------------------------------------------------------------------
# Renal-function cohort accounting
# ------------------------------------------------------------------

renal_filter_results <- apply_renal_filters(
  renal_filter_ids
)

raw_filtered <- renal_filter_results$raw
date_filtered <- renal_filter_results$date
organ_filtered <- renal_filter_results$organ
diagnosis_filtered <- renal_filter_results$diagnosis
modality_filtered <- renal_filter_results$modality
tumour_filtered <- renal_filter_results$tumour_size

n_egfr_raw <- n_distinct(raw_filtered$PtID)
n_egfr_in_cancer <- n_distinct(raw_filtered$PtID)
n_after_date <- n_distinct(date_filtered$PtID)
n_after_organ <- n_distinct(organ_filtered$PtID)
n_after_diagnosis <- n_distinct(diagnosis_filtered$PtID)
n_after_modality <- n_distinct(modality_filtered$PtID)
n_after_tumour_size <- tumour_filtered %>% distinct(PtID) %>% nrow()

# Safety: modality cohort may not exist if RxModality is absent
if ("modality" %in% names(renal_filter_results)) {
  modality_filtered <- renal_filter_results$modality
} else {
  modality_filtered <- diagnosis_filtered
}


# Patient counts after each filtering stage
n_egfr_raw <- raw_filtered %>%
  distinct(PtID) %>%
  nrow()

n_after_date <- date_filtered %>%
  distinct(PtID) %>%
  nrow()

n_after_organ <- organ_filtered %>%
  distinct(PtID) %>%
  nrow()

n_after_diagnosis <- diagnosis_filtered %>%
  distinct(PtID) %>%
  nrow()

n_after_modality <- modality_filtered %>%
  distinct(PtID) %>%
  nrow()

n_after_tumour_size <- tumour_filtered %>%
  distinct(PtID) %>%
  nrow()

n_egfr_raw <- raw_filtered %>%
  distinct(PtID) %>%
  nrow()

# Final renal analysis cohort
final_patient_ids <- tumour_filtered %>%
  distinct(PtID)

renalFn_analysis <- renalFn_data %>%
  semi_join(
    final_patient_ids,
    by = "PtID"
  )

renalFn_analysis <- renalFn_analysis %>%
  arrange(PtID, TreatmentDate) %>%
  group_by(PtID) %>%
  dplyr::mutate(
    Rx_number = dense_rank(TreatmentDate)
  ) %>%
  ungroup()

renalFn_analysis <- renalFn_analysis %>%
  filter(
    !is.na(eGFR),
    !is.na(MonthsFromRx),
    MonthsFromRx <= report_max_months_followup
  )

# Baseline patients in FINAL cohort
baseline_ids <- renalFn_analysis %>%
  filter(
    DaysFromRx < 0,
    DaysFromRx >= -182.6,
    !is.na(eGFR)
  ) %>%
  distinct(PtID)

post_ids <- renalFn_analysis %>%
  filter(DaysFromRx >= 0, !is.na(eGFR)) %>%
  distinct(PtID)

# ------------------------------------------------------------
# Paired baseline + post eGFR by treatment number
# ------------------------------------------------------------

paired_rx <- renalFn_analysis %>%
  filter(!is.na(eGFR)) %>%
  group_by(TreatmentID, PtID) %>%
  summarise(
    Rx_number = first(Rx_number),
    has_baseline = any(
      DaysFromRx < 0 &
      DaysFromRx >= -182.6
    ),
    has_post = any(
      DaysFromRx >= 0
    ),
    .groups = "drop"
  ) %>%
  filter(
    has_baseline,
    has_post
  ) %>%
  count(Rx_number, name = "n_patients")

n_final_renal <- n_distinct(renalFn_analysis$PtID)

n_patients_baseline <- n_distinct(baseline_ids$PtID)

n_patients_valid_delta <- length(
  intersect(
    baseline_ids$PtID,
    post_ids$PtID
  )
)

n_valid_delta_rx1 <- paired_rx %>%
  filter(Rx_number == 1) %>%
  pull(n_patients)

n_valid_delta_rx2 <- paired_rx %>%
  filter(Rx_number == 2) %>%
  pull(n_patients)

n_valid_delta_rx3 <- paired_rx %>%
  filter(Rx_number >= 3) %>%
  pull(n_patients)

n_valid_delta_rx1 <- ifelse(length(n_valid_delta_rx1), n_valid_delta_rx1, 0)
n_valid_delta_rx2 <- ifelse(length(n_valid_delta_rx2), n_valid_delta_rx2, 0)
n_valid_delta_rx3 <- ifelse(length(n_valid_delta_rx3), n_valid_delta_rx3, 0)

# Total eGFR readings after linking renal records to final report cohort
n_patients_with_egfr <- renalFn_data %>%
  semi_join(
    final_patient_ids,
    by="PtID"
  ) %>%
  filter(!is.na(eGFR)) %>%
  distinct(PtID) %>%
  nrow()


# eGFR measurements actually included in renal analysis
# after all renal exclusions including follow-up window
renal_analysis_measurements <- renalFn_analysis %>%
  filter(
    !is.na(eGFR),
    !is.na(MonthsFromRx)
  ) %>%
  dplyr::mutate(
    FollowUp = cut(
      MonthsFromRx,
      breaks = followup_bins$breaks,
      labels = followup_bins$labels,
      include.lowest = TRUE,
      right = FALSE
    )
  ) %>%
  filter(!is.na(FollowUp))

n_egfr_included_analysis <- nrow(renal_analysis_measurements)

n_report_treatments <- n_distinct(treatment_data$ID)

debug_log("Counts:")
debug_log("renal eGFR patients:", n_distinct(renal_egfr_ids$PtID))
debug_log("matching treatment patients:", n_distinct(renal_filter_ids$PtID))
debug_log("after date:", n_distinct(date_filtered$PtID))
debug_log("after organ:", n_distinct(organ_filtered$PtID))
debug_log("after diagnosis:", n_distinct(diagnosis_filtered$PtID))
debug_log("after modality:", n_distinct(modality_filtered$PtID))


# ------------------------------------------------------------------
# Summary table
# ------------------------------------------------------------------

# ------------------------------------------------------------------
# Ensure renal cohort accounting variables exist for summary table
# ------------------------------------------------------------------

n_egfr_raw <- renalFn.df %>%
  filter(!is.na(eGFR)) %>%
  dplyr::mutate(
    PtID = sub("-[0-9]+$", "", as.character(PtID))
  ) %>%
  distinct(PtID) %>%
  nrow()


n_egfr_patients_in_cancer <- renalFn.df %>%
  filter(!is.na(eGFR)) %>%
  dplyr::mutate(
    PtID = sub("-[0-9]+$", "", as.character(PtID))
  ) %>%
  semi_join(
    cancerPerPatientData %>%
      dplyr::mutate(
        PtID = sub("-[0-9]+$", "", as.character(ID))
      ) %>%
      distinct(PtID),
    by = "PtID"
  ) %>%
  distinct(PtID) %>%
  nrow()

# ------------------------------------------------------------------
# Treatment number distribution in final report cohort
# ------------------------------------------------------------------

final_treatment_counts <- treatment_data %>%
  filter(PtID %in% final_patient_ids$PtID) %>%
  group_by(PtID) %>%
  summarise(
    n_treatments = n_distinct(TreatmentID),
    .groups = "drop"
  )

n_single_treatment <- final_treatment_counts %>%
  filter(n_treatments == 1) %>%
  nrow()

n_two_treatments <- final_treatment_counts %>%
  filter(n_treatments == 2) %>%
  nrow()

n_three_plus_treatments <- final_treatment_counts %>%
  filter(n_treatments >= 3) %>%
  nrow()


table1 <- tibble::tibble(
  Metric = c(
    "No. Patients with eGFR measurement(s) in EDC (unfiltered)",
    "...with matching cancer treatment data",
    "...after report-period filter",
    "...after organ filter",
    "...after diagnosis filter",
    "...after modality filter",
    "...after tumour size filter",
    "<b>Patients in final report cohort</b>",
    "...with single treatment",
    "...with two treatments",
    "...with three or more treatments",
    "<b>Tumours treated in final report cohort</b>",
    "Number of tumours treated",
    "Median tumour size (mm)",
    "SD tumour size (mm)"
  ),
  Value = c(
    format(n_egfr_raw, big.mark=","),
    format(n_egfr_patients_in_cancer, big.mark=","),
    format(n_after_date, big.mark=","),
    format(n_after_organ, big.mark=","),
    format(n_after_diagnosis, big.mark=","),
    format(n_after_modality, big.mark=","),
    format(n_after_tumour_size,big.mark=","),
    "",
    format(n_single_treatment, big.mark=","),
    format(n_two_treatments, big.mark=","),
    format(n_three_plus_treatments, big.mark=","),
    "",
   format(n_distinct(lesion_data$TreatmentID), big.mark=","),
   format(tumour_summary$median, digits=1),
   format(tumour_summary$sd, digits=1)
    
  )
)

baseline <- renalFn_analysis %>%
  filter(DaysFromRx < 0, DaysFromRx >= -182.6, !is.na(eGFR)) %>%
  group_by(TreatmentID) %>%
  summarise(Baseline = mean(eGFR, na.rm = TRUE), .groups = "drop")

egfr_window_delta <- renalFn_analysis %>%
  left_join(baseline, by = "TreatmentID") %>%
  filter(!is.na(eGFR), !is.na(Baseline), !is.na(DaysFromRx)) %>%
  mutate(Delta = eGFR - Baseline)

mean_baseline_egfr <- mean(baseline$Baseline, na.rm = TRUE)

mean_delta_0_2wk <- egfr_window_delta %>%
  filter(DaysFromRx >= 0, DaysFromRx <= 14) %>%
  group_by(TreatmentID) %>%
  summarise(Delta = mean(Delta, na.rm = TRUE), .groups = "drop") %>%
  summarise(x = mean(Delta, na.rm = TRUE)) %>%
  pull(x)

mean_delta_6_12m <- egfr_window_delta %>%
  filter(DaysFromRx >= 6 * 30.44, DaysFromRx <= 12 * 30.44) %>%
  group_by(TreatmentID) %>%
  summarise(Delta = mean(Delta, na.rm = TRUE), .groups = "drop") %>%
  summarise(x = mean(Delta, na.rm = TRUE)) %>%
  pull(x)

mean_baseline_egfr <- ifelse(is.finite(mean_baseline_egfr), mean_baseline_egfr, NA_real_)
mean_delta_0_2wk <- ifelse(is.finite(mean_delta_0_2wk), mean_delta_0_2wk, NA_real_)
mean_delta_6_12m <- ifelse(is.finite(mean_delta_6_12m), mean_delta_6_12m, NA_real_)

table2 <- tibble::tibble(
  Metric = c(
    "<b>Renal function cohort</b>",
    "Patients treated in final renal analysis (≥1 valid eGFR within follow-up window)",
    "...with ≥1 eGFR measurement",
    "...with baseline eGFR before ablation",
    "...with paired eGFR on any treatment",
    "...with paired eGFR on 1st treatment",
    "...with paired eGFR on 2nd treatment",
    "...with paired eGFR on 3rd+ treatment",
    "",
    "<b>Renal function summary</b>",
    "Mean baseline eGFR",
    "Mean ΔeGFR 0–2 weeks",
    "Mean ΔeGFR 6–12 months",
    "",
    "<b>Total Number of eGFR measurements</b>",
    "...available after cohort filtering",
    "...included in the final analysis"
  ),
  Value = c(
    "",
    format(n_final_renal, big.mark=","),
    format(n_patients_with_egfr, big.mark=","),
    format(n_patients_baseline, big.mark=","),
    format(n_patients_valid_delta, big.mark=","),
    format(n_valid_delta_rx1, big.mark=","),
    format(n_valid_delta_rx2, big.mark=","),
    format(n_valid_delta_rx3, big.mark=","),
    "",
    "",
    format(round(mean_baseline_egfr, 1), nsmall=1),
    format(round(mean_delta_0_2wk, 1), nsmall=1),
    format(round(mean_delta_6_12m, 1), nsmall=1),
    "",
    "",
    format(nrow(renalFn_analysis %>% filter(!is.na(eGFR))), big.mark=","),
    format(nrow(renal_analysis_measurements), big.mark=",")
  )
)


# ------------------------------------------------------------------
# Render tables
# ------------------------------------------------------------------

table1_html <- kable(
  table1,
  format = "html",
  escape = FALSE,
  caption = "Patient Cohort"
) |>
  kableExtra::kable_styling(
    full_width = TRUE,
    bootstrap_options = "condensed"
  ) |>
  as.character()

table2_html <- kable(
  table2,
  format = "html",
  escape = FALSE,
  caption = "Renal Function Analysis"
) |>
  kableExtra::kable_styling(
    full_width = TRUE,
    bootstrap_options = "condensed"
  ) |>
  as.character()

cat(
  '<div style="display:flex; gap:25px; align-items:flex-start;">',
  '<div style="flex:1; min-width:0;">',
  table1_html,
  '</div>',
  '<div style="flex:1; min-width:0;">',
  table2_html,
  '</div>',
  '</div>'
)

renalPatients <- renalFn_data %>%
  arrange(TreatmentID, DaysFromRx) %>%
  group_by(TreatmentID)
```

```{r}
renalFn_display <- renalFn_data
if (isTRUE(reportAnonymised)) {
  renalFn_display$PtID <- anonymise_ptid(renalFn_display$PtID)
}
```

```{r renal-summary-plot, fig.width=10, fig.height=5}

renal.summary <- renalFn_analysis %>%
  filter(
    !is.na(MonthsFromRx),
    !is.na(eGFR)
  ) %>%
  dplyr::mutate(
    FollowUp = cut(
      MonthsFromRx,
      breaks = followup_bins$breaks,
      labels = followup_bins$labels,
      include.lowest = TRUE,
      right = FALSE
    )
  ) %>%
  filter(!is.na(FollowUp)) %>%

  # Patient-level mean within interval
  group_by(TreatmentID, FollowUp) %>%
  summarise(
    eGFR = mean(eGFR, na.rm = TRUE),
    .groups = "drop"
  ) %>%

  # Summary across patients
  group_by(FollowUp) %>%
  summarise(
    Mean = mean(eGFR, na.rm = TRUE),
    Median = median(eGFR, na.rm = TRUE),
    SD = sd(eGFR, na.rm = TRUE),
    N_patients = n_distinct(TreatmentID),
    SE = SD / sqrt(N_patients),
    Lower = Mean - 1.96 * SE,
    Upper = Mean + 1.96 * SE,
    .groups = "drop"
  ) %>%

  # Add raw measurement counts separately
  left_join(
    renalFn_analysis %>%
      filter(
        !is.na(MonthsFromRx),
        !is.na(eGFR)
      ) %>%
      dplyr::mutate(
        FollowUp = cut(
          MonthsFromRx,
          breaks = followup_bins$breaks,
          labels = followup_bins$labels,
          include.lowest = TRUE,
          right = FALSE
        )
      ) %>%
      filter(!is.na(FollowUp)) %>%
      group_by(FollowUp) %>%
      summarise(
        n_readings = n(),
        .groups = "drop"
      ),
    by = "FollowUp"
  ) %>%
  
  dplyr::mutate(
    FollowUp = factor(
      FollowUp,
      levels = followup_bins$labels
    )
  )
  
  baseline_mean <- renal.summary %>%
    filter(FollowUp == "Baseline") %>%
    pull(Mean)
  
  if (length(baseline_mean) == 0) {
    baseline_mean <- NA_real_
  }
  
  
  ggplot(
      renal.summary,
      aes(FollowUp, Mean, group = 1)
  ) +
    
  geom_hline(
    yintercept = baseline_mean,
    colour = "red",
    linetype = 2
  ) +

  geom_ribbon(
      aes(
          ymin = Lower,
          ymax = Upper
      ),
      fill = "#4C9BE8",
      alpha = .20
  ) +

  geom_line(
      colour = "#005BBB",
      linewidth = 1.2
  ) +

  geom_point(
      aes(size = N_patients),
      colour = "#005BBB"
  ) +

  geom_text_repel(
    aes(
      label = paste0(
        "N=", N_patients,
        "\n(n=", n_readings, " readings)"
      )
    ),
    size = 3.8,
    colour = "black",
    fontface = "bold",
    box.padding = 0.5,
    point.padding = 0.4,
    min.segment.length = 0,
    seed = 123
  ) +

  scale_size(
      range = c(3,10),
      name = "Patients"
  ) +

  labs(
      x = "Follow-up interval",
      y = "Mean eGFR"
  ) +

  coord_cartesian(
      ylim = c(20,100)
  ) +

  theme_bw(base_size = 14) +

  theme(
      legend.position = "right",
      panel.grid.minor = element_blank(),
      axis.title = element_text(face = "bold")
  )
 
```
**Figure 1. Mean estimated glomerular filtration rate (eGFR) over follow-up.** Mean eGFR is shown for each follow-up interval among patients included in the renal function analysis. For patients with multiple measurements within an interval, measurements were first averaged within patient and then across patients. Points are scaled according to the number of patients contributing data to each interval, with the corresponding number shown alongside each point. Shaded areas represent 95% confidence intervals for the mean. The dashed horizontal line indicates baseline.
  

```{r egfr-delta-plot, fig.width=10, fig.height=5}

#---------------------------------------
# Calculate baseline renal function
#---------------------------------------

baseline <- renalFn_data %>%
  filter(
    DaysFromRx < 0,
    DaysFromRx >= -182.6,
    !is.na(eGFR)
  ) %>%
  group_by(TreatmentID) %>%
  summarise(
    Baseline = mean(eGFR, na.rm = TRUE),
    .groups = "drop"
  )


#---------------------------------------
# Calculate change from baseline
#---------------------------------------

renal.delta <- renalFn_analysis %>%
  left_join(
    baseline,
    by = "TreatmentID"
  ) %>%
  filter(!is.na(Baseline)) %>%
  
  dplyr::mutate(
    Delta = eGFR - Baseline,
    FollowUp = cut(
      MonthsFromRx,
        breaks = followup_bins$breaks,
        labels = followup_bins$labels,
        include.lowest = TRUE,
        right = FALSE)

  ) %>%
  
  # force baseline to exactly zero
  dplyr::mutate(
    Delta = ifelse(FollowUp == "Baseline", 0, Delta)
  ) %>%
  
  filter(!is.na(FollowUp))

baseline.count <- renal.delta %>%
  filter(
    !is.na(Baseline),
    !is.na(PtID),
    !is.na(FollowUp)
  ) %>%
  group_by(FollowUp) %>%
  summarise(
    N_baseline = n_distinct(TreatmentID),
    .groups = "drop"
  )

#---------------------------------------
# Average within patient then across patients
#---------------------------------------

# Raw reading counts per follow-up interval
reading.count <- renal.delta %>%
  filter(
    !is.na(Delta),
    !is.na(FollowUp)
  ) %>%
  group_by(FollowUp) %>%
  summarise(
    n_readings = n(),
    .groups = "drop"
  )


# Patient-level averaging within interval
renal.delta.summary <- renal.delta %>%
  filter(
    !is.na(Delta),
    !is.na(FollowUp)
  ) %>%

  # flatten multiple readings per patient per interval
  group_by(TreatmentID, FollowUp) %>%
  summarise(
    Delta = mean(Delta, na.rm = TRUE),
    .groups = "drop"
  ) %>%

  # now calculate mean across patients
  group_by(FollowUp) %>%
  summarise(
    Mean = mean(Delta, na.rm = TRUE),
    SD = sd(Delta, na.rm = TRUE),
    N_patients = n_distinct(TreatmentID),
    SE = SD / sqrt(N_patients),
    Lower = Mean - 1.96 * SE,
    Upper = Mean + 1.96 * SE,
    .groups = "drop"
  ) %>%

  left_join(
    reading.count,
    by = "FollowUp"
  )


#---------------------------------------
# Plot
#---------------------------------------

ggplot(
  renal.delta.summary,
  aes(
    FollowUp,
    Mean,
    group = 1
  )
) +

geom_hline(
  yintercept = 0,
  colour = "red",
  linetype = 2
) +

geom_ribbon(
  aes(
    ymin = Lower,
    ymax = Upper
  ),
  fill = "#4C9BE8",
  alpha = 0.25
) +

geom_line(
  colour = "#005BBB",
  linewidth = 1.2
) +

geom_point(
  aes(size = N_patients),
  colour = "#005BBB"
) +

geom_text_repel(
  aes(label = paste0(
    "N=", N_patients,
    "\n(", n_readings, " readings)"
  )),
  size = 3.8,
  colour = "black",
  fontface = "bold",
  box.padding = 0.5,
  point.padding = 0.4,
  min.segment.length = 0,
  seed = 123
) +

scale_size(
  range = c(3,10),
  name = "Patients (N)"
) +

labs(
  x = "Follow-up interval",
  y = "Δ eGFR from baseline"
) +

theme_bw(base_size = 14) +

theme(
  legend.position = "right",
  panel.grid.minor = element_blank(),
  axis.title = element_text(face = "bold"),
  axis.text = element_text(size = 12)

)
```
**Figure 2. Change in estimated glomerular filtration rate (Δ eGFR) from baseline over follow-up.** Baseline eGFR was defined as the mean of available eGFR measurements obtained within 6 months before treatment for each patient. Δ eGFR represents the difference between eGFR at each follow-up interval and the patient-specific baseline eGFR. Measurements were first averaged within patient and follow-up interval and then across patients. Points are scaled according to the number of patients contributing to each interval; Labels show the number of patients contributing ΔeGFR data to each interval mean (N) followed in parentheses by the number of individual eGFR measurements contributing to that mean. Shaded areas represent 95% confidence intervals. The dashed horizontal line indicates no change from baseline.

```{r renal-patient-plots, results='asis', fig.width=12, fig.height=10}

if (isTRUE(reportIndividualPtPlots))
{
  cat("## Individual patient plots for follow-up eGFR\n\n")

  plots <- lapply(unique(renalFn_display$TreatmentID), function(pt) {

  df <- renalFn_display %>%
    filter(TreatmentID == pt) %>%
    arrange(DaysFromRx)

  # sensible y-axis limits
  y_range <- range(df$eGFR, na.rm = TRUE)

  if (length(unique(df$eGFR)) == 1) {
    y_limits <- c(
      y_range[1] - 5,
      y_range[1] + 5
    )
  } else {
    padding <- max(
      5,
      diff(y_range) * 0.15
    )

    y_limits <- c(
      y_range[1] - padding,
      y_range[2] + padding
    )
  }


  ggplot(df,
         aes(DaysFromRx, eGFR)) +

    geom_vline(
      xintercept = 0,
      colour = "red",
      linetype = 2
    ) +

    geom_line(linewidth = 0.5) +

    geom_point(size = 1.5) +

    scale_y_continuous(
      limits = y_limits,
      breaks = scales::pretty_breaks(n = 5),
      labels = scales::label_number(
        accuracy = 1
      )
    ) +

    labs(
      title = paste("Treatment ID:", pt),
      x = "Days",
      y = "eGFR"
    ) +

    theme_bw(base_size = 10) +

    theme(
      plot.title = element_text(size = 11, face = "bold"),
      axis.title = element_text(size = 9, face = "bold"),
      axis.text = element_text(size = 8)
    )
  })  
  
  page_size <- 12
  
  for(i in seq(1, length(plots), by = page_size)) {
  
    page_plots <- plots[i:min(i + page_size - 1, length(plots))]
  
    # Pad incomplete pages with empty panels so plots retain
    # the same 3-column width and do not stretch.
    n_spacers <- page_size - length(page_plots)
  
    if (n_spacers > 0) {
      page_plots <- c(
        page_plots,
        rep(list(patchwork::plot_spacer()), n_spacers)
      )
    }
  
    print(
      wrap_plots(
        page_plots,
        ncol = 3
      )
    )
  }
}
```
`r if (isTRUE(reportIndividualPtPlots)) paste0(
"**Figure 3. Individual patient eGFR trajectories.** ",
"Each panel shows longitudinal eGFR measurements for an individual patient included in the renal function report. ",
"The horizontal axis represents days relative to treatment, with day 0 indicating the date of treatment. ",
"Points represent individual eGFR measurements and lines connect measurements chronologically. ",
"The dashed vertical line indicates the treatment date. ",
"Patient identifiers are anonymised where anonymisation has been selected for the report."
) else ""`


## Credits

```{r reportLogo, warning=FALSE}
logo_src <- here("www", "TARGETPlotterLogo.png")
if (file.exists(logo_src)) {
  knitr::include_graphics(normalizePath(logo_src))
} else {
  cat("<!-- TARGETPlotterLogo.png logo not available -->")
}

progress$set(
  value = 1.0,
  message = "Rendering report..."
)

later::later(
  function() {
    progress$close()
  },
  delay = 3
)

```



<br>
Report Report Developer: Dr. Paul Lyon<br>
TARGET-UK Lead: Dr. Paul Lyon, FRCR
