---
title: "TARGET-UK: Renal Function Report"
output:
  html_document:
    toc: true
    self_contained: true
date: "`r format(Sys.Date(), '%d %B %Y')`"
params:
  report_start_date: !r Sys.Date() - 365
  report_end_date: !r Sys.Date()
  report_organs: "All"
  report_diagnosis_type: "All"
  report_subtypes: ["All"]
  report_genders: ["Female", "Male", "Unknown"]
  report_modality: "All"
  report_min_tumour_size: 0
  report_max_tumour_size: 100
  report_min_months_followup: 3
  report_max_months_followup: 5
  report_renal_fn_anonymised: FALSE
---

```{css, echo=FALSE}
body { font-size: 14px; }
table {
  font-size: 13px;
  width: 100% !important;
  table-layout: auto;
}
th, td {
  padding: 4px 8px !important;
  font-size: 13px;
}
img { max-width: 100% !important; height: auto !important; }

@media print {
  @page {
    size: A4 portrait;
    margin: 8mm 6mm 8mm 6mm;
  }
  body {
    font-size: 11px;
    width: 198mm;
  }
  table {
    font-size: 10px;
    page-break-inside: avoid;
    table-layout: auto;
  }
  th, td { padding: 2px 4px !important; font-size: 10px; }
  img, .plot {
    max-width: 196mm !important;
    width: 196mm !important;
    height: auto !important;
    page-break-inside: avoid;
  }
  .figure {
    max-width: 196mm !important;
    page-break-inside: avoid;
  }
  h2 { page-break-before: auto; }
}
```


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(fig.width = 10, fig.height = 5, dpi = 120)
options(knitr.table.format = "html")

library(dplyr)
library(ggplot2)
library(scales)
library(kableExtra)
library(htmltools)
library(gridExtra)
library(later)
library(patchwork)
library(ggrepel)

report_start_date               <- params$report_start_date
report_end_date                 <- params$report_end_date
report_organs                   <- params$report_organs
report_diagnosis_type           <- params$report_diagnosis_type
report_subtypes                 <- params$report_subtypes
report_genders                  <- params$report_genders
report_modality                 <- unique(params$report_modality)
report_min_tumour_size          <- params$report_min_tumour_size
report_max_tumour_size          <- params$report_max_tumour_size
report_max_months_followup      <- as.numeric(params$report_max_months_followup)
report_min_months_followup      <- as.numeric(params$report_min_months_followup)
reportStart                     <- as.Date(params$report_start_date)
reportEnd                       <- as.Date(params$report_end_date)
reportAnonymised                <- isTRUE(params$report_renal_fn_anonymised)

if (is.null(report_modality) || length(report_modality) == 0)
{
  report_modality <- "All"
}
report_modality <- as.character(report_modality)
if ("All" %in% report_modality) # If All selected, ignore other selections
{
  report_modality <- "All"
}

DEBUG_MODE <- toupper(Sys.getenv("DEBUG_MODE", unset = "FALSE")) == "TRUE"

debug_log <- function(...) {
  if (isTRUE(DEBUG_MODE)) {
    txt <- paste(
      capture.output(...),
      collapse = "\n"
    )
    cat(txt, "\n", file = stderr())
  }
}

debug_table <- function(label, x) {
  if (isTRUE(DEBUG_MODE)) {
    cat(label, "\n", file = stderr(), sep = "")
    cat(capture.output(print(table(x, useNA = "ifany"))), sep = "\n", file = stderr())
  }
}

filter_by_report_diagnosis <- function(d, report_diagnosis_type, report_subtypes) {
  if (!is.data.frame(d) || nrow(d) == 0) return(d)
  if (is.null(report_diagnosis_type) || identical(report_diagnosis_type, "All")) return(d)

  if (is.null(report_subtypes)) report_subtypes <- "All"
  report_subtypes <- setdiff(as.character(report_subtypes), "All")

  if (report_diagnosis_type == "1o & 2o") {
    return(
      d |>
        filter(
          (DiagnosisType == "P" & Diagnosis1o %in% report_subtypes) |
          (DiagnosisType == "S" & Diagnosis2o %in% report_subtypes)
        )
    )
  }

  diag_code <- switch(
    report_diagnosis_type,
    "Primary"   = "P",
    "Secondary" = "S",
    "Benign"    = "B",
    "Unknown"   = "U",
    ""
  )

  diag_col <- switch(
    diag_code,
    "P" = "Diagnosis1o",
    "S" = "Diagnosis2o",
    "B" = "DiagnosisBn",
    "U" = "DiagnosisUn",
    ""
  )

  if (nzchar(diag_col) && all(c("DiagnosisType", diag_col) %in% names(d))) {
    d |>
      filter(
        DiagnosisType == diag_code,
        .data[[diag_col]] %in% report_subtypes
      )
  } else {
    d
  }
}

# Builds FollowUp interval breaks/labels dynamically, scaled to
# report_max_months_followup, rather than a fixed 5-year scaffold.
# Always starts with a -6 to 0 month "Baseline" window, then 3/6-month
# resolution out to 1 year, then yearly thereafter, truncated (and closed)
# exactly at report_max_months_followup.
build_followup_bins <- function(max_months_followup) {

  candidates <- c(0, 3, 6, 12, 24, 36, 48, 60, 72, 84, 96, 108, 120)

  max_months_followup <- suppressWarnings(as.numeric(max_months_followup))
  if (is.na(max_months_followup) || max_months_followup <= 0) {
    max_months_followup <- 60 # fallback (5 years) if param missing/invalid
  }

  breaks <- candidates[candidates <= max_months_followup]
  if (length(breaks) == 0 || breaks[length(breaks)] < max_months_followup) {
    breaks <- c(breaks, max_months_followup)
  }
  if (breaks[1] != 0) breaks <- c(0, breaks)
  breaks <- unique(breaks)
  breaks <- c(-6, breaks) # prepend the baseline window

  label_interval <- function(a, b) {
    if (a == -6 && b == 0) return("Baseline")
    if (b <= 12) return(paste0(a, "-", b, " m"))
    if (a %% 12 == 0 && b %% 12 == 0) return(paste0(a / 12, "-", b / 12, " y"))
    paste0(a, "-", b, " m")
  }

  labels <- vapply(
    seq_len(length(breaks) - 1),
    function(i) label_interval(breaks[i], breaks[i + 1]),
    character(1)
  )

  list(breaks = breaks, labels = labels)
}
followup_bins <- build_followup_bins(report_max_months_followup)

filter_by_tumour_size <- function(df, size_col, min_size, max_size) {
  if (!is.data.frame(df) || nrow(df) == 0 || !size_col %in% names(df)) return(df)

  df[[size_col]] <- suppressWarnings(as.numeric(df[[size_col]]))

  df |>
    dplyr::filter(
      is.na(.data[[size_col]]) |
        dplyr::between(.data[[size_col]], min_size, max_size)
    )
}

normalise_organs <- function(x) {
  if (is.null(x) || length(x) == 0 || anyNA(x)) return("All")
  if (length(x) == 1 && identical(x, "All")) return("All")
  x
}

report_organs <- normalise_organs(report_organs)

filter_patient_rows <- function(df) {
  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  d <- df |> filter(!is.na(FirstRxDate))

  d <- d |> filter(FirstRxDate >= reportStart, FirstRxDate <= reportEnd)

  if (!identical(report_organs, "All")) {
    d <- d |> filter(Organ %in% report_organs)
  }

  d_before_diag <- d
  d <- filter_by_report_diagnosis(d, report_diagnosis_type, report_subtypes)

  if (!identical(report_modality, "All"))
  {
    d <- d |>
      filter(
        vapply(
          RxModalities,
          function(x) {
            if (is.na(x) || length(x) == 0) return(FALSE)
            any(
              vapply(
                report_modality,
                function(m) grepl(m, x, fixed = TRUE),
                logical(1)
              )
            )
          },
          logical(1)
        )
      )
  }
  return(d)
}

filter_lesion_rows <- function(df)
{
  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  d <- df |>
    filter(!is.na(RxDate)) |>
    filter(RxDate >= reportStart, RxDate <= reportEnd)

  if (!identical(report_organs, "All")) {
    d <- d |> filter(Organ %in% report_organs)
  }

  d <- filter_by_report_diagnosis(d, report_diagnosis_type, report_subtypes)

  if (!identical(report_modality, "All") &&
      "RxModality" %in% names(d)) {
  
    d <- d |>
      filter(
        Reduce(
          `|`,
          lapply(report_modality, function(m)
            grepl(m, RxModality, fixed = TRUE)
          )
        )
      )
  }
  d
}

# Get the filtered patient data and select only those where the MaxTumourSize is in reporting range
patient_data <- if (exists("cancerPerPatientData") && is.data.frame(cancerPerPatientData)) {
  filter_patient_rows(cancerPerPatientData)
} else {
  data.frame()
}

if (nrow(patient_data) > 0) {
  n_before_size <- nrow(patient_data)
  patient_data <- filter_by_tumour_size(
    patient_data,
    "MaxTumourSize",
    report_min_tumour_size,
    report_max_tumour_size
  )
} else {
    lesion_data <- data.frame()
    renalFn_data <- data.frame()
}

# Derive the bare patient ID (referral suffix stripped) unconditionally -
# lesion_data is keyed on PtID without the "-N" referral
# suffix, so keep_ids must be in the same bare format to match correctly.
patient_data <- patient_data |>
  dplyr::mutate(PtID = sub("-[0-9]+$", "", ID))

# Data frame with Patient IDs that passed ALL report filters
keep_ids <- patient_data |>
  distinct(PtID)

lesion_data <- if (exists("cancerPerLesionData") &&
                   is.data.frame(cancerPerLesionData)) {
    cancerPerLesionData %>%
        semi_join(keep_ids, by = "PtID")
} else {
    data.frame()
}

lesion_data <- filter_by_tumour_size(
  lesion_data,
  "TumourSize",
  report_min_tumour_size,
  report_max_tumour_size
)

if (nrow(patient_data) > 0 && "MaxTumourSize" %in% names(patient_data)) {
  patient_data$MaxTumourSize <- suppressWarnings(as.numeric(patient_data$MaxTumourSize))
}
if (nrow(lesion_data) > 0 && "TumourSize" %in% names(lesion_data)) {
  lesion_data$TumourSize <- suppressWarnings(as.numeric(lesion_data$TumourSize))
}


renalFn_data <- if (exists("renalFn.df") && is.data.frame(renalFn.df))
{
  renalFn.df %>%
    semi_join(keep_ids, by = "PtID") %>%
    left_join(
      patient_data %>%
        select(any_of(c("PtID", "FirstRxDate"))) %>%
        distinct(PtID, .keep_all = TRUE),
      by = "PtID"
    )

} else {
  data.frame()
}

if (nrow(renalFn_data) > 0) {

  renalFn_data <- renalFn_data %>%
    mutate(
      Date = as.Date(sapply(Date, convertToDate)),
      FirstRxDate = as.Date(FirstRxDate),
      eGFR = as.numeric(eGFR),
      DaysFromRx = as.numeric(Date - FirstRxDate),
      MonthsFromRx = DaysFromRx / 30.44
    ) %>%
    # Restrict to the guaranteed minimum follow-up window: any reading taken
    # more than report_min_months_followup months AFTER treatment is dropped,
    # so every patient contributes an equal, unbiased follow-up window
    # rather than patients with longer follow-up dominating later
    # timepoints. Baseline / pre-treatment readings (MonthsFromRx <= 0) are
    # never affected -- only post-treatment readings are capped.
    filter(
      MonthsFromRx <= 0 | MonthsFromRx <= report_max_months_followup
    )
}

fmt_modality <- function(modality, df = NULL) {
  if (!identical(modality, "All")) {
    return(modality)
  }

  if (!is.data.frame(df) || !"RxModalities" %in% names(df)) {
    return("All")
  }

  mods <- unique(unlist(strsplit(
    as.character(df$RxModalities),
    split = ",|;|\\+|\\s+"
  )))

  mods <- trimws(mods)
  mods <- mods[mods != "" & !is.na(mods)]

  if (length(mods) == 0) {
    "All"
  } else {
    paste(sort(unique(mods)), collapse = ", ")
  }
}

fmt_param <- function(x) {
  x <- setdiff(as.character(x), "All")
  if (length(x) == 0) "All" else paste(x, collapse = ", ")
}

```

## Report Parameters

| Parameter | Value |
|:----------|:------|
| **Report generated** | `r format(Sys.time(), "%a %d %B %Y %H:%M")` |
| **Report period** | `r format(reportStart, "%d %B %Y")` – `r format(reportEnd, "%d %B %Y")` |
| **Organ(s)** | `r if (identical(report_organs, "All")) "All" else paste(report_organs, collapse = ", ")` |
| **Diagnosis type** | `r fmt_param(report_diagnosis_type)` |
| **Subtype(s)** | `r fmt_param(report_subtypes)` |
| **Tumour Size Range** | `r fmt_param(paste0(report_min_tumour_size, "-", report_max_tumour_size," mm"))` |
| **Gender(s)** | `r paste(report_genders, collapse = ", ")` |
| **Modality** | `r fmt_modality(report_modality, patient_data)` |
| **Minimum follow-up (m)** | `r report_min_months_followup` months |
| **Maximum follow-up (m)** | `r report_max_months_followup` months |
| **Renal function anonymised** | `r if(reportAnonymised) "Yes" else "No"` |

---

```{r generate-all-plots, echo=FALSE, fig.height=4.8}
# Secret code to generate all the plots but dont plot them yet!


progress <- shiny::Progress$new()
progress$set(
  value = 0.2,
  message = "Setting things up..."
)

```

## Outcome Summary
```{r overview-table, echo=FALSE, results='asis'}

progress$set(
  value = 0.3,
  message = "Generating renal function report summary ..."
)

tumour_summary <- if (nrow(lesion_data) > 0 && "TumourSize" %in% names(lesion_data)) {
  lesion_data |>
    summarise(
      n = sum(!is.na(TumourSize)),
      median = median(TumourSize, na.rm = TRUE),
      sd = sd(TumourSize, na.rm = TRUE),
      mean = mean(TumourSize, na.rm = TRUE)
    )
} else {
  tibble::tibble(n = 0, median = NA_real_, sd = NA_real_, mean = NA_real_)
}

# --- Renal function data completeness metrics -----------------------------
# Moved up from later in the report so these can feed the summary table.
# "Baseline" = an eGFR reading in the 6 months (182.6 days) before FirstRxDate.
# "Valid delta" = a patient who has both a baseline reading AND at least one
# post-treatment reading (DaysFromRx >= 0), i.e. a genuine before/after
# comparison rather than just a lone baseline value.

baseline_ids <- renalFn_data %>%
  filter(
    DaysFromRx < 0,
    DaysFromRx >= -182.6,
    !is.na(eGFR)
  ) %>%
  distinct(PtID)

renalFn_analysis <- renalFn_data %>%
  semi_join(baseline_ids, by = "PtID")

post_ids <- renalFn_analysis %>%
  filter(DaysFromRx >= 0, !is.na(eGFR)) %>%
  distinct(PtID)

n_patients_baseline      <- n_distinct(baseline_ids$PtID)
n_patients_valid_delta   <- length(intersect(baseline_ids$PtID, post_ids$PtID))
n_egfr_total_raw         <- sum(!is.na(renalFn_data$eGFR))
n_egfr_included_analysis <- renalFn_analysis %>% filter(!is.na(eGFR)) %>% nrow()

overview_metrics <- c(
  "Patients",
  "Tumours treated",
  "Median tumour size (mm)",
  "SD tumour size (mm)",
  "Patients with baseline eGFR",
  "Patients with valid delta eGFR (baseline + post)",
  "Total eGFR readings (all patients)",
  "Total eGFR readings included in analysis"
)

overview_values <- c(
  format(nrow(patient_data), big.mark=","),
  format(nrow(lesion_data), big.mark=","),
  sprintf("%.1f", tumour_summary$median[1]),
  sprintf("%.1f", tumour_summary$sd[1]),
  format(n_patients_baseline, big.mark=","),
  format(n_patients_valid_delta, big.mark=","),
  format(n_egfr_total_raw, big.mark=","),
  format(n_egfr_included_analysis, big.mark=",")
)

overview_tbl <- tibble::tibble(
  Metric = overview_metrics,
  Value = overview_values
)

mid <- ceiling(nrow(overview_tbl) / 2)

table1 <- overview_tbl[1:mid, ]
table2 <- overview_tbl[(mid + 1):nrow(overview_tbl), ]

table1_html <- kable(
  table1,
  caption = "Renal Function summary"
) |>
  kableExtra::kable_styling(full_width = FALSE) |>
  as.character()

table2_html <- kable(
  table2,
  caption = ""
) |>
  kableExtra::kable_styling(full_width = FALSE) |>
  as.character()

cat(
  '<div style="display:flex; gap:25px; align-items:flex-start;">',
  '<div style="flex:1;">',
  table1_html,
  '</div>',
  '<div style="flex:1;">',
  table2_html,
  '</div>',
  '</div>'
)

renalPatients <- renalFn_data %>%
  arrange(PtID, DaysFromRx) %>%
  group_by(PtID)
```

```{r}
renalFn_display <- renalFn_data
if (isTRUE(reportAnonymised)) {
  renalFn_display$PtID <- anonymise_ptid(renalFn_display$PtID)
}
```

```{r renal-summary-plot, fig.width=10, fig.height=5}

renal.summary <-
    renalFn_analysis %>%

    filter(
        !is.na(MonthsFromRx),
        !is.na(eGFR)
    ) %>%

    mutate(
      FollowUp = cut(
          MonthsFromRx,
          breaks = followup_bins$breaks,
          labels = followup_bins$labels,
          include.lowest = TRUE,
          right = FALSE
        )
    ) %>%

    filter(!is.na(FollowUp)) %>%

    ## One eGFR per patient per interval
    group_by(PtID, FollowUp) %>%
    summarise(
        eGFR = mean(eGFR, na.rm = TRUE),
        .groups = "drop"
    ) %>%

    ## Then summarise across patients
    group_by(FollowUp) %>%
    summarise(
        Mean = mean(eGFR, na.rm = TRUE),
        Median = median(eGFR, na.rm = TRUE),
        SD = sd(eGFR, na.rm = TRUE),
        N = n_distinct(PtID),
        SE = SD / sqrt(N),
        Lower = Mean - 1.96 * SE,
        Upper = Mean + 1.96 * SE,
        .groups = "drop"
    ) %>%
    mutate(
      FollowUp = factor(FollowUp, levels = followup_bins$labels)
    )
  
  ggplot(
      renal.summary,
      aes(FollowUp, Mean, group = 1)
  ) +

  geom_ribbon(
      aes(
          ymin = Lower,
          ymax = Upper
      ),
      fill = "#4C9BE8",
      alpha = .20
  ) +

  geom_line(
      colour = "#005BBB",
      linewidth = 1.2
  ) +

  geom_point(
      aes(size = N),
      colour = "#005BBB"
  ) +

  geom_text_repel(
    aes(label = paste0("n=", N)),
    size = 3.8,
    colour = "black",
    fontface = "bold",
    box.padding = 0.5,
    point.padding = 0.4,
    min.segment.length = 0,
    seed = 123
  ) +

  scale_size(
      range = c(3,10),
      name = "Patients"
  ) +

  labs(
      x = "Follow-up interval",
      y = "Mean eGFR"
  ) +

  coord_cartesian(
      ylim = c(20,100)
  ) +

  theme_bw(base_size = 14) +

  theme(
      legend.position = "right",
      panel.grid.minor = element_blank(),
      axis.title = element_text(face = "bold")
  )
```


```{r egfr-delta-plot, fig.width=10, fig.height=5}

#---------------------------------------
# Calculate baseline renal function
#---------------------------------------

baseline <- renalFn_data %>%
  filter(
    DaysFromRx < 0,
    DaysFromRx >= -182.6,
    !is.na(eGFR)
  ) %>%
  group_by(PtID) %>%
  summarise(
    Baseline = mean(eGFR, na.rm = TRUE),
    .groups = "drop"
  )


#---------------------------------------
# Calculate change from baseline
#---------------------------------------

renal.delta <- renalFn_analysis %>%
  left_join(
    baseline,
    by = "PtID"
  ) %>%
  filter(!is.na(Baseline)) %>%
  
  mutate(
    Delta = eGFR - Baseline,
    FollowUp = cut(
      MonthsFromRx,
        breaks = followup_bins$breaks,
        labels = followup_bins$labels,
        include.lowest = TRUE,
        right = FALSE)

  ) %>%
  
  # force baseline to exactly zero
  mutate(
    Delta = ifelse(FollowUp == "Baseline", 0, Delta)
  ) %>%
  
  filter(!is.na(FollowUp))

baseline.count <- renal.delta %>%
  filter(
    !is.na(Baseline),
    !is.na(PtID),
    !is.na(FollowUp)
  ) %>%
  group_by(FollowUp) %>%
  summarise(
    N_baseline = n_distinct(PtID),
    .groups = "drop"
  )


#---------------------------------------
# Average within patient then across patients
#---------------------------------------

#---------------------------------------
# Average within patient then across patients
#---------------------------------------

renal.delta.summary <- renal.delta %>%

  filter(
    !is.na(Delta),
    !is.na(PtID),
    !is.na(FollowUp)
  ) %>%

  # one delta value per patient per interval
  group_by(PtID, FollowUp) %>%
  summarise(
    Delta = mean(Delta, na.rm = TRUE),
    .groups = "drop"
  ) %>%

  # then summarise across patients
  group_by(FollowUp) %>%
  summarise(
    Mean    = mean(Delta, na.rm = TRUE),
    SD      = sd(Delta, na.rm = TRUE),
    N_delta = n_distinct(PtID),
    SE      = SD / sqrt(N_delta),
    Lower   = Mean - 1.96 * SE,
    Upper   = Mean + 1.96 * SE,
    .groups = "drop"
  ) %>%

  left_join(
    baseline.count,
    by = "FollowUp"
  )

#---------------------------------------
# Plot
#---------------------------------------

ggplot(
  renal.delta.summary,
  aes(
    FollowUp,
    Mean,
    group = 1
  )
) +

geom_hline(
  yintercept = 0,
  colour = "red",
  linetype = 2
) +

geom_ribbon(
  aes(
    ymin = Lower,
    ymax = Upper
  ),
  fill = "#4C9BE8",
  alpha = 0.25
) +

geom_line(
  colour = "#005BBB",
  linewidth = 1.2
) +

geom_point(
  aes(size = N_delta),
  colour = "#005BBB"
) +

geom_text_repel(
  aes(label = paste0(
    "n=", N_delta,
    "\n(base=", N_baseline, ")"
  )),
  size = 3.8,
  colour = "black",
  fontface = "bold",
  box.padding = 0.5,
  point.padding = 0.4,
  min.segment.length = 0,
  seed = 123
) +

scale_size(
  range = c(3,10),
  name = "Patients"
) +

labs(
  x = "Follow-up interval",
  y = "Δ eGFR from baseline"
) +

theme_bw(base_size = 14) +

theme(
  legend.position = "right",
  panel.grid.minor = element_blank(),
  axis.title = element_text(face = "bold"),
  axis.text = element_text(size = 12)

)
```


```{r renal-patient-plots, fig.width=12, fig.height=10}

plots <- lapply(unique(renalFn_display$PtID), function(pt) {

  df <- renalFn_display %>%
    filter(PtID == pt) %>%
    arrange(DaysFromRx)

  ggplot(df,
         aes(DaysFromRx, eGFR)) +

    geom_vline(
      xintercept = 0,
      colour = "red",
      linetype = 2
    ) +

    geom_line(linewidth = 0.5) +

    geom_point(size = 1.5) +

    labs(
      title = paste("Patient", pt),
      x = "Days",
      y = "eGFR"
    ) +

    theme_bw(base_size = 10) +

    theme(
      plot.title = element_text(size = 11, face = "bold"),
      axis.title = element_text(size = 9, face = "bold"),
      axis.text = element_text(size = 8)
    )
})


page_size <- 9

for(i in seq(1, length(plots), by = page_size)) {

  print(
    wrap_plots(
      plots[i:min(i + page_size - 1, length(plots))],
      ncol = 3
    )
  )
}
```


## Credits

```{r reportLogo, warning=FALSE}
logo_src <- here("www", "TARGETPlotterLogo.png")
if (file.exists(logo_src)) {
  knitr::include_graphics(normalizePath(logo_src))
} else {
  cat("<!-- TARGETPlotterLogo.png logo not available -->")
}

progress$set(
  value = 1.0,
  message = "Rendering report..."
)

later::later(
  function() {
    progress$close()
  },
  delay = 3
)

```



<br>
Report Report Developer: Dr. Paul Lyon<br>
TARGET-UK Lead: Dr. Paul Lyon, FRCR
