---
title: "TARGET-UK: Renal Function Report"
output:
  html_document:
    toc: true
    self_contained: true
date: "`r format(Sys.Date(), '%d %B %Y')`"
params:
  report_start_date: !r Sys.Date() - 365
  report_end_date: !r Sys.Date()
  report_organs: "All"
  report_diagnosis_type: "All"
  report_subtypes: ["All"]
  report_genders: ["Female", "Male", "Unknown"]
  report_modality: "All"
  report_min_tumour_size: 0
  report_max_tumour_size: 100
  report_min_months_followup: 3
  report_max_months_followup: 5
  report_include_aki_bin: FALSE
  report_renal_fn_anonymised: FALSE
  report_renal_fn_pt_plots: FALSE
---

```{css, echo=FALSE}
body { font-size: 14px; }
table {
  font-size: 13px;
  width: 100% !important;
  table-layout: auto;
}
th, td {
  padding: 4px 8px !important;
  font-size: 13px;
}
img { max-width: 100% !important; height: auto !important; }

@media print {
  @page {
    size: A4 portrait;
    margin: 8mm 6mm 8mm 6mm;
  }
  body {
    font-size: 11px;
    width: 198mm;
  }
  table {
    font-size: 10px;
    page-break-inside: avoid;
    table-layout: auto;
  }
  th, td { padding: 2px 4px !important; font-size: 10px; }
  img, .plot {
    max-width: 196mm !important;
    width: 196mm !important;
    height: auto !important;
    page-break-inside: avoid;
  }
  .figure {
    max-width: 196mm !important;
    page-break-inside: avoid;
  }
  h2 { page-break-before: auto; }
}
```


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(fig.width = 10, fig.height = 5, dpi = 120)
options(knitr.table.format = "html")

library(dplyr)
library(ggplot2)
library(scales)
library(kableExtra)
library(htmltools)
library(gridExtra)
library(later)
library(patchwork)
library(ggrepel)

report_start_date               <- params$report_start_date
report_end_date                 <- params$report_end_date
report_organs                   <- params$report_organs
report_diagnosis_type           <- params$report_diagnosis_type
report_subtypes                 <- params$report_subtypes
report_genders                  <- params$report_genders
report_modality                 <- unique(params$report_modality)
report_min_tumour_size          <- params$report_min_tumour_size
report_max_tumour_size          <- params$report_max_tumour_size
report_max_months_followup      <- as.numeric(params$report_max_months_followup)
report_min_months_followup      <- as.numeric(params$report_min_months_followup)
reportStart                     <- as.Date(params$report_start_date)
reportEnd                       <- as.Date(params$report_end_date)
report_include_aki_bin          <- isTRUE(params$report_include_aki_bin)
reportAnonymised                <- isTRUE(params$report_renal_fn_anonymised)
reportIndividualPtPlots         <- isTRUE(params$report_renal_fn_pt_plots)

if (is.null(report_modality) || length(report_modality) == 0)
{
  report_modality <- "All"
}
report_modality <- as.character(report_modality)
if ("All" %in% report_modality) # If All selected, ignore other selections
{
  report_modality <- "All"
}

DEBUG_MODE <- toupper(Sys.getenv("DEBUG_MODE", unset = "FALSE")) == "TRUE"
DEBUG_MODE <- TRUE

debug_log <- function(...) {
  if (isTRUE(DEBUG_MODE)) {
    txt <- paste(
      capture.output(...),
      collapse = "\n"
    )
    cat(txt, "\n", file = stderr())
  }
}

debug_table <- function(label, x) {
  if (isTRUE(DEBUG_MODE)) {
    cat(label, "\n", file = stderr(), sep = "")
    cat(capture.output(print(table(x, useNA = "ifany"))), sep = "\n", file = stderr())
  }
}

filter_by_report_diagnosis <- function(d, report_diagnosis_type, report_subtypes) {
  if (!is.data.frame(d) || nrow(d) == 0) return(d)
  if (is.null(report_diagnosis_type) || identical(report_diagnosis_type, "All")) return(d)

  if (is.null(report_subtypes)) report_subtypes <- "All"
  report_subtypes <- setdiff(as.character(report_subtypes), "All")

  if (report_diagnosis_type == "1o & 2o") {
    return(
      d |>
        filter(
          (DiagnosisType == "P" & Diagnosis1o %in% report_subtypes) |
          (DiagnosisType == "S" & Diagnosis2o %in% report_subtypes)
        )
    )
  }

  diag_code <- switch(
    report_diagnosis_type,
    "Primary"   = "P",
    "Secondary" = "S",
    "Benign"    = "B",
    "Unknown"   = "U",
    ""
  )

  diag_col <- switch(
    diag_code,
    "P" = "Diagnosis1o",
    "S" = "Diagnosis2o",
    "B" = "DiagnosisBn",
    "U" = "DiagnosisUn",
    ""
  )

  if (nzchar(diag_col) && all(c("DiagnosisType", diag_col) %in% names(d))) {
    d |>
      filter(
        DiagnosisType == diag_code,
        .data[[diag_col]] %in% report_subtypes
      )
  } else {
    d
  }
}

# Builds FollowUp interval breaks/labels dynamically, scaled to
# report_max_months_followup, rather than a fixed 5-year scaffold.
# Always starts with a -6 to 0 month "Baseline" window, then 3/6-month
# resolution out to 1 year, then yearly thereafter, truncated (and closed)
# exactly at report_max_months_followup.
build_followup_bins <- function(max_months_followup,
                                include_aki_bin = FALSE) {

  candidates <- c(0, 3, 6, 12, 24, 36, 48, 60, 72, 84, 96, 108, 120)

  max_months_followup <- suppressWarnings(as.numeric(max_months_followup))

  if (is.na(max_months_followup) || max_months_followup <= 0) {
    max_months_followup <- 60
  }

  # 2 weeks expressed in months
  aki_months <- 14 / 30.44

  if (isTRUE(include_aki_bin)) {
    candidates <- sort(unique(c(0, aki_months, candidates)))
  }

  breaks <- candidates[candidates <= max_months_followup]

  if (length(breaks) == 0 || breaks[length(breaks)] < max_months_followup) {
    breaks <- c(breaks, max_months_followup)
  }

  if (breaks[1] != 0) {
    breaks <- c(0, breaks)
  }

  breaks <- unique(breaks)

  # Prepend baseline window
  breaks <- c(-6, breaks)

  label_interval <- function(a, b) {
  
    if (a == -6 && b == 0)
      return("Baseline")
  
    if (a == 0 && b < 1)
      return("0-2 wk")
  
    if (b == 3)
      return("2 wk-3 m")
  
    if (b <= 12)
      return(paste0(round(a), "-", round(b), " m"))
  
    if (a %% 12 == 0 && b %% 12 == 0)
      return(paste0(a / 12, "-", b / 12, " y"))
  
    paste0(round(a, 2), "-", round(b, 2), " m")
  }

  labels <- vapply(
    seq_len(length(breaks) - 1),
    function(i) label_interval(breaks[i], breaks[i + 1]),
    character(1)
  )

  list(
    breaks = breaks,
    labels = labels
  )
}

followup_bins <- build_followup_bins(report_max_months_followup, report_include_aki_bin)

filter_by_tumour_size <- function(df, size_col, min_size, max_size) {
  if (!is.data.frame(df) || nrow(df) == 0 || !size_col %in% names(df)) return(df)

  df[[size_col]] <- suppressWarnings(as.numeric(df[[size_col]]))

  df |>
    dplyr::filter(
      is.na(.data[[size_col]]) |
        dplyr::between(.data[[size_col]], min_size, max_size)
    )
}

normalise_organs <- function(x) {
  if (is.null(x) || length(x) == 0 || anyNA(x)) return("All")
  if (length(x) == 1 && identical(x, "All")) return("All")
  x
}

report_organs <- normalise_organs(report_organs)

filter_patient_rows <- function(df) {

  # initialise counters
  renal_filter_counts <<- list()

  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  # starting cohort
  d <- df |> 
    filter(!is.na(FirstRxDate))

  renal_filter_counts$start <- d %>%
    distinct(ID) %>%
    nrow()

  # report date filter
  d <- d |> 
    filter(FirstRxDate >= reportStart,
           FirstRxDate <= reportEnd)

  renal_filter_counts$report_period <- d %>%
    distinct(ID) %>%
    nrow()

  # organ filter
  if (!identical(report_organs, "All")) {
    d <- d |> 
      filter(
        grepl(
          paste(report_organs, collapse="|"),
          Organ
        )
      )
    }

  renal_filter_counts$organ <- d %>%
    distinct(ID) %>%
    nrow()

  # diagnosis filter
  d <- filter_by_report_diagnosis(
    d,
    report_diagnosis_type,
    report_subtypes
  )

  renal_filter_counts$diagnosis <- d %>%
    distinct(ID) %>%
    nrow()


  # modality filter
  if (!identical(report_organs, "All")) {
  
    d <- d |>
      filter(
        vapply(
          Organ,
          function(x) {
  
            if (is.na(x))
              return(FALSE)
  
            organs <- trimws(
              unlist(strsplit(x, ","))
            )
  
            all(organs %in% report_organs)
  
          },
          logical(1)
        )
      )
  }

  renal_filter_counts$modality <- d %>%
    distinct(ID) %>%
    nrow()

  d
}

filter_lesion_rows <- function(df)
{
  if (!is.data.frame(df) || nrow(df) == 0) return(df)

  d <- df |>
    filter(!is.na(RxDate)) |>
    filter(RxDate >= reportStart, RxDate <= reportEnd)

  if (!identical(report_organs, "All")) {
    d <- d |> filter(Organ %in% report_organs)
  }

  d <- filter_by_report_diagnosis(d, report_diagnosis_type, report_subtypes)

  if (!identical(report_modality, "All") &&
      "RxModality" %in% names(d)) {
  
    d <- d |>
      filter(
        Reduce(
          `|`,
          lapply(report_modality, function(m)
            grepl(m, RxModality, fixed = TRUE)
          )
        )
      )
  }
  d
}

# Get the filtered patient data and select only those where the MaxTumourSize is in reporting range
patient_data <- if (exists("cancerPerPatientData") && is.data.frame(cancerPerPatientData)) {
  filter_patient_rows(cancerPerPatientData)
} else {
  data.frame()
}

# ------------------------------------------------------------------
# Permanent renal cohort accounting counters for report summary
# ------------------------------------------------------------------

# All patients with eGFR entries
renal_egfr_ids <- renalFn.df %>%
  filter(!is.na(eGFR)) %>%
  mutate(PtID = sub("-[0-9]+$", "", PtID)) %>%
  distinct(PtID)

n_egfr_patients_raw <- nrow(renal_egfr_ids)


# Patients represented in cancerPerPatientData
cancer_ids <- cancerPerPatientData %>%
  mutate(PtID = sub("-[0-9]+$", "", ID)) %>%
  distinct(PtID)

n_egfr_patients_in_cancer <- renal_egfr_ids %>%
  semi_join(cancer_ids, by = "PtID") %>%
  nrow()

# Patients surviving all report filters
final_report_ids <- patient_data %>%
  mutate(PtID = sub("-[0-9]+$", "", ID)) %>%
  distinct(PtID)

n_egfr_patients_final <- renal_egfr_ids %>%
  semi_join(final_report_ids, by = "PtID") %>%
  nrow()

n_egfr_patients_excluded <- 
  n_egfr_patients_in_cancer - n_egfr_patients_final






# ------------------------------------------------------------
# DEBUG: identify exactly which cohort filter removes
# renal-function patients
# ------------------------------------------------------------

if (isTRUE(DEBUG_MODE) &&
    exists("renalFn.df") &&
    is.data.frame(renalFn.df) &&
    exists("cancerPerPatientData") &&
    is.data.frame(cancerPerPatientData)) {

  renal_ids <- renalFn.df %>%
    filter(!is.na(eGFR)) %>%
    mutate(PtID = as.character(PtID)) %>%
    distinct(PtID)

  # Start with all cancer patients
  test <- cancerPerPatientData %>%
    mutate(PtID = sub("-[0-9]+$", "", ID))

  renal_test <- test %>%
    semi_join(renal_ids, by = "PtID")

  debug_log(
    "Renal eGFR patients in cancerPerPatientData:",
    n_distinct(renal_test$PtID)
  )

  # ----------------------------------------------------------
  # 1. FirstRxDate filter
  # ----------------------------------------------------------

  after_date <- renal_test %>%
    filter(
      !is.na(FirstRxDate),
      FirstRxDate >= reportStart,
      FirstRxDate <= reportEnd
    )

  debug_log(
    "After FirstRxDate/report-period filter:",
    n_distinct(after_date$PtID)
  )

  debug_log(
    "Lost by FirstRxDate/report-period filter:",
    n_distinct(renal_test$PtID) -
      n_distinct(after_date$PtID)
  )

  debug_log(
    "DEBUG report_organs:",
    paste(report_organs, collapse = " | ")
  )
  
  debug_log(
    "DEBUG Organ values in renal cohort:",
    paste(
      head(sort(unique(after_date$Organ)), 20),
      collapse = " | "
    )
  )

  
  # ----------------------------------------------------------
  # 2. Organ filter
  # ----------------------------------------------------------

  if (identical(report_organs, "All")) {

    after_organ <- after_date

  } else {

    after_organ <- after_date %>%
      filter(
        vapply(
          Organ,
          function(x) {
            any(
              sapply(
                report_organs,
                function(o) grepl(o, x, fixed = TRUE)
              )
            )
          },
          logical(1)
        )
      )
  }

  debug_log(
    "After organ filter:",
    n_distinct(after_organ$PtID)
  )

  debug_log(
    "Lost by organ filter:",
    n_distinct(after_date$PtID) -
      n_distinct(after_organ$PtID)
  )

  # ----------------------------------------------------------
  # 3. Diagnosis filter
  # ----------------------------------------------------------

  after_diagnosis <- filter_by_report_diagnosis(
    after_organ,
    report_diagnosis_type,
    report_subtypes
  )

  debug_log(
    "After diagnosis filter:",
    n_distinct(after_diagnosis$PtID)
  )

  debug_log(
    "Lost by diagnosis filter:",
    n_distinct(after_organ$PtID) -
      n_distinct(after_diagnosis$PtID)
  )

  # ----------------------------------------------------------
  # 4. Modality filter
  # ----------------------------------------------------------

  if (identical(report_modality, "All")) {

    after_modality <- after_diagnosis

  } else {

    after_modality <- after_diagnosis %>%
      filter(
        vapply(
          RxModalities,
          function(x) {

            if (is.na(x) || length(x) == 0)
              return(FALSE)

            any(
              vapply(
                report_modality,
                function(m)
                  grepl(m, x, fixed = TRUE),
                logical(1)
              )
            )
          },
          logical(1)
        )
      )
  }

  debug_log(
    "After modality filter:",
    n_distinct(after_modality$PtID)
  )

  debug_log(
    "Lost by modality filter:",
    n_distinct(after_diagnosis$PtID) -
      n_distinct(after_modality$PtID)
  )

  debug_log(
    "Final renal eGFR patients surviving patient filters:",
    n_distinct(after_modality$PtID)
  )

  debug_log(
    "Current report_organs:",
    paste(report_organs, collapse = ", ")
  )

  debug_log(
    "Current report_diagnosis_type:",
    report_diagnosis_type
  )

  debug_log(
    "Current report_subtypes:",
    paste(report_subtypes, collapse = ", ")
  )

  debug_log(
    "Current report_modality:",
    paste(report_modality, collapse = ", ")
  )
}


if (nrow(patient_data) > 0) {
  n_before_size <- nrow(patient_data)
  patient_data <- filter_by_tumour_size(
    patient_data,
    "MaxTumourSize",
    report_min_tumour_size,
    report_max_tumour_size
  )
} else {
    lesion_data <- data.frame()
    renalFn_data <- data.frame()
}

# Derive the bare patient ID (referral suffix stripped) unconditionally -
# lesion_data is keyed on PtID without the "-N" referral
# suffix, so keep_ids must be in the same bare format to match correctly.
patient_data <- patient_data |>
  dplyr::mutate(PtID = sub("-[0-9]+$", "", ID))

# Apply modality filter to the patient cohort before renal extraction

if (!identical(report_modality, "All") &&
    "RxModalities" %in% names(patient_data)) {

  patient_data <- patient_data %>%
    filter(
      vapply(
        RxModalities,
        function(x) {

          if (is.na(x))
            return(FALSE)

          any(
            vapply(
              report_modality,
              function(m)
                grepl(m, x, fixed = TRUE),
              logical(1)
            )
          )

        },
        logical(1)
      )
    )
}


keep_ids <- patient_data %>%
  distinct(PtID)

lesion_data <- if (exists("cancerPerLesionData") &&
                   is.data.frame(cancerPerLesionData)) {

  cancerPerLesionData %>%
    semi_join(
      renal_egfr_ids_final,
      by = "PtID"
    )

} else {
  data.frame()
}

if (!identical(report_organs, "All")) {
  lesion_data <- lesion_data %>%
    filter(Organ %in% report_organs)
}

if (!identical(report_modality, "All") &&
    "RxModality" %in% names(lesion_data)) {
  lesion_data <- lesion_data %>%
    filter(
      grepl(
        paste(report_modality, collapse="|"),
        RxModality
      )
    )
}

lesion_data <- filter_by_tumour_size(
  lesion_data,
  "TumourSize",
  report_min_tumour_size,
  report_max_tumour_size
)






if (nrow(patient_data) > 0 && "MaxTumourSize" %in% names(patient_data)) {
  patient_data$MaxTumourSize <- suppressWarnings(as.numeric(patient_data$MaxTumourSize))
}
if (nrow(lesion_data) > 0 && "TumourSize" %in% names(lesion_data)) {
  lesion_data$TumourSize <- suppressWarnings(as.numeric(lesion_data$TumourSize))
}


renalFn_data <- if (exists("renalFn.df") && is.data.frame(renalFn.df))
{
  renalFn.df %>%
    semi_join(keep_ids, by = "PtID") %>%
    left_join(
      patient_data %>%
        select(any_of(c("PtID", "FirstRxDate"))) %>%
        distinct(PtID, .keep_all = TRUE),
      by = "PtID"
    )

} else {
  data.frame()
}

renal_egfr_ids_final <- renalFn_data %>%
  filter(!is.na(eGFR)) %>%
  distinct(PtID)


if (nrow(renalFn_data) > 0) {

  renalFn_data <- renalFn_data %>%
    mutate(
      Date = as.Date(sapply(Date, convertToDate)),
      FirstRxDate = as.Date(FirstRxDate),
      eGFR = as.numeric(eGFR),
      DaysFromRx = as.numeric(Date - FirstRxDate),
      MonthsFromRx = DaysFromRx / 30.44
    ) %>%
    # Restrict to the guaranteed minimum follow-up window: any reading taken
    # more than report_min_months_followup months AFTER treatment is dropped,
    # so every patient contributes an equal, unbiased follow-up window
    # rather than patients with longer follow-up dominating later
    # timepoints. Baseline / pre-treatment readings (MonthsFromRx <= 0) are
    # never affected -- only post-treatment readings are capped.
    filter(
      MonthsFromRx <= 0 | MonthsFromRx <= report_max_months_followup
    )
}







# ------------------------------------------------------------------
# DEBUG: renal baseline/post-treatment patient accounting
# ------------------------------------------------------------------

if (isTRUE(DEBUG_MODE) && nrow(renalFn_data) > 0) {

  renal_valid <- renalFn_data %>%
    filter(!is.na(eGFR), !is.na(PtID))

  baseline_ids_debug <- renal_valid %>%
    filter(
      DaysFromRx < 0,
      DaysFromRx >= -182.6
    ) %>%
    distinct(PtID)

  post_3m_ids_debug <- renal_valid %>%
    filter(
      DaysFromRx >= 0,
      DaysFromRx <= 3 * 30.44
    ) %>%
    distinct(PtID)

  both_debug <- intersect(
    baseline_ids_debug$PtID,
    post_3m_ids_debug$PtID
  )

  debug_log("==========================================")
  debug_log("RENAL BASELINE / POST-3M ACCOUNTING")
  debug_log("==========================================")

  debug_log(
    "Unique patients with any valid eGFR:",
    n_distinct(renal_valid$PtID)
  )

  debug_log(
    "Patients with baseline eGFR:",
    n_distinct(baseline_ids_debug$PtID)
  )

  debug_log(
    "Patients with post-treatment eGFR within 3 months:",
    n_distinct(post_3m_ids_debug$PtID)
  )

  debug_log(
    "Patients with BOTH baseline and post-treatment eGFR within 3 months:",
    length(both_debug)
  )

  debug_log(
    "Baseline patients WITHOUT post-3m eGFR:",
    length(setdiff(
      baseline_ids_debug$PtID,
      post_3m_ids_debug$PtID
    ))
  )

  debug_log(
    "Post-3m patients WITHOUT baseline eGFR:",
    length(setdiff(
      post_3m_ids_debug$PtID,
      baseline_ids_debug$PtID
    ))
  )

  debug_log(
    "Patients with post-treatment eGFR after 3 months:",
    n_distinct(
      renal_valid %>%
        filter(DaysFromRx > 3 * 30.44) %>%
        pull(PtID)
    )
  )

  debug_log("==========================================")
}






fmt_modality <- function(modality, df = NULL) {
  if (!identical(modality, "All")) {
    return(modality)
  }

  if (!is.data.frame(df) || !"RxModalities" %in% names(df)) {
    return("All")
  }

  mods <- unique(unlist(strsplit(
    as.character(df$RxModalities),
    split = ",|;|\\+|\\s+"
  )))

  mods <- trimws(mods)
  mods <- mods[mods != "" & !is.na(mods)]

  if (length(mods) == 0) {
    "All"
  } else {
    paste(sort(unique(mods)), collapse = ", ")
  }
}

fmt_param <- function(x) {
  x <- setdiff(as.character(x), "All")
  if (length(x) == 0) "All" else paste(x, collapse = ", ")
}

```

## Report Parameters

| Parameter | Value |
|:----------|:------|
| **Report generated** | `r format(Sys.time(), "%a %d %B %Y %H:%M")` |
| **Report period** | `r format(reportStart, "%d %B %Y")` – `r format(reportEnd, "%d %B %Y")` |
| **Organ(s)** | `r if (identical(report_organs, "All")) "All" else paste(report_organs, collapse = ", ")` |
| **Diagnosis type** | `r fmt_param(report_diagnosis_type)` |
| **Subtype(s)** | `r fmt_param(report_subtypes)` |
| **Tumour Size Range** | `r fmt_param(paste0(report_min_tumour_size, "-", report_max_tumour_size," mm"))` |
| **Gender(s)** | `r paste(report_genders, collapse = ", ")` |
| **Modality** | `r fmt_modality(report_modality, patient_data)` |
| **Minimum follow-up** | `r report_min_months_followup` months |
| **Maximum follow-up** | `r report_max_months_followup` months |
| **AKI Bin (0..2wk) Included** | `r if(report_include_aki_bin) "Yes" else "No"` |
| **Pt IDs anonymised** | `r if(reportAnonymised) "Yes" else "No"` |
| **Individual Pt. Plots** | `r if(reportAnonymised) "Yes" else "No"` |

---

```{r generate-all-plots, echo=FALSE, fig.height=4.8}
# Secret code to generate all the plots but dont plot them yet!


progress <- shiny::Progress$new()
progress$set(
  value = 0.2,
  message = "Setting things up..."
)

```

## Outcome Summary
```{r overview-table, echo=FALSE, results='asis'}

progress$set(
  value = 0.3,
  message = "Generating renal function report summary ..."
)

tumour_summary <- if (nrow(lesion_data) > 0 && "TumourSize" %in% names(lesion_data)) {
  lesion_data |>
    summarise(
      n = sum(!is.na(TumourSize)),
      median = median(TumourSize, na.rm = TRUE),
      sd = sd(TumourSize, na.rm = TRUE),
      mean = mean(TumourSize, na.rm = TRUE)
    )
} else {
  tibble::tibble(n = 0, median = NA_real_, sd = NA_real_, mean = NA_real_)
}

# --- Renal function data completeness metrics -----------------------------
# Moved up from later in the report so these can feed the summary table.
# "Baseline" = an eGFR reading in the 6 months (182.6 days) before FirstRxDate.
# "Valid delta" = a patient who has both a baseline reading AND at least one
# post-treatment reading (DaysFromRx >= 0), i.e. a genuine before/after
# comparison rather than just a lone baseline value.

baseline_ids <- renalFn_data %>%
  filter(
    DaysFromRx < 0,
    DaysFromRx >= -182.6,
    !is.na(eGFR)
  ) %>%
  distinct(PtID)

renalFn_analysis <- renalFn_data %>%
  semi_join(baseline_ids, by = "PtID")

post_ids <- renalFn_analysis %>%
  filter(DaysFromRx >= 0, !is.na(eGFR)) %>%
  distinct(PtID)








# ------------------------------------------------------------------
# Renal-function cohort accounting using permanent filter counters
# ------------------------------------------------------------------

# Permanent counters were created in filter_patient_rows()
# renal_filter_counts:
# start
# report_period
# organ
# diagnosis
# modality

n_egfr_raw <- n_egfr_patients_raw

n_egfr_in_cancer <- n_egfr_patients_in_cancer
# ------------------------------------------------------------------
# Renal-function filter accounting
# Recalculate from the actual patient cohort so values cannot be NA
# ------------------------------------------------------------------

renal_filter_ids <- cancerPerPatientData %>%
  mutate(PtID = sub("-[0-9]+$", "", ID)) %>%
  semi_join(
    renal_egfr_ids,
    by = "PtID"
  ) %>%
  distinct(PtID, .keep_all = TRUE)


# Date filter
date_filtered <- renal_filter_ids %>%
  filter(
    FirstRxDate >= reportStart,
    FirstRxDate <= reportEnd
  )


# Organ filter (strict: only requested organs, e.g. Kidney matches Kidney,Kidney but not Kidney,Liver)
if (identical(report_organs, "All")) {

  organ_filtered <- date_filtered

} else {

  organ_filtered <- date_filtered %>%
    filter(
      vapply(
        Organ,
        function(x) {

          if (is.na(x))
            return(FALSE)

          organs <- trimws(unlist(strsplit(x, ",")))

          all(organs %in% report_organs)

        },
        logical(1)
      )
    )
}


# Diagnosis filter
diagnosis_filtered <- filter_by_report_diagnosis(
  organ_filtered,
  report_diagnosis_type,
  report_subtypes
)


# Modality filter
if (identical(report_modality, "All")) {

  modality_filtered <- diagnosis_filtered

} else {

  modality_filtered <- diagnosis_filtered %>%
    filter(
      vapply(
        RxModalities,
        function(x) {

          if (is.na(x))
            return(FALSE)

          any(
            vapply(
              report_modality,
              function(m)
                grepl(m, x, fixed = TRUE),
              logical(1)
            )
          )
        },
        logical(1)
      )
    )
}

n_after_date <- date_filtered %>%
  distinct(PtID) %>%
  nrow()

n_after_organ <- organ_filtered %>%
  distinct(PtID) %>%
  nrow()

n_after_diagnosis <- diagnosis_filtered %>%
  distinct(PtID) %>%
  nrow()

n_after_modality <- modality_filtered %>%
  distinct(PtID) %>%
  nrow()

n_final_renal <- n_after_modality

date_filtered <- renal_filter_ids %>%
  filter(
    FirstRxDate >= reportStart,
    FirstRxDate <= reportEnd
  )


if (identical(report_organs, "All")) {

  organ_filtered <- date_filtered

} else {

  organ_filtered <- date_filtered %>%
    filter(
      vapply(
        Organ,
        function(x) {
  
          if (is.na(x))
            return(FALSE)
  
          organs <- trimws(
            unlist(strsplit(x, ","))
          )
  
          all(organs %in% report_organs)
  
        },
        logical(1)
      )
    )

}

diagnosis_filtered <- filter_by_report_diagnosis(
  organ_filtered,
  report_diagnosis_type,
  report_subtypes
)



if (identical(report_modality, "All")) {

  modality_filtered <- diagnosis_filtered

} else {

  modality_filtered <- diagnosis_filtered %>%
    filter(
      vapply(
        RxModalities,
        function(x) {
          any(
            vapply(
              report_modality,
              function(m)
                grepl(m, x, fixed = TRUE),
              logical(1)
            )
          )
        },
        logical(1)
      )
    )
}

n_final_renal <- n_after_modality

# ------------------------------------------------------------------
# Renal completeness
# ------------------------------------------------------------------

n_patients_baseline <- n_distinct(baseline_ids$PtID)

n_patients_valid_delta <- length(
  intersect(
    baseline_ids$PtID,
    post_ids$PtID
  )
)

n_egfr_total <- renalFn_data %>%
  filter(!is.na(eGFR)) %>%
  nrow()

n_egfr_included_analysis <- renalFn_analysis %>%
  filter(!is.na(eGFR)) %>%
  nrow()

n_report_patients <- n_distinct(patient_data$PtID)

# ------------------------------------------------------------------
# Summary table
# ------------------------------------------------------------------

# ------------------------------------------------------------------
# Summary table
# ------------------------------------------------------------------

table1 <- tibble::tibble(
  Metric = c(

    "No. Patients with eGFR(s) in EDC (unfiltered)",
    "...with matching cancer treatment data", # i.e. cancerPerPatientData
    "...after report-period filter",
    "...after organ filter",
    "...after diagnosis filter",
    "...after modality filter",
    "Patients in final report cohort",
    "Tumours treated",
    "Median tumour size (mm)",
    "SD tumour size (mm)"
  ),
  Value = c(

    format(n_egfr_raw, big.mark=","),
    format(n_egfr_in_cancer, big.mark=","),
    format(n_after_date, big.mark=","),
    format(n_after_organ, big.mark=","),
    format(n_after_diagnosis, big.mark=","),
    format(n_after_modality, big.mark=","),
    format(n_final_renal, big.mark=","),
    format(nrow(lesion_data), big.mark=","),
    format(tumour_summary$median, digits=1),
    format(tumour_summary$sd, digits=1)
  )
)


table2 <- tibble::tibble(
  Metric = c(
    "Patients with eGFR",
    "Patients with baseline eGFR",
    "Patients with valid delta eGFR (baseline + post)",
    "Total eGFR readings",
    "Total eGFR readings included in analysis"
  ),
  Value = c(
    format(n_distinct(renalFn_data$PtID), big.mark=","),
    format(n_patients_baseline, big.mark=","),
    format(n_patients_valid_delta, big.mark=","),
    format(n_egfr_total, big.mark=","),
    format(n_egfr_included_analysis, big.mark=",")
  )
)


# ------------------------------------------------------------------
# Render tables
# ------------------------------------------------------------------

table1_html <- kable(
  table1,
  format = "html",
  caption = "Cohort"
) |>
  kableExtra::kable_styling(
    full_width = TRUE,
    bootstrap_options = "condensed"
  ) |>
  as.character()

table2_html <- kable(
  table2,
  format = "html",
  caption = "Renal function"
) |>
  kableExtra::kable_styling(
    full_width = TRUE,
    bootstrap_options = "condensed"
  ) |>
  as.character()

cat(
  '<div style="display:flex; gap:25px; align-items:flex-start;">',
  '<div style="flex:1; min-width:0;">',
  table1_html,
  '</div>',
  '<div style="flex:1; min-width:0;">',
  table2_html,
  '</div>',
  '</div>'
)


renalPatients <- renalFn_data %>%
  arrange(PtID, DaysFromRx) %>%
  group_by(PtID)
```

```{r}
renalFn_display <- renalFn_data
if (isTRUE(reportAnonymised)) {
  renalFn_display$PtID <- anonymise_ptid(renalFn_display$PtID)
}
```

```{r renal-summary-plot, fig.width=10, fig.height=5}

renal.summary <-
    renalFn_analysis %>%

    filter(
        !is.na(MonthsFromRx),
        !is.na(eGFR)
    ) %>%

    mutate(
      FollowUp = cut(
          MonthsFromRx,
          breaks = followup_bins$breaks,
          labels = followup_bins$labels,
          include.lowest = TRUE,
          right = FALSE
        )
    ) %>%

    filter(!is.na(FollowUp)) %>%

    ## One eGFR per patient per interval
    group_by(PtID, FollowUp) %>%
    summarise(
        eGFR = mean(eGFR, na.rm = TRUE),
        .groups = "drop"
    ) %>%

    ## Then summarise across patients
    group_by(FollowUp) %>%
    summarise(
        Mean = mean(eGFR, na.rm = TRUE),
        Median = median(eGFR, na.rm = TRUE),
        SD = sd(eGFR, na.rm = TRUE),
        N = n_distinct(PtID),
        N_readings = n(),
        SE = SD / sqrt(N),
        Lower = Mean - 1.96 * SE,
        Upper = Mean + 1.96 * SE,
        .groups = "drop"
    ) %>%
    mutate(
      FollowUp = factor(FollowUp, levels = followup_bins$labels)
    )
  
  baseline_mean <- renal.summary %>%
    filter(FollowUp == "Baseline") %>%
    pull(Mean)
  
  if (length(baseline_mean) == 0) {
    baseline_mean <- NA_real_
  }
  
  
  ggplot(
      renal.summary,
      aes(FollowUp, Mean, group = 1)
  ) +
    
  geom_hline(
    yintercept = baseline_mean,
    colour = "red",
    linetype = 2
  ) +

  geom_ribbon(
      aes(
          ymin = Lower,
          ymax = Upper
      ),
      fill = "#4C9BE8",
      alpha = .20
  ) +

  geom_line(
      colour = "#005BBB",
      linewidth = 1.2
  ) +

  geom_point(
      aes(size = N),
      colour = "#005BBB"
  ) +

  geom_text_repel(
    aes(label = paste0("N=", N)),
    size = 3.8,
    colour = "black",
    fontface = "bold",
    box.padding = 0.5,
    point.padding = 0.4,
    min.segment.length = 0,
    seed = 123
  ) +

  scale_size(
      range = c(3,10),
      name = "Patients"
  ) +

  labs(
      x = "Follow-up interval",
      y = "Mean eGFR"
  ) +

  coord_cartesian(
      ylim = c(20,100)
  ) +

  theme_bw(base_size = 14) +

  theme(
      legend.position = "right",
      panel.grid.minor = element_blank(),
      axis.title = element_text(face = "bold")
  )
 
```
**Figure 1. Mean estimated glomerular filtration rate (eGFR) over follow-up.** Mean eGFR is shown for each follow-up interval among patients included in the renal function analysis. For patients with multiple measurements within an interval, measurements were first averaged within patient and then across patients. Points are scaled according to the number of patients contributing data to each interval, with the corresponding number shown alongside each point. Shaded areas represent 95% confidence intervals for the mean. The dashed horizontal line indicates baseline.
  

```{r egfr-delta-plot, fig.width=10, fig.height=5}

#---------------------------------------
# Calculate baseline renal function
#---------------------------------------

baseline <- renalFn_data %>%
  filter(
    DaysFromRx < 0,
    DaysFromRx >= -182.6,
    !is.na(eGFR)
  ) %>%
  group_by(PtID) %>%
  summarise(
    Baseline = mean(eGFR, na.rm = TRUE),
    .groups = "drop"
  )


#---------------------------------------
# Calculate change from baseline
#---------------------------------------

renal.delta <- renalFn_analysis %>%
  left_join(
    baseline,
    by = "PtID"
  ) %>%
  filter(!is.na(Baseline)) %>%
  
  mutate(
    Delta = eGFR - Baseline,
    FollowUp = cut(
      MonthsFromRx,
        breaks = followup_bins$breaks,
        labels = followup_bins$labels,
        include.lowest = TRUE,
        right = FALSE)

  ) %>%
  
  # force baseline to exactly zero
  mutate(
    Delta = ifelse(FollowUp == "Baseline", 0, Delta)
  ) %>%
  
  filter(!is.na(FollowUp))

baseline.count <- renal.delta %>%
  filter(
    !is.na(Baseline),
    !is.na(PtID),
    !is.na(FollowUp)
  ) %>%
  group_by(FollowUp) %>%
  summarise(
    N_baseline = n_distinct(PtID),
    .groups = "drop"
  )


#---------------------------------------
# Average within patient then across patients
#---------------------------------------

# Number of raw eGFR readings contributing to each interval
reading.count <- renal.delta %>%
  filter(
    !is.na(Delta),
    !is.na(PtID),
    !is.na(FollowUp)
  ) %>%
  group_by(FollowUp) %>%
  summarise(
    N_readings = n(),
    .groups = "drop"
  )

renal.delta.summary <- renal.delta %>%

  filter(
    !is.na(Delta),
    !is.na(PtID),
    !is.na(FollowUp)
  ) %>%

  # one delta value per patient per interval
  group_by(PtID, FollowUp) %>%
  summarise(
    Delta = mean(Delta, na.rm = TRUE),
    .groups = "drop"
  ) %>%

  # then summarise across patients
  group_by(FollowUp) %>%
  summarise(
    Mean    = mean(Delta, na.rm = TRUE),
    SD      = sd(Delta, na.rm = TRUE),
    N_delta = n_distinct(PtID),
    SE      = SD / sqrt(N_delta),
    Lower   = Mean - 1.96 * SE,
    Upper   = Mean + 1.96 * SE,
    .groups = "drop"
  ) %>%

  left_join(
    baseline.count,
    by = "FollowUp"
  ) %>%
  
  left_join(
    reading.count,
    by = "FollowUp"
  )

#---------------------------------------
# Plot
#---------------------------------------

ggplot(
  renal.delta.summary,
  aes(
    FollowUp,
    Mean,
    group = 1
  )
) +

geom_hline(
  yintercept = 0,
  colour = "red",
  linetype = 2
) +

geom_ribbon(
  aes(
    ymin = Lower,
    ymax = Upper
  ),
  fill = "#4C9BE8",
  alpha = 0.25
) +

geom_line(
  colour = "#005BBB",
  linewidth = 1.2
) +

geom_point(
  aes(size = N_delta),
  colour = "#005BBB"
) +

geom_text_repel(
  aes(label = paste0(
    "N=", N_delta,
    "\n(", N_readings, " readings)"
  )),
  size = 3.8,
  colour = "black",
  fontface = "bold",
  box.padding = 0.5,
  point.padding = 0.4,
  min.segment.length = 0,
  seed = 123
) +

scale_size(
  range = c(3,10),
  name = "Patients"
) +

labs(
  x = "Follow-up interval",
  y = "Δ eGFR from baseline"
) +

theme_bw(base_size = 14) +

theme(
  legend.position = "right",
  panel.grid.minor = element_blank(),
  axis.title = element_text(face = "bold"),
  axis.text = element_text(size = 12)

)
```
**Figure 2. Change in estimated glomerular filtration rate (Δ eGFR) from baseline over follow-up.** Baseline eGFR was defined as the mean of available eGFR measurements obtained within 6 months before treatment for each patient. Δ eGFR represents the difference between eGFR at each follow-up interval and the patient-specific baseline eGFR. Measurements were first averaged within patient and follow-up interval and then across patients. Points are scaled according to the number of patients contributing to each interval; Labels show the number of patients contributing ΔeGFR data to each interval mean (N) followed in parentheses by the number of individual eGFR measurements contributing to that mean. Shaded areas represent 95% confidence intervals. The dashed horizontal line indicates no change from baseline.

# All the individual patient plots for follow-up eGFR
```{r renal-patient-plots, fig.width=12, fig.height=10}

if (isTRUE(reportIndividualPtPlots))
{
  plots <- lapply(unique(renalFn_display$PtID), function(pt) {
  
    df <- renalFn_display %>%
      filter(PtID == pt) %>%
      arrange(DaysFromRx)
  
    ggplot(df,
           aes(DaysFromRx, eGFR)) +
  
      geom_vline(
        xintercept = 0,
        colour = "red",
        linetype = 2
      ) +
  
      geom_line(linewidth = 0.5) +
  
      geom_point(size = 1.5) +
  
      labs(
        title = paste("Patient", pt),
        x = "Days",
        y = "eGFR"
      ) +
  
      theme_bw(base_size = 10) +
  
      theme(
        plot.title = element_text(size = 11, face = "bold"),
        axis.title = element_text(size = 9, face = "bold"),
        axis.text = element_text(size = 8)
      )
  })
  
  
  page_size <- 9
  
  for(i in seq(1, length(plots), by = page_size)) {
  
    page_plots <- plots[i:min(i + page_size - 1, length(plots))]
  
    # Pad incomplete pages with empty panels so plots retain
    # the same 3-column width and do not stretch.
    n_spacers <- page_size - length(page_plots)
  
    if (n_spacers > 0) {
      page_plots <- c(
        page_plots,
        rep(list(patchwork::plot_spacer()), n_spacers)
      )
    }
  
    print(
      wrap_plots(
        page_plots,
        ncol = 3
      )
    )
  }
}
```
**Figure 3. Individual patient eGFR trajectories.** Each panel shows longitudinal eGFR measurements for an individual patient included in the renal function report. The horizontal axis represents days relative to treatment, with day 0 indicating the date of treatment. Points represent individual eGFR measurements and lines connect measurements chronologically. The dashed vertical line indicates the treatment date. Patient identifiers are anonymised where anonymisation has been selected for the report.


## Credits

```{r reportLogo, warning=FALSE}
logo_src <- here("www", "TARGETPlotterLogo.png")
if (file.exists(logo_src)) {
  knitr::include_graphics(normalizePath(logo_src))
} else {
  cat("<!-- TARGETPlotterLogo.png logo not available -->")
}

progress$set(
  value = 1.0,
  message = "Rendering report..."
)

later::later(
  function() {
    progress$close()
  },
  delay = 3
)

```



<br>
Report Report Developer: Dr. Paul Lyon<br>
TARGET-UK Lead: Dr. Paul Lyon, FRCR
